### 2018-09-20 manuscript/manuscript ideas.Rmd
Create new folder for manuscript ideas

---
title: "lambda manuscript ideas"
author: "James Grecian; Ian Jonsen"
date: "20/09/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-09-21 manuscript/manuscript_template.Rmd
Update markdown manuscript template

<!DOCTYPE html>
<html lang="en">
  <head>
    <meta charset="utf-8">
  <link rel="dns-prefetch" href="https://assets-cdn.github.com">
  <link rel="dns-prefetch" href="https://avatars0.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars1.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars2.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars3.githubusercontent.com">
  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">

  <link crossorigin="anonymous" media="all" integrity="sha512-/yZA7MGD9acBi5MmgjnivwjGeiNsmimsI/bhLlK7akrRuw+hMxNpJoQEMO9Zt0Nq6ZRu1m1NGV6r95Ib0zx7Qw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/frameworks-1ca00d32d1a8adc78ae7bb6677410eb1.css" />
  <link crossorigin="anonymous" media="all" integrity="sha512-pHF1luoMSUFxvz63bW3jEbbifYl/pruHUw+kljThAPi2g0nhgMdvWj4bQRh4O8MYp9NR60XYcylaLXmYA8YXSw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/github-5043b3d96d50b119b971c2cdde4e0a62.css" />

  <meta name="viewport" content="width=device-width">

  <title>Blog/manuscript_template.Rmd at master · petrkeil/Blog</title>
    <meta name="description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog">
    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
  <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
  <meta property="fb:app_id" content="1401488693436528">

    <meta property="og:image" content="https://avatars2.githubusercontent.com/u/5421227?s=400&amp;v=4" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="petrkeil/Blog" /><meta property="og:url" content="https://github.com/petrkeil/Blog" /><meta property="og:description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog" />

  <link rel="assets" href="https://assets-cdn.github.com/">
  <link rel="web-socket" href="wss://live.github.com/_sockets/VjI6MzE5MjkzMDMyOmY4ZDEyYmU0MjE5YTNjMTg5YzMwODMwOTRhOWJmYjA2NmU1ZDRjYzNmNTlkMmZmNThiNmEyMDhkY2U0ODM3YjU=--6699b174fe2e40623d9cdaf2af3c8eb14a2753a8">
  <meta name="pjax-timeout" content="1000">
  <link rel="sudo-modal" href="/sessions/sudo_modal">
  <meta name="request-id" content="DEC4:7B80:13DB109:2408B1B:5BA52F38" data-pjax-transient>

  <meta name="selected-link" value="repo_source" data-pjax-transient>

      <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
    <meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
    <meta name="google-site-verification" content="GXs5KoUUkNCoaAZn7wPN-t01Pywp9M3sEjnt_3_ZWPc">

  <meta name="octolytics-host" content="collector.githubapp.com" /><meta name="octolytics-app-id" content="github" /><meta name="octolytics-event-url" content="https://collector.githubapp.com/github-external/browser_event" /><meta name="octolytics-dimension-request_id" content="DEC4:7B80:13DB109:2408B1B:5BA52F38" /><meta name="octolytics-dimension-region_edge" content="iad" /><meta name="octolytics-dimension-region_render" content="iad" /><meta name="octolytics-actor-id" content="34245401" /><meta name="octolytics-actor-login" content="jamesgrecian" /><meta name="octolytics-actor-hash" content="821728246d06cdfe784e56dfb8dc2a4447ec5ee2fb7525c8728616156ffa29a2" />
<meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" />

    <meta name="google-analytics" content="UA-3769691-2">

  <meta class="js-ga-set" name="userId" content="078bbd73f63945865b3a6f9e3c674706" %>

<meta class="js-ga-set" name="dimension1" content="Logged In">

      <meta name="hostname" content="github.com">
    <meta name="user-login" content="jamesgrecian">

      <meta name="expected-hostname" content="github.com">
    <meta name="js-proxy-site-detection-payload" content="NGYyMDUzNWVkYjVhZGU3ZTI0NmJjNzE5MmZkYTM3N2YwMDRlOTk2MTFmMDRkYjNjY2VjZDJlYTIzN2JlYTFlN3x7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjM0LjI0OC4yMDciLCJyZXF1ZXN0X2lkIjoiREVDNDo3QjgwOjEzREIxMDk6MjQwOEIxQjo1QkE1MkYzOCIsInRpbWVzdGFtcCI6MTUzNzU1MjE5NiwiaG9zdCI6ImdpdGh1Yi5jb20ifQ==">

    <meta name="enabled-features" content="DASHBOARD_V2_LAYOUT_OPT_IN,EXPLORE_DISCOVER_REPOSITORIES,UNIVERSE_BANNER,MARKETPLACE_PLAN_RESTRICTION_EDITOR,MARKETPLACE_RETARGETING,QUOTE_MARKDOWN">

  <meta name="html-safe-nonce" content="4d33eb369dbc9e939c0c70269799ff90a62c9762">

  <meta http-equiv="x-pjax-version" content="3842ef7af97baac02526bd1bb609fd99">

      <link href="https://github.com/petrkeil/Blog/commits/master.atom" rel="alternate" title="Recent Commits to Blog:master" type="application/atom+xml">

  <meta name="go-import" content="github.com/petrkeil/Blog git https://github.com/petrkeil/Blog.git">

  <meta name="octolytics-dimension-user_id" content="5421227" /><meta name="octolytics-dimension-user_login" content="petrkeil" /><meta name="octolytics-dimension-repository_id" content="32012442" /><meta name="octolytics-dimension-repository_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="32012442" /><meta name="octolytics-dimension-repository_network_root_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_explore_github_marketplace_ci_cta_shown" content="false" />

    <link rel="canonical" href="https://github.com/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.Rmd" data-pjax-transient>

  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">

  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">

  <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#000000">
  <link rel="icon" type="image/x-icon" class="js-site-favicon" href="https://assets-cdn.github.com/favicon.ico">

<meta name="theme-color" content="#1e2327">

  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">

  </head>

  <body class="logged-in env-production page-blob">

  <div class="position-relative js-header-wrapper ">
    <a href="#start-of-content" tabindex="1" class="p-3 bg-blue text-white show-on-focus js-skip-to-content">Skip to content</a>
    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>

<header class="Header  f5" role="banner">
  <div class="d-flex flex-justify-between px-3 ">
    <div class="d-flex flex-justify-between ">
      <div class="">
        <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
  <svg height="32" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="32" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
</a>

      </div>

    </div>

    <div class="HeaderMenu d-flex flex-justify-between flex-auto">
      <div class="d-flex">
            <div class="">
              <div class="header-search scoped-search site-scoped-search js-site-search position-relative js-jump-to"
  role="combobox"
  aria-owns="jump-to-results"
  aria-label="Search or jump to"
  aria-haspopup="listbox"
  aria-expanded="false"
>
  <div class="position-relative">
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-site-search-form" data-scope-type="Repository" data-scope-id="32012442" data-scoped-search-url="/petrkeil/Blog/search" data-unscoped-search-url="/search" action="/petrkeil/Blog/search" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
      <label class="form-control header-search-wrapper header-search-wrapper-jump-to position-relative d-flex flex-justify-between flex-items-center js-chromeless-input-container">
        <input type="text"
          class="form-control header-search-input jump-to-field js-jump-to-field js-site-search-focus js-site-search-field is-clearable"
          data-hotkey="s,/"
          name="q"
          value=""
          placeholder="Search or jump to…"
          data-unscoped-placeholder="Search or jump to…"
          data-scoped-placeholder="Search or jump to…"
          autocapitalize="off"
          aria-autocomplete="list"
          aria-controls="jump-to-results"
          data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations#csrf-token=vKtepHuL5c+ELLxqvw5pBoFyrsH33qoqLeuwQXRDqVrb+0oabwda3WZ6kzvLvbGCX4m1kWaOg5yCDa6OI6VHtw=="
          spellcheck="false"
          autocomplete="off"
          >
          <input type="hidden" class="js-site-search-type-field" name="type" >
            <img src="https://assets-cdn.github.com/images/search-shortcut-hint.svg" alt="" class="mr-2 header-search-key-slash">

            <div class="Box position-absolute overflow-hidden d-none jump-to-suggestions js-jump-to-suggestions-container">
              <ul class="d-none js-jump-to-suggestions-template-container">
                <li class="d-flex flex-justify-start flex-items-center p-0 f5 navigation-item js-navigation-item" role="option">
                  <a tabindex="-1" class="no-underline d-flex flex-auto flex-items-center p-2 jump-to-suggestions-path js-jump-to-suggestion-path js-navigation-open" href="">
                    <div class="jump-to-octicon js-jump-to-octicon mr-2 text-center d-none">
                      <svg height="16" width="16" class="octicon octicon-repo flex-shrink-0 js-jump-to-octicon-repo d-none" title="Repository" aria-label="Repository" viewBox="0 0 12 16" version="1.1" role="img"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-project flex-shrink-0 js-jump-to-octicon-project d-none" title="Project" aria-label="Project" viewBox="0 0 15 16" version="1.1" role="img"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-search flex-shrink-0 js-jump-to-octicon-search d-none" title="Search" aria-label="Search" viewBox="0 0 16 16" version="1.1" role="img"><path fill-rule="evenodd" d="M15.7 13.3l-3.81-3.83A5.93 5.93 0 0 0 13 6c0-3.31-2.69-6-6-6S1 2.69 1 6s2.69 6 6 6c1.3 0 2.48-.41 3.47-1.11l3.83 3.81c.19.2.45.3.7.3.25 0 .52-.09.7-.3a.996.996 0 0 0 0-1.41v.01zM7 10.7c-2.59 0-4.7-2.11-4.7-4.7 0-2.59 2.11-4.7 4.7-4.7 2.59 0 4.7 2.11 4.7 4.7 0 2.59-2.11 4.7-4.7 4.7z"/></svg>
                    </div>

                    <img class="avatar mr-2 flex-shrink-0 js-jump-to-suggestion-avatar d-none" alt="" aria-label="Team" src="" width="28" height="28">

                    <div class="jump-to-suggestion-name js-jump-to-suggestion-name flex-auto overflow-hidden text-left no-wrap css-truncate css-truncate-target">
                    </div>

                    <div class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none js-jump-to-badge-search">
                      <span class="js-jump-to-badge-search-text-default d-none" aria-label="in this repository">
                        In this repository
                      </span>
                      <span class="js-jump-to-badge-search-text-global d-none" aria-label="in all of GitHub">
                        All GitHub
                      </span>
                      <span aria-hidden="true" class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>

                    <div aria-hidden="true" class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none d-on-nav-focus js-jump-to-badge-jump">
                      Jump to
                      <span class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>
                  </a>
                </li>
              </ul>
              <ul class="d-none js-jump-to-no-results-template-container">
                <li class="d-flex flex-justify-center flex-items-center p-3 f5 d-none">
                  <span class="text-gray">No suggested jump to results</span>
                </li>
              </ul>

              <ul id="jump-to-results" role="listbox" class="js-navigation-container jump-to-suggestions-results-container js-jump-to-suggestions-results-container" >
                <li class="d-flex flex-justify-center flex-items-center p-0 f5">
                  <img src="https://assets-cdn.github.com/images/spinners/octocat-spinner-128.gif" alt="Octocat Spinner Icon" class="m-2" width="28">
                </li>
              </ul>
            </div>
      </label>
</form>  </div>
</div>

            </div>

          <ul class="d-flex pl-2 flex-items-center text-bold list-style-none" role="navigation">
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g p" data-ga-click="Header, click, Nav menu - item:pulls context:user" aria-label="Pull requests you created" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls" href="/pulls">
                Pull requests
</a>            </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g i" data-ga-click="Header, click, Nav menu - item:issues context:user" aria-label="Issues you created" data-selected-links="/issues /issues/assigned /issues/mentioned /issues" href="/issues">
                Issues
</a>            </li>
              <li>
                <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:marketplace context:user" data-octo-click="marketplace_click" data-octo-dimensions="location:nav_bar" data-selected-links=" /marketplace" href="/marketplace">
                   Marketplace
</a>              </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:explore" data-selected-links="/explore /trending /trending/developers /integrations /integrations/feature/code /integrations/feature/collaborate /integrations/feature/ship showcases showcases_search showcases_landing /explore" href="/explore">
                Explore
</a>            </li>
          </ul>
      </div>

      <div class="d-flex">

<ul class="user-nav d-flex flex-items-center list-style-none" id="user-links">
  <li class="dropdown">
    <span class="d-inline-block  px-2">

    <a aria-label="You have no unread notifications" class="notification-indicator tooltipped tooltipped-s  js-socket-channel js-notification-indicator" data-hotkey="g n" data-ga-click="Header, go to notifications, icon:read" data-channel="notification-changed:34245401" href="/notifications">
        <span class="mail-status "></span>
        <svg class="octicon octicon-bell" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M13.99 11.991v1H0v-1l.73-.58c.769-.769.809-2.547 1.189-4.416.77-3.767 4.077-4.996 4.077-4.996 0-.55.45-1 .999-1 .55 0 1 .45 1 1 0 0 3.387 1.229 4.156 4.996.38 1.879.42 3.657 1.19 4.417l.659.58h-.01zM6.995 15.99c1.11 0 1.999-.89 1.999-1.999H4.996c0 1.11.89 1.999 1.999 1.999z"/></svg>
</a>
    </span>
  </li>

  <li class="dropdown">
    <details class="details-overlay details-reset d-flex px-2 flex-items-center">
      <summary class="HeaderNavlink"
         aria-label="Create new…"
         data-ga-click="Header, create new, icon:add">
        <svg class="octicon octicon-plus float-left mr-1 mt-1" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 9H7v5H5V9H0V7h5V2h2v5h5v2z"/></svg>
        <span class="dropdown-caret mt-1"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">

<a role="menuitem" class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
  New repository
</a>

  <a role="menuitem" class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
    Import repository
  </a>

<a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, create new gist">
  New gist
</a>

  <a role="menuitem" class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
    New organization
  </a>

  <div class="dropdown-divider"></div>
  <div class="dropdown-header">
    <span title="petrkeil/Blog">This repository</span>
  </div>
    <a role="menuitem" class="dropdown-item" href="/petrkeil/Blog/issues/new" data-ga-click="Header, create new issue">
      New issue
    </a>

      </details-menu>
    </details>
  </li>

  <li class="dropdown">

    <details class="details-overlay details-reset d-flex pl-2 flex-items-center">
      <summary class="HeaderNavlink name mt-1"
        aria-label="View profile and more"
        data-ga-click="Header, show menu, icon:avatar">
        <img alt="@jamesgrecian" class="avatar float-left mr-1" src="https://avatars2.githubusercontent.com/u/34245401?s=40&amp;v=4" height="20" width="20">
        <span class="dropdown-caret"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">
        <ul>
          <li class="header-nav-current-user css-truncate"><a role="menuitem" class="no-underline user-profile-link px-3 pt-2 pb-2 mb-n2 mt-n1 d-block" href="/jamesgrecian" data-ga-click="Header, go to profile, text:Signed in as">Signed in as <strong class="css-truncate-target">jamesgrecian</strong></a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian" data-ga-click="Header, go to profile, text:your profile">Your profile</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=repositories" data-ga-click="Header, go to repositories, text:your repositories">Your repositories</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">Your stars</a></li>
            <li><a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, your gists, text:your gists">Your gists</a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">Help</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">Settings</a></li>
          <li>
            <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="logout-form" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="70z+7pfJi/hSwFPV+HwBpRO+h6tPFRwPr5KWtHt/uVnEYJnva1K9ZZ8MF/preCNcmvA/GicmqsAz47+DjSrHhg==" />
              <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout" role="menuitem">
                Sign out
              </button>
</form>          </li>
        </ul>
      </details-menu>
    </details>
  </li>
</ul>

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="sr-only right-0" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="xmQg0zHF9HnWv4MzKNWcgsKD5qm6fAiK0ZheRQvWYivtSEfSzV7C5Btzxxy70b57S81eGNJPvkVN6Xdy/YMc9A==" />
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </div>
</header>

  </div>

  <div id="start-of-content" class="show-on-focus"></div>

    <div id="js-flash-container">

</div>

  <div role="main" class="application-main ">
        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
    <div id="js-repo-pjax-container" data-pjax-container >

  <div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav  ">
    <div class="repohead-details-container clearfix container">

      <ul class="pagehead-actions">
  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form data-autosubmit="true" data-remote="true" class="js-social-container" action="/notifications/subscribe" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="oOjYFEFAFqKUnhayqPj0oBlERt/6I+ne5pf8Sl8iMXmjlzqHCag0+YA+/9+8U1yIKjTim6/xQpufP+1q6zhkGQ==" />      <input type="hidden" name="repository_id" id="repository_id" value="32012442" class="form-control" />

        <div class="select-menu js-menu-container js-select-menu">
          <a href="/petrkeil/Blog/subscription"
            class="btn btn-sm btn-with-count select-menu-button js-menu-target"
            role="button"
            aria-haspopup="true"
            aria-expanded="false"
            aria-label="Toggle repository notifications menu"
            data-ga-click="Repository, click Watch settings, action:blob#show">
            <span class="js-select-button">
                <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                Watch
            </span>
          </a>
          <a class="social-count js-social-count"
            href="/petrkeil/Blog/watchers"
            aria-label="17 users are watching this repository">
            17
          </a>

        <div class="select-menu-modal-holder">
          <div class="select-menu-modal subscription-menu-modal js-menu-content">
            <div class="select-menu-header js-navigation-enable" tabindex="-1">
              <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
              <span class="select-menu-title">Notifications</span>
            </div>

              <div class="select-menu-list js-navigation-container" role="menu">

                <div class="select-menu-item js-navigation-item selected" role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_included" value="included" checked="checked" />
                    <span class="select-menu-item-heading">Not watching</span>
                    <span class="description">Be notified when participating or @mentioned.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                      Watch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_subscribed" value="subscribed" />
                    <span class="select-menu-item-heading">Watching</span>
                    <span class="description">Be notified of all conversations.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                        Unwatch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_ignore" value="ignore" />
                    <span class="select-menu-item-heading">Ignoring</span>
                    <span class="description">Never be notified.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-mute v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 2.81v10.38c0 .67-.81 1-1.28.53L3 10H1c-.55 0-1-.45-1-1V7c0-.55.45-1 1-1h2l3.72-3.72C7.19 1.81 8 2.14 8 2.81zm7.53 3.22l-1.06-1.06-1.97 1.97-1.97-1.97-1.06 1.06L11.44 8 9.47 9.97l1.06 1.06 1.97-1.97 1.97 1.97 1.06-1.06L13.56 8l1.97-1.97z"/></svg>
                        Stop ignoring
                    </span>
                  </div>
                </div>

              </div>

            </div>
          </div>
        </div>
</form>
  </li>

  <li>

  <div class="js-toggler-container js-social-container starring-container ">
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="starred js-social-form" action="/petrkeil/Blog/unstar" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="J1oHiD/jIasQWYvIghtqwNeIcq7Wz8HRwv5jjbAgOUiPVQ0EIQakzs+VFq2Jme9ff2CNRtGmfDd21a9Dmlzz+g==" />
      <input type="hidden" name="context" value="repository"></input>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Unstar this repository" title="Unstar petrkeil/Blog"
        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
        Unstar
      </button>
        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
           aria-label="79 users starred this repository">
          79
        </a>
</form>
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="unstarred js-social-form" action="/petrkeil/Blog/star" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="QDgeOt/aBH8Yr862sLVj5rnSJEuVN8SGuxtswA5f/IDNGmAIWBfI4wwEyYlLxWpNLF8Shijy9vdBluRlDnHlzg==" />
      <input type="hidden" name="context" value="repository"></input>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Star this repository" title="Star petrkeil/Blog"
        data-ga-click="Repository, click star button, action:blob#show; text:Star">
        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
        Star
      </button>
        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
           aria-label="79 users starred this repository">
          79
        </a>
</form>  </div>

  </li>

  <li>
          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="btn-with-count" action="/petrkeil/Blog/fork" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="Y84ilm5ix19gKu7BVYnfUlbhnPecmOc6pf0ITkJM8rS5L8RVxf9S1+VeyBggIdVBYUlUVnj+9FNoFw91y42Z/Q==" />
            <button
                type="submit"
                class="btn btn-sm btn-with-count"
                data-ga-click="Repository, show fork modal, action:blob#show; text:Fork"
                title="Fork your own copy of petrkeil/Blog to your account"
                aria-label="Fork your own copy of petrkeil/Blog to your account">
              <svg class="octicon octicon-repo-forked v-align-text-bottom" viewBox="0 0 10 16" version="1.1" width="10" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 1a1.993 1.993 0 0 0-1 3.72V6L5 8 3 6V4.72A1.993 1.993 0 0 0 2 1a1.993 1.993 0 0 0-1 3.72V6.5l3 3v1.78A1.993 1.993 0 0 0 5 15a1.993 1.993 0 0 0 1-3.72V9.5l3-3V4.72A1.993 1.993 0 0 0 8 1zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3 10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3-10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
              Fork
            </button>
</form>
    <a href="/petrkeil/Blog/network/members" class="social-count"
       aria-label="130 users forked this repository">
      130
    </a>
  </li>
</ul>

      <h1 class="public ">
  <svg class="octicon octicon-repo" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
  <span class="author" itemprop="author"><a class="url fn" rel="author" href="/petrkeil">petrkeil</a></span><!--
--><span class="path-divider">/</span><!--
--><strong itemprop="name"><a data-pjax="#js-repo-pjax-container" href="/petrkeil/Blog">Blog</a></strong>

</h1>

    </div>

<nav class="reponav js-repo-nav js-sidenav-container-pjax container"
     itemscope
     itemtype="http://schema.org/BreadcrumbList"
     role="navigation"
     data-pjax="#js-repo-pjax-container">

  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
    <a class="js-selected-navigation-item selected reponav-item" itemprop="url" data-hotkey="g c" data-selected-links="repo_source repo_downloads repo_commits repo_releases repo_tags repo_branches repo_packages /petrkeil/Blog" href="/petrkeil/Blog">
      <svg class="octicon octicon-code" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M9.5 3L8 4.5 11.5 8 8 11.5 9.5 13 14 8 9.5 3zm-5 0L0 8l4.5 5L6 11.5 2.5 8 6 4.5 4.5 3z"/></svg>
      <span itemprop="name">Code</span>
      <meta itemprop="position" content="1">
</a>  </span>

    <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
      <a itemprop="url" data-hotkey="g i" class="js-selected-navigation-item reponav-item" data-selected-links="repo_issues repo_labels repo_milestones /petrkeil/Blog/issues" href="/petrkeil/Blog/issues">
        <svg class="octicon octicon-issue-opened" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7 2.3c3.14 0 5.7 2.56 5.7 5.7s-2.56 5.7-5.7 5.7A5.71 5.71 0 0 1 1.3 8c0-3.14 2.56-5.7 5.7-5.7zM7 1C3.14 1 0 4.14 0 8s3.14 7 7 7 7-3.14 7-7-3.14-7-7-7zm1 3H6v5h2V4zm0 6H6v2h2v-2z"/></svg>
        <span itemprop="name">Issues</span>
        <span class="Counter">1</span>
        <meta itemprop="position" content="2">
</a>    </span>

  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
    <a data-hotkey="g p" itemprop="url" class="js-selected-navigation-item reponav-item" data-selected-links="repo_pulls checks /petrkeil/Blog/pulls" href="/petrkeil/Blog/pulls">
      <svg class="octicon octicon-git-pull-request" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 11.28V5c-.03-.78-.34-1.47-.94-2.06C9.46 2.35 8.78 2.03 8 2H7V0L4 3l3 3V4h1c.27.02.48.11.69.31.21.2.3.42.31.69v6.28A1.993 1.993 0 0 0 10 15a1.993 1.993 0 0 0 1-3.72zm-1 2.92c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zM4 3c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v6.56A1.993 1.993 0 0 0 2 15a1.993 1.993 0 0 0 1-3.72V4.72c.59-.34 1-.98 1-1.72zm-.8 10c0 .66-.55 1.2-1.2 1.2-.65 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
      <span itemprop="name">Pull requests</span>
      <span class="Counter">0</span>
      <meta itemprop="position" content="3">
</a>  </span>

    <a data-hotkey="g b" class="js-selected-navigation-item reponav-item" data-selected-links="repo_projects new_repo_project repo_project /petrkeil/Blog/projects" href="/petrkeil/Blog/projects">
      <svg class="octicon octicon-project" viewBox="0 0 15 16" version="1.1" width="15" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
      Projects
      <span class="Counter" >0</span>
</a>

    <a class="js-selected-navigation-item reponav-item" data-hotkey="g w" data-selected-links="repo_wiki /petrkeil/Blog/wiki" href="/petrkeil/Blog/wiki">
      <svg class="octicon octicon-book" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M3 5h4v1H3V5zm0 3h4V7H3v1zm0 2h4V9H3v1zm11-5h-4v1h4V5zm0 2h-4v1h4V7zm0 2h-4v1h4V9zm2-6v9c0 .55-.45 1-1 1H9.5l-1 1-1-1H2c-.55 0-1-.45-1-1V3c0-.55.45-1 1-1h5.5l1 1 1-1H15c.55 0 1 .45 1 1zm-8 .5L7.5 3H2v9h6V3.5zm7-.5H9.5l-.5.5V12h6V3z"/></svg>
      Wiki
</a>
  <a class="js-selected-navigation-item reponav-item" data-selected-links="repo_graphs repo_contributors dependency_graph pulse /petrkeil/Blog/pulse" href="/petrkeil/Blog/pulse">
    <svg class="octicon octicon-graph" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M16 14v1H0V0h1v14h15zM5 13H3V8h2v5zm4 0H7V3h2v10zm4 0h-2V6h2v7z"/></svg>
    Insights
</a>

</nav>

  </div>

<div class="container new-discussion-timeline experiment-repo-nav  ">
  <div class="repository-content ">

  <a class="d-none js-permalink-shortcut" data-hotkey="y" href="/petrkeil/Blog/blob/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.Rmd">Permalink</a>

  <!-- blob contrib key: blob_contributors:v21:0cba21dec00b9f9b447a2242a22fa2b0 -->

  <div class="file-navigation">

<div class="select-menu branch-select-menu js-menu-container js-select-menu float-left">
  <button class=" btn btn-sm select-menu-button js-menu-target css-truncate" data-hotkey="w"

    type="button" aria-label="Switch branches or tags" aria-expanded="false" aria-haspopup="true">
      <i>Branch:</i>
      <span class="js-select-button css-truncate-target">master</span>
  </button>

  <div class="select-menu-modal-holder js-menu-content js-navigation-container" data-pjax>

    <div class="select-menu-modal">
      <div class="select-menu-header">
        <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
        <span class="select-menu-title">Switch branches/tags</span>
      </div>

      <div class="select-menu-filters">
        <div class="select-menu-text-filter">
          <input type="text" aria-label="Filter branches/tags" id="context-commitish-filter-field" class="form-control js-filterable-field js-navigation-enable" placeholder="Filter branches/tags">
        </div>
        <div class="select-menu-tabs">
          <ul>
            <li class="select-menu-tab">
              <a href="#" data-tab-filter="branches" data-filter-placeholder="Filter branches/tags" class="js-select-menu-tab" role="tab">Branches</a>
            </li>
            <li class="select-menu-tab">
              <a href="#" data-tab-filter="tags" data-filter-placeholder="Find a tag…" class="js-select-menu-tab" role="tab">Tags</a>
            </li>
          </ul>
        </div>
      </div>

      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="branches" role="menu">

        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">

            <a class="select-menu-item js-navigation-item js-navigation-open selected"
               href="/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.Rmd"
               data-name="master"
               data-skip-pjax="true"
               rel="nofollow">
              <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
              <span class="select-menu-item-text css-truncate-target js-select-menu-filter-text">
                master
              </span>
            </a>
        </div>

          <div class="select-menu-no-results">Nothing to show</div>
      </div>

      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="tags">
        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">

        </div>

        <div class="select-menu-no-results">Nothing to show</div>
      </div>

    </div>
  </div>
</div>

    <div class="BtnGroup float-right">
      <a href="/petrkeil/Blog/find/master"
            class="js-pjax-capture-input btn btn-sm BtnGroup-item"
            data-pjax
            data-hotkey="t">
        Find file
      </a>
      <clipboard-copy for="blob-path" class="btn btn-sm BtnGroup-item">
        Copy path
      </clipboard-copy>
    </div>
    <div id="blob-path" class="breadcrumb">
      <span class="repo-root js-repo-root"><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog"><span>Blog</span></a></span></span><span class="separator">/</span><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog/tree/master/2015_03_12_R_ms_template"><span>2015_03_12_R_ms_template</span></a></span><span class="separator">/</span><strong class="final-path">manuscript_template.Rmd</strong>
    </div>
  </div>

  <div class="commit-tease">
      <span class="float-right">
        <a class="commit-tease-sha" href="/petrkeil/Blog/commit/52b1e1cde0fb01bb0a205930ff265432581bb784" data-pjax>
          52b1e1c
        </a>
        <relative-time datetime="2015-03-12T22:12:59Z">Mar 12, 2015</relative-time>
      </span>
      <div>
        <img class="avatar" width="20" height="20" alt="" src="https://camo.githubusercontent.com/758da529902cc2f78e89a8a8ff28794146eabdf1/68747470733a2f2f322e67726176617461722e636f6d2f6176617461722f38626534333437643665363765386533353066616361316435613237663331643f643d68747470732533412532462532466173736574732d63646e2e6769746875622e636f6d253246696d6167657325324667726176617461727325324667726176617461722d757365722d3432302e706e6726723d6726733d313430" data-canonical-src="https://2.gravatar.com/avatar/8be4347d6e67e8e350faca1d5a27f31d?d=https%3A%2F%2Fassets-cdn.github.com%2Fimages%2Fgravatars%2Fgravatar-user-420.png&amp;r=g&amp;s=140" />
        <span class="user-mention">Petr Keil</span>
          <a data-pjax="true" title="Citations modified to include R and packages" class="message" href="/petrkeil/Blog/commit/52b1e1cde0fb01bb0a205930ff265432581bb784">Citations modified to include R and packages</a>
      </div>

    <div class="commit-tease-contributors">

<details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark float-left mr-2" id="blob_contributors_box">
  <summary class="btn-link" aria-haspopup="dialog"  >

    <span><strong>0</strong> contributors</span>
  </summary>
  <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast " aria-label="Users who have contributed to this file">
    <div class="Box-header">
      <button class="Box-btn-octicon btn-octicon float-right" type="button" aria-label="Close dialog" data-close-dialog>
        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
      </button>
      <h3 class="Box-title">Users who have contributed to this file</h3>
    </div>

        <ul class="list-style-none overflow-auto">
        </ul>

  </details-dialog>
</details>

    </div>
  </div>

  <div class="file">
    <div class="file-header">
  <div class="file-actions">

    <div class="BtnGroup">
      <a id="raw-url" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/raw/master/2015_03_12_R_ms_template/manuscript_template.Rmd">Raw</a>
        <a class="btn btn-sm js-update-url-with-hash BtnGroup-item" data-hotkey="b" href="/petrkeil/Blog/blame/master/2015_03_12_R_ms_template/manuscript_template.Rmd">Blame</a>
      <a rel="nofollow" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/commits/master/2015_03_12_R_ms_template/manuscript_template.Rmd">History</a>
    </div>

          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form js-update-url-with-hash" action="/petrkeil/Blog/edit/master/2015_03_12_R_ms_template/manuscript_template.Rmd" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="RDQWb0ZLZztiOYIPlc8RR++SnYgTcU462l3VdiTyiYFsCe4KWd8HON+YIzeb3gW38TGuLa9sVdJc/AOC18Cn4w==" />
            <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
              aria-label="Fork this project and edit the file" data-hotkey="e" data-disable-with>
              <svg class="octicon octicon-pencil" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"/></svg>
            </button>
</form>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form" action="/petrkeil/Blog/delete/master/2015_03_12_R_ms_template/manuscript_template.Rmd" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="2SKvxp3pXN29EtFLN/3i3X0L0HbpmjB1H77ptWHdxXcWgHhUCtbdjiLn0Y5q/XAe46BnM5fLjZqhWOZPztrDLg==" />
          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
            aria-label="Fork this project and delete the file" data-disable-with>
            <svg class="octicon octicon-trashcan" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"/></svg>
          </button>
</form>  </div>

  <div class="file-info">
      112 lines (71 sloc)
      <span class="file-info-divider"></span>
    5.18 KB
  </div>
</div>

  <div id="readme" class="readme blob instapaper_body">
    <article class="markdown-body entry-content" itemprop="text"><table data-table-type="yaml-metadata">
  <thead>
  <tr>
  <th>title</th>
  <th>author</th>
  <th>date</th>
  <th>output</th>
  <th>csl</th>
  <th>bibliography</th>
  </tr>
  </thead>
  <tbody>
  <tr>
  <td><div>Template for writing scientific papers in R markdown</div></td>
  <td><div>Petr Keil, pkeil@seznam.cz</div></td>
  <td><div>11/1/2015</div></td>
  <td><div><table>
  <thead>
  <tr>
  <th>pdf_document</th>
  <th>html_document</th>
  </tr>
  </thead>
  <tbody>
  <tr>
  <td><div><table>
  <thead>
  <tr>
  <th>fig_caption</th>
  <th>keep_tex</th>
  <th>number_sections</th>
  </tr>
  </thead>
  <tbody>
  <tr>
  <td><div>true</div></td>
  <td><div>true</div></td>
  <td><div>true</div></td>
  </tr>
  </tbody>
</table>
</div></td>
  <td><div><table>
  <thead>
  <tr>
  <th>fig_caption</th>
  <th>force_captions</th>
  <th>highlight</th>
  <th>number_sections</th>
  <th>theme</th>
  </tr>
  </thead>
  <tbody>
  <tr>
  <td><div>true</div></td>
  <td><div>true</div></td>
  <td><div>pygments</div></td>
  <td><div>true</div></td>
  <td><div>cerulean</div></td>
  </tr>
  </tbody>
</table>
</div></td>
  </tr>
  </tbody>
</table>
</div></td>
  <td><div>mee.csl</div></td>
  <td><div>references.bib</div></td>
  </tr>
  </tbody>
</table>

<pre lang="{r,"><code>  # devtools::install_github("cboettig/knitcitations@v1")
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=FALSE)
  library(bibtex)
</code></pre>
<h1><a id="user-content-abstract" class="anchor" aria-hidden="true" href="#abstract"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Abstract</h1>
<p><em>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</em></p>
<h1><a id="user-content-introduction" class="anchor" aria-hidden="true" href="#introduction"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Introduction</h1>
<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</p>
<p>Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.</p>
<p>Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes percipitur at vis. Numquam similique in per, te quo saepe utroque pericula.</p>
<p>Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne suas latine vix, eos oblique sanctus pertinax cu.</p>
<h1><a id="user-content-methods" class="anchor" aria-hidden="true" href="#methods"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Methods</h1>
<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</p>
<p>Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.</p>
<h2><a id="user-content-equations" class="anchor" aria-hidden="true" href="#equations"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Equations</h2>
<p>The deterministic part of the model is defined by this <strong>in-line equation</strong> as
$\mu_i = \beta_0 + \beta_1x$, and the stochastic part by the <strong>centered equation</strong>:</p>
<p>$$ \frac{1}{\sqrt{2\pi}\sigma}e^{-(x-\mu_i)^2/(2\sigma^2)} $$</p>
<h2><a id="user-content-tables" class="anchor" aria-hidden="true" href="#tables"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Tables</h2>
<pre lang="{r"><code>library(knitr)

x &lt;- rnorm(100)
y &lt;- 2*x + rnorm(100)
out &lt;- lm(y ~ x)
kable(summary(out)$coef, digits=2, caption="This is a GLM summary table.")
</code></pre>
<pre lang="{r"><code>library(xtable)
tab &lt;- xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
              caption="This is a GLM summary table.")
print(tab, type="latex")
</code></pre>
<h2><a id="user-content-plots" class="anchor" aria-hidden="true" href="#plots"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Plots</h2>
<pre lang="{r"><code>  plot(x, y)
  abline(out)
</code></pre>
<h2><a id="user-content-citations" class="anchor" aria-hidden="true" href="#citations"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Citations</h2>
<p>The relationship was first described by
<code>r citet("10.1111/j.1461-0248.2005.00827.x")</code>. However, there are also opinions
that the relationship is spurious <code>r citep("10.1111/j.2041-210x.2012.00264.x")</code>.
We used R for our calculations <code>r citep(citation())</code>, and we used package <code>knitcitations</code> <code>r citep(citation("knitcitations"))</code> to make the bibliography.</p>
<h1><a id="user-content-results-and-discussion" class="anchor" aria-hidden="true" href="#results-and-discussion"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Results and discussion</h1>
<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</p>
<p>Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.</p>
<p>Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes percipitur at vis. Numquam similique in per, te quo saepe utroque pericula.</p>
<p>Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne suas latine vix, eos oblique sanctus pertinax cu.</p>
<h1><a id="user-content-references" class="anchor" aria-hidden="true" href="#references"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>References</h1>
<pre lang="{r,"><code>  write.bibtex(file="references.bib")
</code></pre>
</article>
  </div>

  </div>

  <details class="details-reset details-overlay details-overlay-dark">
    <summary data-hotkey="l" aria-label="Jump to line"></summary>
    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast linejump" aria-label="Jump to line">
      <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-jump-to-line-form Box-body d-flex" action="" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
        <input class="form-control flex-auto mr-3 linejump-input js-jump-to-line-field" type="text" placeholder="Jump to line&hellip;" aria-label="Jump to line" autofocus>
        <button type="submit" class="btn" data-close-dialog>Go</button>
</form>    </details-dialog>
  </details>

  </div>
  <div class="modal-backdrop js-touch-events"></div>
</div>

    </div>
  </div>

  </div>

<div class="footer container-lg px-3" role="contentinfo">
  <div class="position-relative d-flex flex-justify-between pt-6 pb-2 mt-6 f6 text-gray border-top border-gray-light ">
    <ul class="list-style-none d-flex flex-wrap ">
      <li class="mr-3">&copy; 2018 <span title="0.17379s from unicorn-6bfd5c759c-j6nwh">GitHub</span>, Inc.</li>
        <li class="mr-3"><a data-ga-click="Footer, go to terms, text:terms" href="https://github.com/site/terms">Terms</a></li>
        <li class="mr-3"><a data-ga-click="Footer, go to privacy, text:privacy" href="https://github.com/site/privacy">Privacy</a></li>
        <li class="mr-3"><a href="https://help.github.com/articles/github-security/" data-ga-click="Footer, go to security, text:security">Security</a></li>
        <li class="mr-3"><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
        <li><a data-ga-click="Footer, go to help, text:help" href="https://help.github.com">Help</a></li>
    </ul>

    <a aria-label="Homepage" title="GitHub" class="footer-octicon mr-lg-4" href="https://github.com">
      <svg height="24" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="24" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
</a>
   <ul class="list-style-none d-flex flex-wrap ">
        <li class="mr-3"><a data-ga-click="Footer, go to contact, text:contact" href="https://github.com/contact">Contact GitHub</a></li>
        <li class="mr-3"><a href="https://github.com/pricing" data-ga-click="Footer, go to Pricing, text:Pricing">Pricing</a></li>
      <li class="mr-3"><a href="https://developer.github.com" data-ga-click="Footer, go to api, text:api">API</a></li>
      <li class="mr-3"><a href="https://training.github.com" data-ga-click="Footer, go to training, text:training">Training</a></li>
        <li class="mr-3"><a href="https://blog.github.com" data-ga-click="Footer, go to blog, text:blog">Blog</a></li>
        <li><a data-ga-click="Footer, go to about, text:about" href="https://github.com/about">About</a></li>

    </ul>
  </div>
  <div class="d-flex flex-justify-center pb-6">
    <span class="f6 text-gray-light"></span>
  </div>
</div>

  <div id="ajax-error-message" class="ajax-error-message flash flash-error">
    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
    <button type="button" class="flash-close js-ajax-error-dismiss" aria-label="Dismiss error">
      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
    </button>
    You can’t perform that action at this time.
  </div>

    <script crossorigin="anonymous" integrity="sha512-RJ1ufbxsSbKjRCyYvinsPNKvTBvcvvKUvEOJ8g+GjtWI5SuRr+QPBlZcvRDws4H9YwAgdQFcGxfL8UbwEfdI7A==" type="application/javascript" src="https://assets-cdn.github.com/assets/compat-daf14de28fadf1e2bc40d100cb773e2b.js"></script>
    <script crossorigin="anonymous" integrity="sha512-IC5Ai6c7cUBfMx54JUAsIjA7VroipzkizlZ8F6/0efsGGyZStweZV7bX9bxSFL07nUNLfwrKSEysVIijX+CeUw==" type="application/javascript" src="https://assets-cdn.github.com/assets/frameworks-5874e38105ec062c740350eeb96bdd8a.js"></script>

    <script crossorigin="anonymous" async="async" integrity="sha512-/E7YUPwg5s5FmwhSiwtXwNsTUCpjjdcrKoK7UFMQCguTSC71dACKl+XDhBftzkBsRra4w+a24G4oU535TieAIA==" type="application/javascript" src="https://assets-cdn.github.com/assets/github-1835546276a57f4d0c3203810d2ec7d6.js"></script>

  <div class="js-stale-session-flash stale-session-flash flash flash-warn flash-banner d-none">
    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
    <span class="signed-in-tab-flash">You signed in with another tab or window. <a href="">Reload</a> to refresh your session.</span>
    <span class="signed-out-tab-flash">You signed out in another tab or window. <a href="">Reload</a> to refresh your session.</span>
  </div>
  <div class="facebox" id="facebox" style="display:none;">
  <div class="facebox-popup">
    <div class="facebox-content" role="dialog" aria-labelledby="facebox-header" aria-describedby="facebox-description">
    </div>
    <button type="button" class="facebox-close js-facebox-close" aria-label="Close modal">
      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
    </button>
  </div>
</div>

  <template id="site-details-dialog">
  <details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark" open>
    <summary aria-haspopup="dialog" aria-label="Close dialog"></summary>
    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast">
      <button class="Box-btn-octicon m-0 btn-octicon position-absolute right-0 top-0" type="button" aria-label="Close dialog" data-close-dialog>
        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
      </button>
      <div class="octocat-spinner my-6 js-details-dialog-spinner"></div>
    </details-dialog>
  </details>
</template>

  <div class="Popover js-hovercard-content position-absolute" style="display: none; outline: none;" tabindex="0">
  <div class="Popover-message Popover-message--bottom-left Popover-message--large Box box-shadow-large" style="width:360px;">
  </div>
</div>

<div id="hovercard-aria-description" class="sr-only">
  Press h to open a hovercard with more details.
</div>

  </body>
</html>

### 2018-09-21 manuscript/manuscript_template.tex
Update markdown manuscript template

<!DOCTYPE html>
<html lang="en">
  <head>
    <meta charset="utf-8">
  <link rel="dns-prefetch" href="https://assets-cdn.github.com">
  <link rel="dns-prefetch" href="https://avatars0.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars1.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars2.githubusercontent.com">
  <link rel="dns-prefetch" href="https://avatars3.githubusercontent.com">
  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">

  <link crossorigin="anonymous" media="all" integrity="sha512-/yZA7MGD9acBi5MmgjnivwjGeiNsmimsI/bhLlK7akrRuw+hMxNpJoQEMO9Zt0Nq6ZRu1m1NGV6r95Ib0zx7Qw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/frameworks-1ca00d32d1a8adc78ae7bb6677410eb1.css" />
  <link crossorigin="anonymous" media="all" integrity="sha512-pHF1luoMSUFxvz63bW3jEbbifYl/pruHUw+kljThAPi2g0nhgMdvWj4bQRh4O8MYp9NR60XYcylaLXmYA8YXSw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/github-5043b3d96d50b119b971c2cdde4e0a62.css" />

  <meta name="viewport" content="width=device-width">

  <title>Blog/manuscript_template.tex at master · petrkeil/Blog</title>
    <meta name="description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog">
    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
  <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
  <meta property="fb:app_id" content="1401488693436528">

    <meta property="og:image" content="https://avatars2.githubusercontent.com/u/5421227?s=400&amp;v=4" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="petrkeil/Blog" /><meta property="og:url" content="https://github.com/petrkeil/Blog" /><meta property="og:description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog" />

  <link rel="assets" href="https://assets-cdn.github.com/">
  <link rel="web-socket" href="wss://live.github.com/_sockets/VjI6MzE5MjkzMDMyOjcxODYyYzE1ZGViNTZjN2U2YjQzMjlhZWYzYzI0Mjk2MjFjODZlN2QzMzM0YmVkYzI2NWJhNDYyY2JkYjc2MTM=--6f13a55f6f2aea699ea77deb92d45357f788dd6a">
  <meta name="pjax-timeout" content="1000">
  <link rel="sudo-modal" href="/sessions/sudo_modal">
  <meta name="request-id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" data-pjax-transient>

  <meta name="selected-link" value="repo_source" data-pjax-transient>

      <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
    <meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
    <meta name="google-site-verification" content="GXs5KoUUkNCoaAZn7wPN-t01Pywp9M3sEjnt_3_ZWPc">

  <meta name="octolytics-host" content="collector.githubapp.com" /><meta name="octolytics-app-id" content="github" /><meta name="octolytics-event-url" content="https://collector.githubapp.com/github-external/browser_event" /><meta name="octolytics-dimension-request_id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" /><meta name="octolytics-dimension-region_edge" content="iad" /><meta name="octolytics-dimension-region_render" content="iad" /><meta name="octolytics-actor-id" content="34245401" /><meta name="octolytics-actor-login" content="jamesgrecian" /><meta name="octolytics-actor-hash" content="821728246d06cdfe784e56dfb8dc2a4447ec5ee2fb7525c8728616156ffa29a2" />
<meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" />

    <meta name="google-analytics" content="UA-3769691-2">

  <meta class="js-ga-set" name="userId" content="078bbd73f63945865b3a6f9e3c674706" %>

<meta class="js-ga-set" name="dimension1" content="Logged In">

      <meta name="hostname" content="github.com">
    <meta name="user-login" content="jamesgrecian">

      <meta name="expected-hostname" content="github.com">
    <meta name="js-proxy-site-detection-payload" content="ZjQ2OTM3ZjcwZjc1MzhhMTAyNTFmYmY2MDk5NmJjYjZlM2NjNmMwMmQwYjExOTc1NGVlZDU4YzMzMzBkYmNhNXx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjM0LjI0OC4yMDciLCJyZXF1ZXN0X2lkIjoiREVDRjo3QjdDOkIzRTU1RToxNDdDOTUzOjVCQTUyRjc1IiwidGltZXN0YW1wIjoxNTM3NTUyMjQ2LCJob3N0IjoiZ2l0aHViLmNvbSJ9">

    <meta name="enabled-features" content="DASHBOARD_V2_LAYOUT_OPT_IN,EXPLORE_DISCOVER_REPOSITORIES,UNIVERSE_BANNER,MARKETPLACE_PLAN_RESTRICTION_EDITOR,MARKETPLACE_RETARGETING,QUOTE_MARKDOWN">

  <meta name="html-safe-nonce" content="4d33eb369dbc9e939c0c70269799ff90a62c9762">

  <meta http-equiv="x-pjax-version" content="3842ef7af97baac02526bd1bb609fd99">

      <link href="https://github.com/petrkeil/Blog/commits/master.atom" rel="alternate" title="Recent Commits to Blog:master" type="application/atom+xml">

  <meta name="go-import" content="github.com/petrkeil/Blog git https://github.com/petrkeil/Blog.git">

  <meta name="octolytics-dimension-user_id" content="5421227" /><meta name="octolytics-dimension-user_login" content="petrkeil" /><meta name="octolytics-dimension-repository_id" content="32012442" /><meta name="octolytics-dimension-repository_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="32012442" /><meta name="octolytics-dimension-repository_network_root_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_explore_github_marketplace_ci_cta_shown" content="false" />

    <link rel="canonical" href="https://github.com/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.tex" data-pjax-transient>

  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">

  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">

  <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#000000">
  <link rel="icon" type="image/x-icon" class="js-site-favicon" href="https://assets-cdn.github.com/favicon.ico">

<meta name="theme-color" content="#1e2327">

  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">

  </head>

  <body class="logged-in env-production page-blob">

  <div class="position-relative js-header-wrapper ">
    <a href="#start-of-content" tabindex="1" class="p-3 bg-blue text-white show-on-focus js-skip-to-content">Skip to content</a>
    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>

<header class="Header  f5" role="banner">
  <div class="d-flex flex-justify-between px-3 ">
    <div class="d-flex flex-justify-between ">
      <div class="">
        <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
  <svg height="32" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="32" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
</a>

      </div>

    </div>

    <div class="HeaderMenu d-flex flex-justify-between flex-auto">
      <div class="d-flex">
            <div class="">
              <div class="header-search scoped-search site-scoped-search js-site-search position-relative js-jump-to"
  role="combobox"
  aria-owns="jump-to-results"
  aria-label="Search or jump to"
  aria-haspopup="listbox"
  aria-expanded="false"
>
  <div class="position-relative">
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-site-search-form" data-scope-type="Repository" data-scope-id="32012442" data-scoped-search-url="/petrkeil/Blog/search" data-unscoped-search-url="/search" action="/petrkeil/Blog/search" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
      <label class="form-control header-search-wrapper header-search-wrapper-jump-to position-relative d-flex flex-justify-between flex-items-center js-chromeless-input-container">
        <input type="text"
          class="form-control header-search-input jump-to-field js-jump-to-field js-site-search-focus js-site-search-field is-clearable"
          data-hotkey="s,/"
          name="q"
          value=""
          placeholder="Search or jump to…"
          data-unscoped-placeholder="Search or jump to…"
          data-scoped-placeholder="Search or jump to…"
          autocapitalize="off"
          aria-autocomplete="list"
          aria-controls="jump-to-results"
          data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations#csrf-token=zcJUvtqaKw72uX3+FzR9OQAX21rWJn+bojDj6/4pZ0qqkkAAzhaUHBTvUq9jh6W93uzACkd2Vi0N1v0kqc+Jpw=="
          spellcheck="false"
          autocomplete="off"
          >
          <input type="hidden" class="js-site-search-type-field" name="type" >
            <img src="https://assets-cdn.github.com/images/search-shortcut-hint.svg" alt="" class="mr-2 header-search-key-slash">

            <div class="Box position-absolute overflow-hidden d-none jump-to-suggestions js-jump-to-suggestions-container">
              <ul class="d-none js-jump-to-suggestions-template-container">
                <li class="d-flex flex-justify-start flex-items-center p-0 f5 navigation-item js-navigation-item" role="option">
                  <a tabindex="-1" class="no-underline d-flex flex-auto flex-items-center p-2 jump-to-suggestions-path js-jump-to-suggestion-path js-navigation-open" href="">
                    <div class="jump-to-octicon js-jump-to-octicon mr-2 text-center d-none">
                      <svg height="16" width="16" class="octicon octicon-repo flex-shrink-0 js-jump-to-octicon-repo d-none" title="Repository" aria-label="Repository" viewBox="0 0 12 16" version="1.1" role="img"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-project flex-shrink-0 js-jump-to-octicon-project d-none" title="Project" aria-label="Project" viewBox="0 0 15 16" version="1.1" role="img"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
                      <svg height="16" width="16" class="octicon octicon-search flex-shrink-0 js-jump-to-octicon-search d-none" title="Search" aria-label="Search" viewBox="0 0 16 16" version="1.1" role="img"><path fill-rule="evenodd" d="M15.7 13.3l-3.81-3.83A5.93 5.93 0 0 0 13 6c0-3.31-2.69-6-6-6S1 2.69 1 6s2.69 6 6 6c1.3 0 2.48-.41 3.47-1.11l3.83 3.81c.19.2.45.3.7.3.25 0 .52-.09.7-.3a.996.996 0 0 0 0-1.41v.01zM7 10.7c-2.59 0-4.7-2.11-4.7-4.7 0-2.59 2.11-4.7 4.7-4.7 2.59 0 4.7 2.11 4.7 4.7 0 2.59-2.11 4.7-4.7 4.7z"/></svg>
                    </div>

                    <img class="avatar mr-2 flex-shrink-0 js-jump-to-suggestion-avatar d-none" alt="" aria-label="Team" src="" width="28" height="28">

                    <div class="jump-to-suggestion-name js-jump-to-suggestion-name flex-auto overflow-hidden text-left no-wrap css-truncate css-truncate-target">
                    </div>

                    <div class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none js-jump-to-badge-search">
                      <span class="js-jump-to-badge-search-text-default d-none" aria-label="in this repository">
                        In this repository
                      </span>
                      <span class="js-jump-to-badge-search-text-global d-none" aria-label="in all of GitHub">
                        All GitHub
                      </span>
                      <span aria-hidden="true" class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>

                    <div aria-hidden="true" class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none d-on-nav-focus js-jump-to-badge-jump">
                      Jump to
                      <span class="d-inline-block ml-1 v-align-middle">↵</span>
                    </div>
                  </a>
                </li>
              </ul>
              <ul class="d-none js-jump-to-no-results-template-container">
                <li class="d-flex flex-justify-center flex-items-center p-3 f5 d-none">
                  <span class="text-gray">No suggested jump to results</span>
                </li>
              </ul>

              <ul id="jump-to-results" role="listbox" class="js-navigation-container jump-to-suggestions-results-container js-jump-to-suggestions-results-container" >
                <li class="d-flex flex-justify-center flex-items-center p-0 f5">
                  <img src="https://assets-cdn.github.com/images/spinners/octocat-spinner-128.gif" alt="Octocat Spinner Icon" class="m-2" width="28">
                </li>
              </ul>
            </div>
      </label>
</form>  </div>
</div>

            </div>

          <ul class="d-flex pl-2 flex-items-center text-bold list-style-none" role="navigation">
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g p" data-ga-click="Header, click, Nav menu - item:pulls context:user" aria-label="Pull requests you created" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls" href="/pulls">
                Pull requests
</a>            </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g i" data-ga-click="Header, click, Nav menu - item:issues context:user" aria-label="Issues you created" data-selected-links="/issues /issues/assigned /issues/mentioned /issues" href="/issues">
                Issues
</a>            </li>
              <li>
                <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:marketplace context:user" data-octo-click="marketplace_click" data-octo-dimensions="location:nav_bar" data-selected-links=" /marketplace" href="/marketplace">
                   Marketplace
</a>              </li>
            <li>
              <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:explore" data-selected-links="/explore /trending /trending/developers /integrations /integrations/feature/code /integrations/feature/collaborate /integrations/feature/ship showcases showcases_search showcases_landing /explore" href="/explore">
                Explore
</a>            </li>
          </ul>
      </div>

      <div class="d-flex">

<ul class="user-nav d-flex flex-items-center list-style-none" id="user-links">
  <li class="dropdown">
    <span class="d-inline-block  px-2">

    <a aria-label="You have no unread notifications" class="notification-indicator tooltipped tooltipped-s  js-socket-channel js-notification-indicator" data-hotkey="g n" data-ga-click="Header, go to notifications, icon:read" data-channel="notification-changed:34245401" href="/notifications">
        <span class="mail-status "></span>
        <svg class="octicon octicon-bell" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M13.99 11.991v1H0v-1l.73-.58c.769-.769.809-2.547 1.189-4.416.77-3.767 4.077-4.996 4.077-4.996 0-.55.45-1 .999-1 .55 0 1 .45 1 1 0 0 3.387 1.229 4.156 4.996.38 1.879.42 3.657 1.19 4.417l.659.58h-.01zM6.995 15.99c1.11 0 1.999-.89 1.999-1.999H4.996c0 1.11.89 1.999 1.999 1.999z"/></svg>
</a>
    </span>
  </li>

  <li class="dropdown">
    <details class="details-overlay details-reset d-flex px-2 flex-items-center">
      <summary class="HeaderNavlink"
         aria-label="Create new…"
         data-ga-click="Header, create new, icon:add">
        <svg class="octicon octicon-plus float-left mr-1 mt-1" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 9H7v5H5V9H0V7h5V2h2v5h5v2z"/></svg>
        <span class="dropdown-caret mt-1"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">

<a role="menuitem" class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
  New repository
</a>

  <a role="menuitem" class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
    Import repository
  </a>

<a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, create new gist">
  New gist
</a>

  <a role="menuitem" class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
    New organization
  </a>

  <div class="dropdown-divider"></div>
  <div class="dropdown-header">
    <span title="petrkeil/Blog">This repository</span>
  </div>
    <a role="menuitem" class="dropdown-item" href="/petrkeil/Blog/issues/new" data-ga-click="Header, create new issue">
      New issue
    </a>

      </details-menu>
    </details>
  </li>

  <li class="dropdown">

    <details class="details-overlay details-reset d-flex pl-2 flex-items-center">
      <summary class="HeaderNavlink name mt-1"
        aria-label="View profile and more"
        data-ga-click="Header, show menu, icon:avatar">
        <img alt="@jamesgrecian" class="avatar float-left mr-1" src="https://avatars2.githubusercontent.com/u/34245401?s=40&amp;v=4" height="20" width="20">
        <span class="dropdown-caret"></span>
      </summary>
      <details-menu class="dropdown-menu dropdown-menu-sw">
        <ul>
          <li class="header-nav-current-user css-truncate"><a role="menuitem" class="no-underline user-profile-link px-3 pt-2 pb-2 mb-n2 mt-n1 d-block" href="/jamesgrecian" data-ga-click="Header, go to profile, text:Signed in as">Signed in as <strong class="css-truncate-target">jamesgrecian</strong></a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian" data-ga-click="Header, go to profile, text:your profile">Your profile</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=repositories" data-ga-click="Header, go to repositories, text:your repositories">Your repositories</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">Your stars</a></li>
            <li><a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, your gists, text:your gists">Your gists</a></li>
          <li class="dropdown-divider"></li>
          <li><a role="menuitem" class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">Help</a></li>
          <li><a role="menuitem" class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">Settings</a></li>
          <li>
            <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="logout-form" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="OM5YtlFU+S06U7ppNLcVxzqWiaBef+wxiPcpMrVBU5MT4j+3rc/PsPef/kanszc+s9gxETZMWv4UhgAFQxQtTA==" />
              <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout" role="menuitem">
                Sign out
              </button>
</form>          </li>
        </ul>
      </details-menu>
    </details>
  </li>
</ul>

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="sr-only right-0" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="N1zKEjZbcCo1MI7p6SB0skpuMDcaIk1EZ0F9bAHxVPkccK0TysBGt/j8ysZ6JFZLwyCIhnIR+4v7MFRb96QqJg==" />
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </div>
</header>

  </div>

  <div id="start-of-content" class="show-on-focus"></div>

    <div id="js-flash-container">

</div>

  <div role="main" class="application-main ">
        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
    <div id="js-repo-pjax-container" data-pjax-container >

  <div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav  ">
    <div class="repohead-details-container clearfix container">

      <ul class="pagehead-actions">
  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form data-autosubmit="true" data-remote="true" class="js-social-container" action="/notifications/subscribe" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="waV7OqLCkNQ0PEw4EE9fOf24fp4CwT8NUr+psybqPnPC2pmp6iqyjyCcpVUE5PcRzsja2lcTlEgrF7iTkvBrEw==" />      <input type="hidden" name="repository_id" id="repository_id" value="32012442" class="form-control" />

        <div class="select-menu js-menu-container js-select-menu">
          <a href="/petrkeil/Blog/subscription"
            class="btn btn-sm btn-with-count select-menu-button js-menu-target"
            role="button"
            aria-haspopup="true"
            aria-expanded="false"
            aria-label="Toggle repository notifications menu"
            data-ga-click="Repository, click Watch settings, action:blob#show">
            <span class="js-select-button">
                <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                Watch
            </span>
          </a>
          <a class="social-count js-social-count"
            href="/petrkeil/Blog/watchers"
            aria-label="17 users are watching this repository">
            17
          </a>

        <div class="select-menu-modal-holder">
          <div class="select-menu-modal subscription-menu-modal js-menu-content">
            <div class="select-menu-header js-navigation-enable" tabindex="-1">
              <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
              <span class="select-menu-title">Notifications</span>
            </div>

              <div class="select-menu-list js-navigation-container" role="menu">

                <div class="select-menu-item js-navigation-item selected" role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_included" value="included" checked="checked" />
                    <span class="select-menu-item-heading">Not watching</span>
                    <span class="description">Be notified when participating or @mentioned.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                      Watch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_subscribed" value="subscribed" />
                    <span class="select-menu-item-heading">Watching</span>
                    <span class="description">Be notified of all conversations.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
                        Unwatch
                    </span>
                  </div>
                </div>

                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
                  <div class="select-menu-item-text">
                    <input type="radio" name="do" id="do_ignore" value="ignore" />
                    <span class="select-menu-item-heading">Ignoring</span>
                    <span class="description">Never be notified.</span>
                    <span class="js-select-button-text hidden-select-button-text">
                      <svg class="octicon octicon-mute v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 2.81v10.38c0 .67-.81 1-1.28.53L3 10H1c-.55 0-1-.45-1-1V7c0-.55.45-1 1-1h2l3.72-3.72C7.19 1.81 8 2.14 8 2.81zm7.53 3.22l-1.06-1.06-1.97 1.97-1.97-1.97-1.06 1.06L11.44 8 9.47 9.97l1.06 1.06 1.97-1.97 1.97 1.97 1.06-1.06L13.56 8l1.97-1.97z"/></svg>
                        Stop ignoring
                    </span>
                  </div>
                </div>

              </div>

            </div>
          </div>
        </div>
</form>
  </li>

  <li>

  <div class="js-toggler-container js-social-container starring-container ">
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="starred js-social-form" action="/petrkeil/Blog/unstar" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="xltxbluajNFId7AvsA2kLFrwH068xBSLr0PJCzWLHSVuVHviRX8JtJe7LUq7jyGz8hjgprutqW0baAXFH/fXlw==" />
      <input type="hidden" name="context" value="repository"></input>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Unstar this repository" title="Unstar petrkeil/Blog"
        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
        Unstar
      </button>
        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
           aria-label="79 users starred this repository">
          79
        </a>
</form>
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="unstarred js-social-form" action="/petrkeil/Blog/star" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="cPLIa0QY+qYMlMwi/9bU+C/A9mTe3RprTTukgLuaBKX90LZZw9U2Ohg/yx0Ept1Tuk3AqWMYKBq3tiwlu7Qd6w==" />
      <input type="hidden" name="context" value="repository"></input>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Star this repository" title="Star petrkeil/Blog"
        data-ga-click="Repository, click star button, action:blob#show; text:Star">
        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
        Star
      </button>
        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
           aria-label="79 users starred this repository">
          79
        </a>
</form>  </div>

  </li>

  <li>
          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="btn-with-count" action="/petrkeil/Blog/fork" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="PsH2GGamjWRUveFXkgE8BlYYfdPSGso9/BRONJENUajkIBDbzTsY7NHJx47nqTYVYbC1cjZ82VQx/kkPGMw64Q==" />
            <button
                type="submit"
                class="btn btn-sm btn-with-count"
                data-ga-click="Repository, show fork modal, action:blob#show; text:Fork"
                title="Fork your own copy of petrkeil/Blog to your account"
                aria-label="Fork your own copy of petrkeil/Blog to your account">
              <svg class="octicon octicon-repo-forked v-align-text-bottom" viewBox="0 0 10 16" version="1.1" width="10" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 1a1.993 1.993 0 0 0-1 3.72V6L5 8 3 6V4.72A1.993 1.993 0 0 0 2 1a1.993 1.993 0 0 0-1 3.72V6.5l3 3v1.78A1.993 1.993 0 0 0 5 15a1.993 1.993 0 0 0 1-3.72V9.5l3-3V4.72A1.993 1.993 0 0 0 8 1zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3 10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3-10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
              Fork
            </button>
</form>
    <a href="/petrkeil/Blog/network/members" class="social-count"
       aria-label="130 users forked this repository">
      130
    </a>
  </li>
</ul>

      <h1 class="public ">
  <svg class="octicon octicon-repo" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
  <span class="author" itemprop="author"><a class="url fn" rel="author" href="/petrkeil">petrkeil</a></span><!--
--><span class="path-divider">/</span><!--
--><strong itemprop="name"><a data-pjax="#js-repo-pjax-container" href="/petrkeil/Blog">Blog</a></strong>

</h1>

    </div>

<nav class="reponav js-repo-nav js-sidenav-container-pjax container"
     itemscope
     itemtype="http://schema.org/BreadcrumbList"
     role="navigation"
     data-pjax="#js-repo-pjax-container">

  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
    <a class="js-selected-navigation-item selected reponav-item" itemprop="url" data-hotkey="g c" data-selected-links="repo_source repo_downloads repo_commits repo_releases repo_tags repo_branches repo_packages /petrkeil/Blog" href="/petrkeil/Blog">
      <svg class="octicon octicon-code" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M9.5 3L8 4.5 11.5 8 8 11.5 9.5 13 14 8 9.5 3zm-5 0L0 8l4.5 5L6 11.5 2.5 8 6 4.5 4.5 3z"/></svg>
      <span itemprop="name">Code</span>
      <meta itemprop="position" content="1">
</a>  </span>

    <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
      <a itemprop="url" data-hotkey="g i" class="js-selected-navigation-item reponav-item" data-selected-links="repo_issues repo_labels repo_milestones /petrkeil/Blog/issues" href="/petrkeil/Blog/issues">
        <svg class="octicon octicon-issue-opened" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7 2.3c3.14 0 5.7 2.56 5.7 5.7s-2.56 5.7-5.7 5.7A5.71 5.71 0 0 1 1.3 8c0-3.14 2.56-5.7 5.7-5.7zM7 1C3.14 1 0 4.14 0 8s3.14 7 7 7 7-3.14 7-7-3.14-7-7-7zm1 3H6v5h2V4zm0 6H6v2h2v-2z"/></svg>
        <span itemprop="name">Issues</span>
        <span class="Counter">1</span>
        <meta itemprop="position" content="2">
</a>    </span>

  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
    <a data-hotkey="g p" itemprop="url" class="js-selected-navigation-item reponav-item" data-selected-links="repo_pulls checks /petrkeil/Blog/pulls" href="/petrkeil/Blog/pulls">
      <svg class="octicon octicon-git-pull-request" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 11.28V5c-.03-.78-.34-1.47-.94-2.06C9.46 2.35 8.78 2.03 8 2H7V0L4 3l3 3V4h1c.27.02.48.11.69.31.21.2.3.42.31.69v6.28A1.993 1.993 0 0 0 10 15a1.993 1.993 0 0 0 1-3.72zm-1 2.92c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zM4 3c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v6.56A1.993 1.993 0 0 0 2 15a1.993 1.993 0 0 0 1-3.72V4.72c.59-.34 1-.98 1-1.72zm-.8 10c0 .66-.55 1.2-1.2 1.2-.65 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
      <span itemprop="name">Pull requests</span>
      <span class="Counter">0</span>
      <meta itemprop="position" content="3">
</a>  </span>

    <a data-hotkey="g b" class="js-selected-navigation-item reponav-item" data-selected-links="repo_projects new_repo_project repo_project /petrkeil/Blog/projects" href="/petrkeil/Blog/projects">
      <svg class="octicon octicon-project" viewBox="0 0 15 16" version="1.1" width="15" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
      Projects
      <span class="Counter" >0</span>
</a>

    <a class="js-selected-navigation-item reponav-item" data-hotkey="g w" data-selected-links="repo_wiki /petrkeil/Blog/wiki" href="/petrkeil/Blog/wiki">
      <svg class="octicon octicon-book" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M3 5h4v1H3V5zm0 3h4V7H3v1zm0 2h4V9H3v1zm11-5h-4v1h4V5zm0 2h-4v1h4V7zm0 2h-4v1h4V9zm2-6v9c0 .55-.45 1-1 1H9.5l-1 1-1-1H2c-.55 0-1-.45-1-1V3c0-.55.45-1 1-1h5.5l1 1 1-1H15c.55 0 1 .45 1 1zm-8 .5L7.5 3H2v9h6V3.5zm7-.5H9.5l-.5.5V12h6V3z"/></svg>
      Wiki
</a>
  <a class="js-selected-navigation-item reponav-item" data-selected-links="repo_graphs repo_contributors dependency_graph pulse /petrkeil/Blog/pulse" href="/petrkeil/Blog/pulse">
    <svg class="octicon octicon-graph" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M16 14v1H0V0h1v14h15zM5 13H3V8h2v5zm4 0H7V3h2v10zm4 0h-2V6h2v7z"/></svg>
    Insights
</a>

</nav>

  </div>

<div class="container new-discussion-timeline experiment-repo-nav  ">
  <div class="repository-content ">

  <a class="d-none js-permalink-shortcut" data-hotkey="y" href="/petrkeil/Blog/blob/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.tex">Permalink</a>

  <!-- blob contrib key: blob_contributors:v21:95c861515a089144992f835be9c5e7ee -->

  <div class="file-navigation">

<div class="select-menu branch-select-menu js-menu-container js-select-menu float-left">
  <button class=" btn btn-sm select-menu-button js-menu-target css-truncate" data-hotkey="w"

    type="button" aria-label="Switch branches or tags" aria-expanded="false" aria-haspopup="true">
      <i>Branch:</i>
      <span class="js-select-button css-truncate-target">master</span>
  </button>

  <div class="select-menu-modal-holder js-menu-content js-navigation-container" data-pjax>

    <div class="select-menu-modal">
      <div class="select-menu-header">
        <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
        <span class="select-menu-title">Switch branches/tags</span>
      </div>

      <div class="select-menu-filters">
        <div class="select-menu-text-filter">
          <input type="text" aria-label="Filter branches/tags" id="context-commitish-filter-field" class="form-control js-filterable-field js-navigation-enable" placeholder="Filter branches/tags">
        </div>
        <div class="select-menu-tabs">
          <ul>
            <li class="select-menu-tab">
              <a href="#" data-tab-filter="branches" data-filter-placeholder="Filter branches/tags" class="js-select-menu-tab" role="tab">Branches</a>
            </li>
            <li class="select-menu-tab">
              <a href="#" data-tab-filter="tags" data-filter-placeholder="Find a tag…" class="js-select-menu-tab" role="tab">Tags</a>
            </li>
          </ul>
        </div>
      </div>

      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="branches" role="menu">

        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">

            <a class="select-menu-item js-navigation-item js-navigation-open selected"
               href="/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.tex"
               data-name="master"
               data-skip-pjax="true"
               rel="nofollow">
              <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
              <span class="select-menu-item-text css-truncate-target js-select-menu-filter-text">
                master
              </span>
            </a>
        </div>

          <div class="select-menu-no-results">Nothing to show</div>
      </div>

      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="tags">
        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">

        </div>

        <div class="select-menu-no-results">Nothing to show</div>
      </div>

    </div>
  </div>
</div>

    <div class="BtnGroup float-right">
      <a href="/petrkeil/Blog/find/master"
            class="js-pjax-capture-input btn btn-sm BtnGroup-item"
            data-pjax
            data-hotkey="t">
        Find file
      </a>
      <clipboard-copy for="blob-path" class="btn btn-sm BtnGroup-item">
        Copy path
      </clipboard-copy>
    </div>
    <div id="blob-path" class="breadcrumb">
      <span class="repo-root js-repo-root"><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog"><span>Blog</span></a></span></span><span class="separator">/</span><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog/tree/master/2015_03_12_R_ms_template"><span>2015_03_12_R_ms_template</span></a></span><span class="separator">/</span><strong class="final-path">manuscript_template.tex</strong>
    </div>
  </div>

  <div class="commit-tease">
      <span class="float-right">
        <a class="commit-tease-sha" href="/petrkeil/Blog/commit/bdb85252abceb5ef19a438325c387cd941fa8e59" data-pjax>
          bdb8525
        </a>
        <relative-time datetime="2017-03-27T15:15:23Z">Mar 27, 2017</relative-time>
      </span>
      <div>
        <a rel="author" data-skip-pjax="true" data-hovercard-user-id="5421227" data-octo-click="hovercard-link-click" data-octo-dimensions="link_type:self" href="/petrkeil"><img class="avatar" src="https://avatars2.githubusercontent.com/u/5421227?s=40&amp;v=4" width="20" height="20" alt="@petrkeil" /></a>
        <a class="user-mention" rel="author" data-hovercard-user-id="5421227" data-octo-click="hovercard-link-click" data-octo-dimensions="link_type:self" href="/petrkeil">petrkeil</a>
          <a data-pjax="true" title="single-point ANOVA inference" class="message" href="/petrkeil/Blog/commit/bdb85252abceb5ef19a438325c387cd941fa8e59">single-point ANOVA inference</a>
      </div>

    <div class="commit-tease-contributors">

<details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark float-left mr-2" id="blob_contributors_box">
  <summary class="btn-link" aria-haspopup="dialog"  >

    <span><strong>1</strong> contributor</span>
  </summary>
  <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast " aria-label="Users who have contributed to this file">
    <div class="Box-header">
      <button class="Box-btn-octicon btn-octicon float-right" type="button" aria-label="Close dialog" data-close-dialog>
        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
      </button>
      <h3 class="Box-title">Users who have contributed to this file</h3>
    </div>

        <ul class="list-style-none overflow-auto">
            <li class="Box-row">
              <a class="link-gray-dark no-underline" href="/petrkeil">
                <img class="avatar mr-2" alt="" src="https://avatars2.githubusercontent.com/u/5421227?s=40&amp;v=4" width="20" height="20" />
                petrkeil
</a>            </li>
        </ul>

  </details-dialog>
</details>

    </div>
  </div>

  <div class="file">
    <div class="file-header">
  <div class="file-actions">

    <div class="BtnGroup">
      <a id="raw-url" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/raw/master/2015_03_12_R_ms_template/manuscript_template.tex">Raw</a>
        <a class="btn btn-sm js-update-url-with-hash BtnGroup-item" data-hotkey="b" href="/petrkeil/Blog/blame/master/2015_03_12_R_ms_template/manuscript_template.tex">Blame</a>
      <a rel="nofollow" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/commits/master/2015_03_12_R_ms_template/manuscript_template.tex">History</a>
    </div>

          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form js-update-url-with-hash" action="/petrkeil/Blog/edit/master/2015_03_12_R_ms_template/manuscript_template.tex" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="w+3hYqJjhuh93uZllWgA4JOlUpjHqPHPgW/C5pBTejUDA3OILy5ZqIwZtUEUGtGOPtTAfSXs33NAtsUeHSZSSA==" />
            <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
              aria-label="Fork this project and edit the file" data-hotkey="e" data-disable-with>
              <svg class="octicon octicon-pencil" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"/></svg>
            </button>
</form>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form" action="/petrkeil/Blog/delete/master/2015_03_12_R_ms_template/manuscript_template.tex" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="efKWsrgtSPI/V5DDU5bGP7EMhrQUES31G2ywFe2D7TzEbIKhujyGp7OMXBU/qR2PeGN1Pdxd256v9Z45qk+w1Q==" />
          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
            aria-label="Fork this project and delete the file" data-disable-with>
            <svg class="octicon octicon-trashcan" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"/></svg>
          </button>
</form>  </div>

  <div class="file-info">
      236 lines (198 sloc)
      <span class="file-info-divider"></span>
    8.71 KB
  </div>
</div>

  <div itemprop="text" class="blob-wrapper data type-tex">
      <table class="highlight tab-size js-file-line-container" data-tab-size="8">
      <tr>
        <td id="L1" class="blob-num js-line-number" data-line-number="1"></td>
        <td id="LC1" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\documentclass</span>[]{article}</td>
      </tr>
      <tr>
        <td id="L2" class="blob-num js-line-number" data-line-number="2"></td>
        <td id="LC2" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{lmodern}</td>
      </tr>
      <tr>
        <td id="L3" class="blob-num js-line-number" data-line-number="3"></td>
        <td id="LC3" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{amssymb,amsmath}</td>
      </tr>
      <tr>
        <td id="L4" class="blob-num js-line-number" data-line-number="4"></td>
        <td id="LC4" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{ifxetex,ifluatex}</td>
      </tr>
      <tr>
        <td id="L5" class="blob-num js-line-number" data-line-number="5"></td>
        <td id="LC5" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{fixltx2e} <span class="pl-c"><span class="pl-c">%</span> provides \textsubscript</span></td>
      </tr>
      <tr>
        <td id="L6" class="blob-num js-line-number" data-line-number="6"></td>
        <td id="LC6" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifnum</span> 0<span class="pl-c1">\ifxetex</span> 1<span class="pl-k">\fi</span><span class="pl-c1">\ifluatex</span> 1<span class="pl-k">\fi</span>=0 <span class="pl-c"><span class="pl-c">%</span> if pdftex</span></td>
      </tr>
      <tr>
        <td id="L7" class="blob-num js-line-number" data-line-number="7"></td>
        <td id="LC7" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\usepackage</span>[T1]{fontenc}</td>
      </tr>
      <tr>
        <td id="L8" class="blob-num js-line-number" data-line-number="8"></td>
        <td id="LC8" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\usepackage</span>[utf8]{inputenc}</td>
      </tr>
      <tr>
        <td id="L9" class="blob-num js-line-number" data-line-number="9"></td>
        <td id="LC9" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\else</span> <span class="pl-c"><span class="pl-c">%</span> if luatex or xelatex</span></td>
      </tr>
      <tr>
        <td id="L10" class="blob-num js-line-number" data-line-number="10"></td>
        <td id="LC10" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\ifxetex</span></td>
      </tr>
      <tr>
        <td id="L11" class="blob-num js-line-number" data-line-number="11"></td>
        <td id="LC11" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\usepackage</span>{mathspec}</td>
      </tr>
      <tr>
        <td id="L12" class="blob-num js-line-number" data-line-number="12"></td>
        <td id="LC12" class="blob-code blob-code-inner js-file-line">  <span class="pl-k">\else</span></td>
      </tr>
      <tr>
        <td id="L13" class="blob-num js-line-number" data-line-number="13"></td>
        <td id="LC13" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\usepackage</span>{fontspec}</td>
      </tr>
      <tr>
        <td id="L14" class="blob-num js-line-number" data-line-number="14"></td>
        <td id="LC14" class="blob-code blob-code-inner js-file-line">  <span class="pl-k">\fi</span></td>
      </tr>
      <tr>
        <td id="L15" class="blob-num js-line-number" data-line-number="15"></td>
        <td id="LC15" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\defaultfontfeatures</span>{Ligatures=TeX,Scale=MatchLowercase}</td>
      </tr>
      <tr>
        <td id="L16" class="blob-num js-line-number" data-line-number="16"></td>
        <td id="LC16" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
      </tr>
      <tr>
        <td id="L17" class="blob-num js-line-number" data-line-number="17"></td>
        <td id="LC17" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> use upquote if available, for straight quotes in verbatim environments</span></td>
      </tr>
      <tr>
        <td id="L18" class="blob-num js-line-number" data-line-number="18"></td>
        <td id="LC18" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{upquote.sty}{<span class="pl-c1">\usepackage</span>{upquote}}{}</td>
      </tr>
      <tr>
        <td id="L19" class="blob-num js-line-number" data-line-number="19"></td>
        <td id="LC19" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> use microtype if available</span></td>
      </tr>
      <tr>
        <td id="L20" class="blob-num js-line-number" data-line-number="20"></td>
        <td id="LC20" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{microtype.sty}{<span class="pl-c"><span class="pl-c">%</span></span></td>
      </tr>
      <tr>
        <td id="L21" class="blob-num js-line-number" data-line-number="21"></td>
        <td id="LC21" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{microtype}</td>
      </tr>
      <tr>
        <td id="L22" class="blob-num js-line-number" data-line-number="22"></td>
        <td id="LC22" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\UseMicrotypeSet</span>[protrusion]{basicmath} <span class="pl-c"><span class="pl-c">%</span> disable protrusion for tt fonts</span></td>
      </tr>
      <tr>
        <td id="L23" class="blob-num js-line-number" data-line-number="23"></td>
        <td id="LC23" class="blob-code blob-code-inner js-file-line">}{}</td>
      </tr>
      <tr>
        <td id="L24" class="blob-num js-line-number" data-line-number="24"></td>
        <td id="LC24" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>[margin=1in]{geometry}</td>
      </tr>
      <tr>
        <td id="L25" class="blob-num js-line-number" data-line-number="25"></td>
        <td id="LC25" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{hyperref}</td>
      </tr>
      <tr>
        <td id="L26" class="blob-num js-line-number" data-line-number="26"></td>
        <td id="LC26" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypersetup</span>{unicode=true,</td>
      </tr>
      <tr>
        <td id="L27" class="blob-num js-line-number" data-line-number="27"></td>
        <td id="LC27" class="blob-code blob-code-inner js-file-line">            pdftitle={Template for writing scientific papers in R markdown},</td>
      </tr>
      <tr>
        <td id="L28" class="blob-num js-line-number" data-line-number="28"></td>
        <td id="LC28" class="blob-code blob-code-inner js-file-line">            pdfauthor={Petr Keil, pkeil@seznam.cz},</td>
      </tr>
      <tr>
        <td id="L29" class="blob-num js-line-number" data-line-number="29"></td>
        <td id="LC29" class="blob-code blob-code-inner js-file-line">            pdfborder={0 0 0},</td>
      </tr>
      <tr>
        <td id="L30" class="blob-num js-line-number" data-line-number="30"></td>
        <td id="LC30" class="blob-code blob-code-inner js-file-line">            breaklinks=true}</td>
      </tr>
      <tr>
        <td id="L31" class="blob-num js-line-number" data-line-number="31"></td>
        <td id="LC31" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\urlstyle</span>{same}  <span class="pl-c"><span class="pl-c">%</span> don&#39;t use monospace font for urls</span></td>
      </tr>
      <tr>
        <td id="L32" class="blob-num js-line-number" data-line-number="32"></td>
        <td id="LC32" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{longtable,booktabs}</td>
      </tr>
      <tr>
        <td id="L33" class="blob-num js-line-number" data-line-number="33"></td>
        <td id="LC33" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{graphicx,grffile}</td>
      </tr>
      <tr>
        <td id="L34" class="blob-num js-line-number" data-line-number="34"></td>
        <td id="LC34" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\makeatletter</span></td>
      </tr>
      <tr>
        <td id="L35" class="blob-num js-line-number" data-line-number="35"></td>
        <td id="LC35" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\maxwidth</span>{<span class="pl-k">\ifdim</span><span class="pl-c1">\Gin@nat@width</span>&gt;<span class="pl-c1">\linewidth\linewidth</span><span class="pl-k">\else</span><span class="pl-c1">\Gin@nat@width</span><span class="pl-k">\fi</span>}</td>
      </tr>
      <tr>
        <td id="L36" class="blob-num js-line-number" data-line-number="36"></td>
        <td id="LC36" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\maxheight</span>{<span class="pl-k">\ifdim</span><span class="pl-c1">\Gin@nat@height</span>&gt;<span class="pl-c1">\textheight\textheight</span><span class="pl-k">\else</span><span class="pl-c1">\Gin@nat@height</span><span class="pl-k">\fi</span>}</td>
      </tr>
      <tr>
        <td id="L37" class="blob-num js-line-number" data-line-number="37"></td>
        <td id="LC37" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\makeatother</span></td>
      </tr>
      <tr>
        <td id="L38" class="blob-num js-line-number" data-line-number="38"></td>
        <td id="LC38" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Scale images if necessary, so that they will not overflow the page</span></td>
      </tr>
      <tr>
        <td id="L39" class="blob-num js-line-number" data-line-number="39"></td>
        <td id="LC39" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> margins by default, and it is still possible to overwrite the defaults</span></td>
      </tr>
      <tr>
        <td id="L40" class="blob-num js-line-number" data-line-number="40"></td>
        <td id="LC40" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> using explicit options in \includegraphics[width, height, ...]{}</span></td>
      </tr>
      <tr>
        <td id="L41" class="blob-num js-line-number" data-line-number="41"></td>
        <td id="LC41" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setkeys</span>{Gin}{width=<span class="pl-c1">\maxwidth</span>,height=<span class="pl-c1">\maxheight</span>,keepaspectratio}</td>
      </tr>
      <tr>
        <td id="L42" class="blob-num js-line-number" data-line-number="42"></td>
        <td id="LC42" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{parskip.sty}{<span class="pl-c"><span class="pl-c">%</span></span></td>
      </tr>
      <tr>
        <td id="L43" class="blob-num js-line-number" data-line-number="43"></td>
        <td id="LC43" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{parskip}</td>
      </tr>
      <tr>
        <td id="L44" class="blob-num js-line-number" data-line-number="44"></td>
        <td id="LC44" class="blob-code blob-code-inner js-file-line">}{<span class="pl-c"><span class="pl-c">%</span> else</span></td>
      </tr>
      <tr>
        <td id="L45" class="blob-num js-line-number" data-line-number="45"></td>
        <td id="LC45" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\parindent</span>}{0pt}</td>
      </tr>
      <tr>
        <td id="L46" class="blob-num js-line-number" data-line-number="46"></td>
        <td id="LC46" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\parskip</span>}{6pt plus 2pt minus 1pt}</td>
      </tr>
      <tr>
        <td id="L47" class="blob-num js-line-number" data-line-number="47"></td>
        <td id="LC47" class="blob-code blob-code-inner js-file-line">}</td>
      </tr>
      <tr>
        <td id="L48" class="blob-num js-line-number" data-line-number="48"></td>
        <td id="LC48" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\emergencystretch</span>}{3em}  <span class="pl-c"><span class="pl-c">%</span> prevent overfull lines</span></td>
      </tr>
      <tr>
        <td id="L49" class="blob-num js-line-number" data-line-number="49"></td>
        <td id="LC49" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\providecommand</span>{<span class="pl-c1">\tightlist</span>}{<span class="pl-c"><span class="pl-c">%</span></span></td>
      </tr>
      <tr>
        <td id="L50" class="blob-num js-line-number" data-line-number="50"></td>
        <td id="LC50" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\setlength</span>{<span class="pl-c1">\itemsep</span>}{0pt}<span class="pl-c1">\setlength</span>{<span class="pl-c1">\parskip</span>}{0pt}}</td>
      </tr>
      <tr>
        <td id="L51" class="blob-num js-line-number" data-line-number="51"></td>
        <td id="LC51" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setcounter</span>{secnumdepth}{5}</td>
      </tr>
      <tr>
        <td id="L52" class="blob-num js-line-number" data-line-number="52"></td>
        <td id="LC52" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Redefines (sub)paragraphs to behave more like sections</span></td>
      </tr>
      <tr>
        <td id="L53" class="blob-num js-line-number" data-line-number="53"></td>
        <td id="LC53" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifx</span><span class="pl-c1">\paragraph\undefined</span><span class="pl-k">\else</span></td>
      </tr>
      <tr>
        <td id="L54" class="blob-num js-line-number" data-line-number="54"></td>
        <td id="LC54" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\oldparagraph\paragraph</span></td>
      </tr>
      <tr>
        <td id="L55" class="blob-num js-line-number" data-line-number="55"></td>
        <td id="LC55" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\renewcommand</span>{<span class="pl-c1">\paragraph</span>}[1]{<span class="pl-c1">\oldparagraph</span>{#1}<span class="pl-c1">\mbox</span>{}}</td>
      </tr>
      <tr>
        <td id="L56" class="blob-num js-line-number" data-line-number="56"></td>
        <td id="LC56" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
      </tr>
      <tr>
        <td id="L57" class="blob-num js-line-number" data-line-number="57"></td>
        <td id="LC57" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifx</span><span class="pl-c1">\subparagraph\undefined</span><span class="pl-k">\else</span></td>
      </tr>
      <tr>
        <td id="L58" class="blob-num js-line-number" data-line-number="58"></td>
        <td id="LC58" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\oldsubparagraph\subparagraph</span></td>
      </tr>
      <tr>
        <td id="L59" class="blob-num js-line-number" data-line-number="59"></td>
        <td id="LC59" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\renewcommand</span>{<span class="pl-c1">\subparagraph</span>}[1]{<span class="pl-c1">\oldsubparagraph</span>{#1}<span class="pl-c1">\mbox</span>{}}</td>
      </tr>
      <tr>
        <td id="L60" class="blob-num js-line-number" data-line-number="60"></td>
        <td id="LC60" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
      </tr>
      <tr>
        <td id="L61" class="blob-num js-line-number" data-line-number="61"></td>
        <td id="LC61" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L62" class="blob-num js-line-number" data-line-number="62"></td>
        <td id="LC62" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span>%% Use protect on footnotes to avoid problems with footnotes in titles</span></td>
      </tr>
      <tr>
        <td id="L63" class="blob-num js-line-number" data-line-number="63"></td>
        <td id="LC63" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\rmarkdownfootnote\footnote</span><span class="pl-c"><span class="pl-c">%</span></span></td>
      </tr>
      <tr>
        <td id="L64" class="blob-num js-line-number" data-line-number="64"></td>
        <td id="LC64" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\footnote</span>{<span class="pl-c1">\protect\rmarkdownfootnote</span>}</td>
      </tr>
      <tr>
        <td id="L65" class="blob-num js-line-number" data-line-number="65"></td>
        <td id="LC65" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L66" class="blob-num js-line-number" data-line-number="66"></td>
        <td id="LC66" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span>%% Change title format to be more compact</span></td>
      </tr>
      <tr>
        <td id="L67" class="blob-num js-line-number" data-line-number="67"></td>
        <td id="LC67" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{titling}</td>
      </tr>
      <tr>
        <td id="L68" class="blob-num js-line-number" data-line-number="68"></td>
        <td id="LC68" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L69" class="blob-num js-line-number" data-line-number="69"></td>
        <td id="LC69" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Create subtitle command for use in maketitle</span></td>
      </tr>
      <tr>
        <td id="L70" class="blob-num js-line-number" data-line-number="70"></td>
        <td id="LC70" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\newcommand</span>{<span class="pl-c1">\subtitle</span>}[1]{</td>
      </tr>
      <tr>
        <td id="L71" class="blob-num js-line-number" data-line-number="71"></td>
        <td id="LC71" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\posttitle</span>{</td>
      </tr>
      <tr>
        <td id="L72" class="blob-num js-line-number" data-line-number="72"></td>
        <td id="LC72" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\begin</span>{center}<span class="pl-c1">\large</span>#1<span class="pl-c1">\end</span>{center}</td>
      </tr>
      <tr>
        <td id="L73" class="blob-num js-line-number" data-line-number="73"></td>
        <td id="LC73" class="blob-code blob-code-inner js-file-line">    }</td>
      </tr>
      <tr>
        <td id="L74" class="blob-num js-line-number" data-line-number="74"></td>
        <td id="LC74" class="blob-code blob-code-inner js-file-line">}</td>
      </tr>
      <tr>
        <td id="L75" class="blob-num js-line-number" data-line-number="75"></td>
        <td id="LC75" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L76" class="blob-num js-line-number" data-line-number="76"></td>
        <td id="LC76" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\droptitle</span>}{-2em}</td>
      </tr>
      <tr>
        <td id="L77" class="blob-num js-line-number" data-line-number="77"></td>
        <td id="LC77" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\title</span>{Template for writing scientific papers in R markdown}</td>
      </tr>
      <tr>
        <td id="L78" class="blob-num js-line-number" data-line-number="78"></td>
        <td id="LC78" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\pretitle</span>{<span class="pl-c1">\vspace</span>{<span class="pl-c1">\droptitle</span>}<span class="pl-c1">\centering\huge</span>}</td>
      </tr>
      <tr>
        <td id="L79" class="blob-num js-line-number" data-line-number="79"></td>
        <td id="LC79" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\posttitle</span>{<span class="pl-c1">\par</span>}</td>
      </tr>
      <tr>
        <td id="L80" class="blob-num js-line-number" data-line-number="80"></td>
        <td id="LC80" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\author</span>{Petr Keil, <span class="pl-c1">\href</span>{mailto:pkeil@seznam.cz}{<span class="pl-c1">\nolinkurl</span>{pkeil@seznam.cz}}}</td>
      </tr>
      <tr>
        <td id="L81" class="blob-num js-line-number" data-line-number="81"></td>
        <td id="LC81" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\preauthor</span>{<span class="pl-c1">\centering\large\emph</span>}</td>
      </tr>
      <tr>
        <td id="L82" class="blob-num js-line-number" data-line-number="82"></td>
        <td id="LC82" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\postauthor</span>{<span class="pl-c1">\par</span>}</td>
      </tr>
      <tr>
        <td id="L83" class="blob-num js-line-number" data-line-number="83"></td>
        <td id="LC83" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\predate</span>{<span class="pl-c1">\centering\large\emph</span>}</td>
      </tr>
      <tr>
        <td id="L84" class="blob-num js-line-number" data-line-number="84"></td>
        <td id="LC84" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\postdate</span>{<span class="pl-c1">\par</span>}</td>
      </tr>
      <tr>
        <td id="L85" class="blob-num js-line-number" data-line-number="85"></td>
        <td id="LC85" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\date</span>{11/1/2015}</td>
      </tr>
      <tr>
        <td id="L86" class="blob-num js-line-number" data-line-number="86"></td>
        <td id="LC86" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L87" class="blob-num js-line-number" data-line-number="87"></td>
        <td id="LC87" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L88" class="blob-num js-line-number" data-line-number="88"></td>
        <td id="LC88" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{document}</td>
      </tr>
      <tr>
        <td id="L89" class="blob-num js-line-number" data-line-number="89"></td>
        <td id="LC89" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\maketitle</span></td>
      </tr>
      <tr>
        <td id="L90" class="blob-num js-line-number" data-line-number="90"></td>
        <td id="LC90" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L91" class="blob-num js-line-number" data-line-number="91"></td>
        <td id="LC91" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Abstract}<span class="pl-c1">\label</span>{abstract}</td>
      </tr>
      <tr>
        <td id="L92" class="blob-num js-line-number" data-line-number="92"></td>
        <td id="LC92" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L93" class="blob-num js-line-number" data-line-number="93"></td>
        <td id="LC93" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\emph</span>{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel</td>
      </tr>
      <tr>
        <td id="L94" class="blob-num js-line-number" data-line-number="94"></td>
        <td id="LC94" class="blob-code blob-code-inner js-file-line">erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet</td>
      </tr>
      <tr>
        <td id="L95" class="blob-num js-line-number" data-line-number="95"></td>
        <td id="LC95" class="blob-code blob-code-inner js-file-line">argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
      </tr>
      <tr>
        <td id="L96" class="blob-num js-line-number" data-line-number="96"></td>
        <td id="LC96" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando</td>
      </tr>
      <tr>
        <td id="L97" class="blob-num js-line-number" data-line-number="97"></td>
        <td id="LC97" class="blob-code blob-code-inner js-file-line">mei.}</td>
      </tr>
      <tr>
        <td id="L98" class="blob-num js-line-number" data-line-number="98"></td>
        <td id="LC98" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L99" class="blob-num js-line-number" data-line-number="99"></td>
        <td id="LC99" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Introduction}<span class="pl-c1">\label</span>{introduction}</td>
      </tr>
      <tr>
        <td id="L100" class="blob-num js-line-number" data-line-number="100"></td>
        <td id="LC100" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L101" class="blob-num js-line-number" data-line-number="101"></td>
        <td id="LC101" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
      </tr>
      <tr>
        <td id="L102" class="blob-num js-line-number" data-line-number="102"></td>
        <td id="LC102" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
      </tr>
      <tr>
        <td id="L103" class="blob-num js-line-number" data-line-number="103"></td>
        <td id="LC103" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
      </tr>
      <tr>
        <td id="L104" class="blob-num js-line-number" data-line-number="104"></td>
        <td id="LC104" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
      </tr>
      <tr>
        <td id="L105" class="blob-num js-line-number" data-line-number="105"></td>
        <td id="LC105" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L106" class="blob-num js-line-number" data-line-number="106"></td>
        <td id="LC106" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
      </tr>
      <tr>
        <td id="L107" class="blob-num js-line-number" data-line-number="107"></td>
        <td id="LC107" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
      </tr>
      <tr>
        <td id="L108" class="blob-num js-line-number" data-line-number="108"></td>
        <td id="LC108" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
      </tr>
      <tr>
        <td id="L109" class="blob-num js-line-number" data-line-number="109"></td>
        <td id="LC109" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
      </tr>
      <tr>
        <td id="L110" class="blob-num js-line-number" data-line-number="110"></td>
        <td id="LC110" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
      </tr>
      <tr>
        <td id="L111" class="blob-num js-line-number" data-line-number="111"></td>
        <td id="LC111" class="blob-code blob-code-inner js-file-line">conceptam.</td>
      </tr>
      <tr>
        <td id="L112" class="blob-num js-line-number" data-line-number="112"></td>
        <td id="LC112" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L113" class="blob-num js-line-number" data-line-number="113"></td>
        <td id="LC113" class="blob-code blob-code-inner js-file-line">Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit</td>
      </tr>
      <tr>
        <td id="L114" class="blob-num js-line-number" data-line-number="114"></td>
        <td id="LC114" class="blob-code blob-code-inner js-file-line">quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos</td>
      </tr>
      <tr>
        <td id="L115" class="blob-num js-line-number" data-line-number="115"></td>
        <td id="LC115" class="blob-code blob-code-inner js-file-line">ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes</td>
      </tr>
      <tr>
        <td id="L116" class="blob-num js-line-number" data-line-number="116"></td>
        <td id="LC116" class="blob-code blob-code-inner js-file-line">percipitur at vis. Numquam similique in per, te quo saepe utroque</td>
      </tr>
      <tr>
        <td id="L117" class="blob-num js-line-number" data-line-number="117"></td>
        <td id="LC117" class="blob-code blob-code-inner js-file-line">pericula.</td>
      </tr>
      <tr>
        <td id="L118" class="blob-num js-line-number" data-line-number="118"></td>
        <td id="LC118" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L119" class="blob-num js-line-number" data-line-number="119"></td>
        <td id="LC119" class="blob-code blob-code-inner js-file-line">Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo</td>
      </tr>
      <tr>
        <td id="L120" class="blob-num js-line-number" data-line-number="120"></td>
        <td id="LC120" class="blob-code blob-code-inner js-file-line">vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque</td>
      </tr>
      <tr>
        <td id="L121" class="blob-num js-line-number" data-line-number="121"></td>
        <td id="LC121" class="blob-code blob-code-inner js-file-line">gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne</td>
      </tr>
      <tr>
        <td id="L122" class="blob-num js-line-number" data-line-number="122"></td>
        <td id="LC122" class="blob-code blob-code-inner js-file-line">suas latine vix, eos oblique sanctus pertinax cu.</td>
      </tr>
      <tr>
        <td id="L123" class="blob-num js-line-number" data-line-number="123"></td>
        <td id="LC123" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L124" class="blob-num js-line-number" data-line-number="124"></td>
        <td id="LC124" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Methods}<span class="pl-c1">\label</span>{methods}</td>
      </tr>
      <tr>
        <td id="L125" class="blob-num js-line-number" data-line-number="125"></td>
        <td id="LC125" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L126" class="blob-num js-line-number" data-line-number="126"></td>
        <td id="LC126" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
      </tr>
      <tr>
        <td id="L127" class="blob-num js-line-number" data-line-number="127"></td>
        <td id="LC127" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
      </tr>
      <tr>
        <td id="L128" class="blob-num js-line-number" data-line-number="128"></td>
        <td id="LC128" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
      </tr>
      <tr>
        <td id="L129" class="blob-num js-line-number" data-line-number="129"></td>
        <td id="LC129" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
      </tr>
      <tr>
        <td id="L130" class="blob-num js-line-number" data-line-number="130"></td>
        <td id="LC130" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L131" class="blob-num js-line-number" data-line-number="131"></td>
        <td id="LC131" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
      </tr>
      <tr>
        <td id="L132" class="blob-num js-line-number" data-line-number="132"></td>
        <td id="LC132" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
      </tr>
      <tr>
        <td id="L133" class="blob-num js-line-number" data-line-number="133"></td>
        <td id="LC133" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
      </tr>
      <tr>
        <td id="L134" class="blob-num js-line-number" data-line-number="134"></td>
        <td id="LC134" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
      </tr>
      <tr>
        <td id="L135" class="blob-num js-line-number" data-line-number="135"></td>
        <td id="LC135" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
      </tr>
      <tr>
        <td id="L136" class="blob-num js-line-number" data-line-number="136"></td>
        <td id="LC136" class="blob-code blob-code-inner js-file-line">conceptam.</td>
      </tr>
      <tr>
        <td id="L137" class="blob-num js-line-number" data-line-number="137"></td>
        <td id="LC137" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L138" class="blob-num js-line-number" data-line-number="138"></td>
        <td id="LC138" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Equations}<span class="pl-c1">\label</span>{equations}</td>
      </tr>
      <tr>
        <td id="L139" class="blob-num js-line-number" data-line-number="139"></td>
        <td id="LC139" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L140" class="blob-num js-line-number" data-line-number="140"></td>
        <td id="LC140" class="blob-code blob-code-inner js-file-line">The deterministic part of the model is defined by this <span class="pl-c1">\textbf</span>{in-line</td>
      </tr>
      <tr>
        <td id="L141" class="blob-num js-line-number" data-line-number="141"></td>
        <td id="LC141" class="blob-code blob-code-inner js-file-line">equation} as <span class="pl-cce">\(</span><span class="pl-c1">\mu</span>_i = <span class="pl-c1">\beta</span>_0 + <span class="pl-c1">\beta</span>_1x<span class="pl-cce">\)</span>, and the stochastic part by</td>
      </tr>
      <tr>
        <td id="L142" class="blob-num js-line-number" data-line-number="142"></td>
        <td id="LC142" class="blob-code blob-code-inner js-file-line">the <span class="pl-c1">\textbf</span>{centered equation}:</td>
      </tr>
      <tr>
        <td id="L143" class="blob-num js-line-number" data-line-number="143"></td>
        <td id="LC143" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L144" class="blob-num js-line-number" data-line-number="144"></td>
        <td id="LC144" class="blob-code blob-code-inner js-file-line"><span class="pl-cce">\[</span> <span class="pl-c1">\frac</span>{1}{<span class="pl-c1">\sqrt</span>{2<span class="pl-c1">\pi</span>}<span class="pl-c1">\sigma</span>}e^{-(x-<span class="pl-c1">\mu</span>_i)^2/(2<span class="pl-c1">\sigma</span>^2)} <span class="pl-cce">\]</span></td>
      </tr>
      <tr>
        <td id="L145" class="blob-num js-line-number" data-line-number="145"></td>
        <td id="LC145" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L146" class="blob-num js-line-number" data-line-number="146"></td>
        <td id="LC146" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Tables}<span class="pl-c1">\label</span>{tables}</td>
      </tr>
      <tr>
        <td id="L147" class="blob-num js-line-number" data-line-number="147"></td>
        <td id="LC147" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L148" class="blob-num js-line-number" data-line-number="148"></td>
        <td id="LC148" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{longtable}[]{@{}lrrrr@{}}</td>
      </tr>
      <tr>
        <td id="L149" class="blob-num js-line-number" data-line-number="149"></td>
        <td id="LC149" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\caption</span>{This is a GLM summary table.}<span class="pl-c1">\tabularnewline</span></td>
      </tr>
      <tr>
        <td id="L150" class="blob-num js-line-number" data-line-number="150"></td>
        <td id="LC150" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\toprule</span></td>
      </tr>
      <tr>
        <td id="L151" class="blob-num js-line-number" data-line-number="151"></td>
        <td id="LC151" class="blob-code blob-code-inner js-file-line">&amp; Estimate &amp; Std. Error &amp; t value &amp;</td>
      </tr>
      <tr>
        <td id="L152" class="blob-num js-line-number" data-line-number="152"></td>
        <td id="LC152" class="blob-code blob-code-inner js-file-line">Pr(<span class="pl-c1">\textgreater</span>{}<span class="pl-c1">\textbar</span>{}t<span class="pl-c1">\textbar</span>{})<span class="pl-c1">\tabularnewline</span></td>
      </tr>
      <tr>
        <td id="L153" class="blob-num js-line-number" data-line-number="153"></td>
        <td id="LC153" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\midrule</span></td>
      </tr>
      <tr>
        <td id="L154" class="blob-num js-line-number" data-line-number="154"></td>
        <td id="LC154" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\endfirsthead</span></td>
      </tr>
      <tr>
        <td id="L155" class="blob-num js-line-number" data-line-number="155"></td>
        <td id="LC155" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\toprule</span></td>
      </tr>
      <tr>
        <td id="L156" class="blob-num js-line-number" data-line-number="156"></td>
        <td id="LC156" class="blob-code blob-code-inner js-file-line">&amp; Estimate &amp; Std. Error &amp; t value &amp;</td>
      </tr>
      <tr>
        <td id="L157" class="blob-num js-line-number" data-line-number="157"></td>
        <td id="LC157" class="blob-code blob-code-inner js-file-line">Pr(<span class="pl-c1">\textgreater</span>{}<span class="pl-c1">\textbar</span>{}t<span class="pl-c1">\textbar</span>{})<span class="pl-c1">\tabularnewline</span></td>
      </tr>
      <tr>
        <td id="L158" class="blob-num js-line-number" data-line-number="158"></td>
        <td id="LC158" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\midrule</span></td>
      </tr>
      <tr>
        <td id="L159" class="blob-num js-line-number" data-line-number="159"></td>
        <td id="LC159" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\endhead</span></td>
      </tr>
      <tr>
        <td id="L160" class="blob-num js-line-number" data-line-number="160"></td>
        <td id="LC160" class="blob-code blob-code-inner js-file-line">(Intercept) &amp; 0.05 &amp; 0.11 &amp; 0.46 &amp; 0.65<span class="pl-c1">\tabularnewline</span></td>
      </tr>
      <tr>
        <td id="L161" class="blob-num js-line-number" data-line-number="161"></td>
        <td id="LC161" class="blob-code blob-code-inner js-file-line">x &amp; 2.00 &amp; 0.12 &amp; 16.91 &amp; 0.00<span class="pl-c1">\tabularnewline</span></td>
      </tr>
      <tr>
        <td id="L162" class="blob-num js-line-number" data-line-number="162"></td>
        <td id="LC162" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\bottomrule</span></td>
      </tr>
      <tr>
        <td id="L163" class="blob-num js-line-number" data-line-number="163"></td>
        <td id="LC163" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{longtable}</td>
      </tr>
      <tr>
        <td id="L164" class="blob-num js-line-number" data-line-number="164"></td>
        <td id="LC164" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L165" class="blob-num js-line-number" data-line-number="165"></td>
        <td id="LC165" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Plots}<span class="pl-c1">\label</span>{plots}</td>
      </tr>
      <tr>
        <td id="L166" class="blob-num js-line-number" data-line-number="166"></td>
        <td id="LC166" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L167" class="blob-num js-line-number" data-line-number="167"></td>
        <td id="LC167" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{figure}[htbp]</td>
      </tr>
      <tr>
        <td id="L168" class="blob-num js-line-number" data-line-number="168"></td>
        <td id="LC168" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\centering</span></td>
      </tr>
      <tr>
        <td id="L169" class="blob-num js-line-number" data-line-number="169"></td>
        <td id="LC169" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\includegraphics</span>{manuscript_template_files/figure-latex/carDataPlot-1.pdf}</td>
      </tr>
      <tr>
        <td id="L170" class="blob-num js-line-number" data-line-number="170"></td>
        <td id="LC170" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\caption</span>{Relationship between x and y. The solid line is least-squares</td>
      </tr>
      <tr>
        <td id="L171" class="blob-num js-line-number" data-line-number="171"></td>
        <td id="LC171" class="blob-code blob-code-inner js-file-line">linear regression.}</td>
      </tr>
      <tr>
        <td id="L172" class="blob-num js-line-number" data-line-number="172"></td>
        <td id="LC172" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{figure}</td>
      </tr>
      <tr>
        <td id="L173" class="blob-num js-line-number" data-line-number="173"></td>
        <td id="LC173" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L174" class="blob-num js-line-number" data-line-number="174"></td>
        <td id="LC174" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Citations}<span class="pl-c1">\label</span>{citations}</td>
      </tr>
      <tr>
        <td id="L175" class="blob-num js-line-number" data-line-number="175"></td>
        <td id="LC175" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L176" class="blob-num js-line-number" data-line-number="176"></td>
        <td id="LC176" class="blob-code blob-code-inner js-file-line">The relationship was first described by Halpern <span class="pl-c1">\emph</span>{et al.} (2006).</td>
      </tr>
      <tr>
        <td id="L177" class="blob-num js-line-number" data-line-number="177"></td>
        <td id="LC177" class="blob-code blob-code-inner js-file-line">However, there are also opinions that the relationship is spurious (Keil</td>
      </tr>
      <tr>
        <td id="L178" class="blob-num js-line-number" data-line-number="178"></td>
        <td id="LC178" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\emph</span>{et al.} 2012). We used R for our calculations (R Core Team 2016),</td>
      </tr>
      <tr>
        <td id="L179" class="blob-num js-line-number" data-line-number="179"></td>
        <td id="LC179" class="blob-code blob-code-inner js-file-line">and we used package <span class="pl-c1">\texttt</span>{knitcitations} (Boettiger 2015) to make the</td>
      </tr>
      <tr>
        <td id="L180" class="blob-num js-line-number" data-line-number="180"></td>
        <td id="LC180" class="blob-code blob-code-inner js-file-line">bibliography.</td>
      </tr>
      <tr>
        <td id="L181" class="blob-num js-line-number" data-line-number="181"></td>
        <td id="LC181" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L182" class="blob-num js-line-number" data-line-number="182"></td>
        <td id="LC182" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Results and discussion}<span class="pl-c1">\label</span>{results-and-discussion}</td>
      </tr>
      <tr>
        <td id="L183" class="blob-num js-line-number" data-line-number="183"></td>
        <td id="LC183" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L184" class="blob-num js-line-number" data-line-number="184"></td>
        <td id="LC184" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
      </tr>
      <tr>
        <td id="L185" class="blob-num js-line-number" data-line-number="185"></td>
        <td id="LC185" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
      </tr>
      <tr>
        <td id="L186" class="blob-num js-line-number" data-line-number="186"></td>
        <td id="LC186" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
      </tr>
      <tr>
        <td id="L187" class="blob-num js-line-number" data-line-number="187"></td>
        <td id="LC187" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
      </tr>
      <tr>
        <td id="L188" class="blob-num js-line-number" data-line-number="188"></td>
        <td id="LC188" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L189" class="blob-num js-line-number" data-line-number="189"></td>
        <td id="LC189" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
      </tr>
      <tr>
        <td id="L190" class="blob-num js-line-number" data-line-number="190"></td>
        <td id="LC190" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
      </tr>
      <tr>
        <td id="L191" class="blob-num js-line-number" data-line-number="191"></td>
        <td id="LC191" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
      </tr>
      <tr>
        <td id="L192" class="blob-num js-line-number" data-line-number="192"></td>
        <td id="LC192" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
      </tr>
      <tr>
        <td id="L193" class="blob-num js-line-number" data-line-number="193"></td>
        <td id="LC193" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
      </tr>
      <tr>
        <td id="L194" class="blob-num js-line-number" data-line-number="194"></td>
        <td id="LC194" class="blob-code blob-code-inner js-file-line">conceptam.</td>
      </tr>
      <tr>
        <td id="L195" class="blob-num js-line-number" data-line-number="195"></td>
        <td id="LC195" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L196" class="blob-num js-line-number" data-line-number="196"></td>
        <td id="LC196" class="blob-code blob-code-inner js-file-line">Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit</td>
      </tr>
      <tr>
        <td id="L197" class="blob-num js-line-number" data-line-number="197"></td>
        <td id="LC197" class="blob-code blob-code-inner js-file-line">quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos</td>
      </tr>
      <tr>
        <td id="L198" class="blob-num js-line-number" data-line-number="198"></td>
        <td id="LC198" class="blob-code blob-code-inner js-file-line">ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes</td>
      </tr>
      <tr>
        <td id="L199" class="blob-num js-line-number" data-line-number="199"></td>
        <td id="LC199" class="blob-code blob-code-inner js-file-line">percipitur at vis. Numquam similique in per, te quo saepe utroque</td>
      </tr>
      <tr>
        <td id="L200" class="blob-num js-line-number" data-line-number="200"></td>
        <td id="LC200" class="blob-code blob-code-inner js-file-line">pericula.</td>
      </tr>
      <tr>
        <td id="L201" class="blob-num js-line-number" data-line-number="201"></td>
        <td id="LC201" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L202" class="blob-num js-line-number" data-line-number="202"></td>
        <td id="LC202" class="blob-code blob-code-inner js-file-line">Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo</td>
      </tr>
      <tr>
        <td id="L203" class="blob-num js-line-number" data-line-number="203"></td>
        <td id="LC203" class="blob-code blob-code-inner js-file-line">vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque</td>
      </tr>
      <tr>
        <td id="L204" class="blob-num js-line-number" data-line-number="204"></td>
        <td id="LC204" class="blob-code blob-code-inner js-file-line">gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne</td>
      </tr>
      <tr>
        <td id="L205" class="blob-num js-line-number" data-line-number="205"></td>
        <td id="LC205" class="blob-code blob-code-inner js-file-line">suas latine vix, eos oblique sanctus pertinax cu.</td>
      </tr>
      <tr>
        <td id="L206" class="blob-num js-line-number" data-line-number="206"></td>
        <td id="LC206" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L207" class="blob-num js-line-number" data-line-number="207"></td>
        <td id="LC207" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>*{References}<span class="pl-c1">\label</span>{references}</td>
      </tr>
      <tr>
        <td id="L208" class="blob-num js-line-number" data-line-number="208"></td>
        <td id="LC208" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\addcontentsline</span>{toc}{section}{References}</td>
      </tr>
      <tr>
        <td id="L209" class="blob-num js-line-number" data-line-number="209"></td>
        <td id="LC209" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L210" class="blob-num js-line-number" data-line-number="210"></td>
        <td id="LC210" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{refs}{}</td>
      </tr>
      <tr>
        <td id="L211" class="blob-num js-line-number" data-line-number="211"></td>
        <td id="LC211" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Boettiger_2015}{}</td>
      </tr>
      <tr>
        <td id="L212" class="blob-num js-line-number" data-line-number="212"></td>
        <td id="LC212" class="blob-code blob-code-inner js-file-line">Boettiger, C. (2015). <span class="pl-c1">\emph</span>{Knitcitations: Citations for &#39;knitr&#39;</td>
      </tr>
      <tr>
        <td id="L213" class="blob-num js-line-number" data-line-number="213"></td>
        <td id="LC213" class="blob-code blob-code-inner js-file-line">markdown files}. Retrieved from</td>
      </tr>
      <tr>
        <td id="L214" class="blob-num js-line-number" data-line-number="214"></td>
        <td id="LC214" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://CRAN.R-project.org/package=knitcitations}</td>
      </tr>
      <tr>
        <td id="L215" class="blob-num js-line-number" data-line-number="215"></td>
        <td id="LC215" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L216" class="blob-num js-line-number" data-line-number="216"></td>
        <td id="LC216" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Halpern_2006}{}</td>
      </tr>
      <tr>
        <td id="L217" class="blob-num js-line-number" data-line-number="217"></td>
        <td id="LC217" class="blob-code blob-code-inner js-file-line">Halpern, B.S., Regan, H.M., Possingham, H.P. <span class="pl-cce">\&amp;</span> McCarthy, M.A. (2006).</td>
      </tr>
      <tr>
        <td id="L218" class="blob-num js-line-number" data-line-number="218"></td>
        <td id="LC218" class="blob-code blob-code-inner js-file-line">Accounting for uncertainty in marine reserve design. <span class="pl-c1">\emph</span>{Ecology</td>
      </tr>
      <tr>
        <td id="L219" class="blob-num js-line-number" data-line-number="219"></td>
        <td id="LC219" class="blob-code blob-code-inner js-file-line">Letters}, <span class="pl-c1">\textbf</span>{9}, 2--11. Retrieved from</td>
      </tr>
      <tr>
        <td id="L220" class="blob-num js-line-number" data-line-number="220"></td>
        <td id="LC220" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://doi.org/10.1111<span class="pl-cce">\%</span>2Fj.1461-0248.2005.00827.x}</td>
      </tr>
      <tr>
        <td id="L221" class="blob-num js-line-number" data-line-number="221"></td>
        <td id="LC221" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L222" class="blob-num js-line-number" data-line-number="222"></td>
        <td id="LC222" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Keil_2012}{}</td>
      </tr>
      <tr>
        <td id="L223" class="blob-num js-line-number" data-line-number="223"></td>
        <td id="LC223" class="blob-code blob-code-inner js-file-line">Keil, P., Belmaker, J., Wilson, A.M., Unitt, P. <span class="pl-cce">\&amp;</span> Jetz, W. (2012).</td>
      </tr>
      <tr>
        <td id="L224" class="blob-num js-line-number" data-line-number="224"></td>
        <td id="LC224" class="blob-code blob-code-inner js-file-line">Downscaling of species distribution models: A hierarchical approach (R.</td>
      </tr>
      <tr>
        <td id="L225" class="blob-num js-line-number" data-line-number="225"></td>
        <td id="LC225" class="blob-code blob-code-inner js-file-line">Freckleton, Ed.). <span class="pl-c1">\emph</span>{Methods in Ecology and Evolution}, <span class="pl-c1">\textbf</span>{4},</td>
      </tr>
      <tr>
        <td id="L226" class="blob-num js-line-number" data-line-number="226"></td>
        <td id="LC226" class="blob-code blob-code-inner js-file-line">82--94. Retrieved from</td>
      </tr>
      <tr>
        <td id="L227" class="blob-num js-line-number" data-line-number="227"></td>
        <td id="LC227" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://doi.org/10.1111<span class="pl-cce">\%</span>2Fj.2041-210x.2012.00264.x}</td>
      </tr>
      <tr>
        <td id="L228" class="blob-num js-line-number" data-line-number="228"></td>
        <td id="LC228" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L229" class="blob-num js-line-number" data-line-number="229"></td>
        <td id="LC229" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-R_Core_Team_2016}{}</td>
      </tr>
      <tr>
        <td id="L230" class="blob-num js-line-number" data-line-number="230"></td>
        <td id="LC230" class="blob-code blob-code-inner js-file-line">R Core Team. (2016). <span class="pl-c1">\emph</span>{R: A language and environment for statistical</td>
      </tr>
      <tr>
        <td id="L231" class="blob-num js-line-number" data-line-number="231"></td>
        <td id="LC231" class="blob-code blob-code-inner js-file-line">computing}. R Foundation for Statistical Computing, Vienna, Austria.</td>
      </tr>
      <tr>
        <td id="L232" class="blob-num js-line-number" data-line-number="232"></td>
        <td id="LC232" class="blob-code blob-code-inner js-file-line">Retrieved from <span class="pl-c1">\url</span>{https://www.R-project.org/}</td>
      </tr>
      <tr>
        <td id="L233" class="blob-num js-line-number" data-line-number="233"></td>
        <td id="LC233" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L234" class="blob-num js-line-number" data-line-number="234"></td>
        <td id="LC234" class="blob-code blob-code-inner js-file-line">
</td>
      </tr>
      <tr>
        <td id="L235" class="blob-num js-line-number" data-line-number="235"></td>
        <td id="LC235" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{document}</td>
      </tr>
</table>

  <details class="details-reset details-overlay BlobToolbar position-absolute js-file-line-actions dropdown d-none" aria-hidden="true">
    <summary class="btn-octicon ml-0 px-2 p-0 bg-white border border-gray-dark rounded-1" aria-label="Inline file action toolbar">
      <svg class="octicon octicon-kebab-horizontal" viewBox="0 0 13 16" version="1.1" width="13" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3zm5 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3zM13 7.5a1.5 1.5 0 1 1-3 0 1.5 1.5 0 0 1 3 0z"/></svg>
    </summary>
    <details-menu>
      <ul class="BlobToolbar-dropdown dropdown-menu dropdown-menu-se mt-2">
        <li><clipboard-copy role="menuitem" class="dropdown-item" id="js-copy-lines" style="cursor:pointer;" data-original-text="Copy lines">Copy lines</clipboard-copy></li>
        <li><clipboard-copy role="menuitem" class="dropdown-item" id="js-copy-permalink" style="cursor:pointer;" data-original-text="Copy permalink">Copy permalink</clipboard-copy></li>
        <li><a class="dropdown-item js-update-url-with-hash" id="js-view-git-blame" role="menuitem" href="/petrkeil/Blog/blame/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.tex">View git blame</a></li>
          <li><a class="dropdown-item" id="js-new-issue" role="menuitem" href="/petrkeil/Blog/issues/new">Open new issue</a></li>
      </ul>
    </details-menu>
  </details>

  </div>

  </div>

  <details class="details-reset details-overlay details-overlay-dark">
    <summary data-hotkey="l" aria-label="Jump to line"></summary>
    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast linejump" aria-label="Jump to line">
      <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-jump-to-line-form Box-body d-flex" action="" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
        <input class="form-control flex-auto mr-3 linejump-input js-jump-to-line-field" type="text" placeholder="Jump to line&hellip;" aria-label="Jump to line" autofocus>
        <button type="submit" class="btn" data-close-dialog>Go</button>
</form>    </details-dialog>
  </details>

  </div>
  <div class="modal-backdrop js-touch-events"></div>
</div>

    </div>
  </div>

  </div>

<div class="footer container-lg px-3" role="contentinfo">
  <div class="position-relative d-flex flex-justify-between pt-6 pb-2 mt-6 f6 text-gray border-top border-gray-light ">
    <ul class="list-style-none d-flex flex-wrap ">
      <li class="mr-3">&copy; 2018 <span title="0.30940s from unicorn-6bfd5c759c-8hwtx">GitHub</span>, Inc.</li>
        <li class="mr-3"><a data-ga-click="Footer, go to terms, text:terms" href="https://github.com/site/terms">Terms</a></li>
        <li class="mr-3"><a data-ga-click="Footer, go to privacy, text:privacy" href="https://github.com/site/privacy">Privacy</a></li>
        <li class="mr-3"><a href="https://help.github.com/articles/github-security/" data-ga-click="Footer, go to security, text:security">Security</a></li>
        <li class="mr-3"><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
        <li><a data-ga-click="Footer, go to help, text:help" href="https://help.github.com">Help</a></li>
    </ul>

    <a aria-label="Homepage" title="GitHub" class="footer-octicon mr-lg-4" href="https://github.com">
      <svg height="24" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="24" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
</a>
   <ul class="list-style-none d-flex flex-wrap ">
        <li class="mr-3"><a data-ga-click="Footer, go to contact, text:contact" href="https://github.com/contact">Contact GitHub</a></li>
        <li class="mr-3"><a href="https://github.com/pricing" data-ga-click="Footer, go to Pricing, text:Pricing">Pricing</a></li>
      <li class="mr-3"><a href="https://developer.github.com" data-ga-click="Footer, go to api, text:api">API</a></li>
      <li class="mr-3"><a href="https://training.github.com" data-ga-click="Footer, go to training, text:training">Training</a></li>
        <li class="mr-3"><a href="https://blog.github.com" data-ga-click="Footer, go to blog, text:blog">Blog</a></li>
        <li><a data-ga-click="Footer, go to about, text:about" href="https://github.com/about">About</a></li>

    </ul>
  </div>
  <div class="d-flex flex-justify-center pb-6">
    <span class="f6 text-gray-light"></span>
  </div>
</div>

  <div id="ajax-error-message" class="ajax-error-message flash flash-error">
    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
    <button type="button" class="flash-close js-ajax-error-dismiss" aria-label="Dismiss error">
      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
    </button>
    You can’t perform that action at this time.
  </div>

    <script crossorigin="anonymous" integrity="sha512-RJ1ufbxsSbKjRCyYvinsPNKvTBvcvvKUvEOJ8g+GjtWI5SuRr+QPBlZcvRDws4H9YwAgdQFcGxfL8UbwEfdI7A==" type="application/javascript" src="https://assets-cdn.github.com/assets/compat-daf14de28fadf1e2bc40d100cb773e2b.js"></script>
    <script crossorigin="anonymous" integrity="sha512-IC5Ai6c7cUBfMx54JUAsIjA7VroipzkizlZ8F6/0efsGGyZStweZV7bX9bxSFL07nUNLfwrKSEysVIijX+CeUw==" type="application/javascript" src="https://assets-cdn.github.com/assets/frameworks-5874e38105ec062c740350eeb96bdd8a.js"></script>

    <script crossorigin="anonymous" async="async" integrity="sha512-/E7YUPwg5s5FmwhSiwtXwNsTUCpjjdcrKoK7UFMQCguTSC71dACKl+XDhBftzkBsRra4w+a24G4oU535TieAIA==" type="application/javascript" src="https://assets-cdn.github.com/assets/github-1835546276a57f4d0c3203810d2ec7d6.js"></script>

  <div class="js-stale-session-flash stale-session-flash flash flash-warn flash-banner d-none">
    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
    <span class="signed-in-tab-flash">You signed in with another tab or window. <a href="">Reload</a> to refresh your session.</span>
    <span class="signed-out-tab-flash">You signed out in another tab or window. <a href="">Reload</a> to refresh your session.</span>
  </div>
  <div class="facebox" id="facebox" style="display:none;">
  <div class="facebox-popup">
    <div class="facebox-content" role="dialog" aria-labelledby="facebox-header" aria-describedby="facebox-description">
    </div>
    <button type="button" class="facebox-close js-facebox-close" aria-label="Close modal">
      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
    </button>
  </div>
</div>

  <template id="site-details-dialog">
  <details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark" open>
    <summary aria-haspopup="dialog" aria-label="Close dialog"></summary>
    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast">
      <button class="Box-btn-octicon m-0 btn-octicon position-absolute right-0 top-0" type="button" aria-label="Close dialog" data-close-dialog>
        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
      </button>
      <div class="octocat-spinner my-6 js-details-dialog-spinner"></div>
    </details-dialog>
  </details>
</template>

  <div class="Popover js-hovercard-content position-absolute" style="display: none; outline: none;" tabindex="0">
  <div class="Popover-message Popover-message--bottom-left Popover-message--large Box box-shadow-large" style="width:360px;">
  </div>
</div>

<div id="hovercard-aria-description" class="sr-only">
  Press h to open a hovercard with more details.
</div>

  </body>
</html>

### 2018-09-21 manuscript/manuscript_template.Rmd
Updating Rmarkdown template

@@
-<!DOCTYPE html>
-<html lang="en">
-  <head>
-    <meta charset="utf-8">
-  <link rel="dns-prefetch" href="https://assets-cdn.github.com">
-  <link rel="dns-prefetch" href="https://avatars0.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars1.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars2.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars3.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
-  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">
+---
+title:  'A template for writing a manuscript in Rmarkdown'
+author:
+- James Grecian One^[University of Somewhere]
+- Ian Jonsen Two^[University of Nowhere]
+date: "`r format(Sys.time(), '%d %B %Y')`"
+tags: [nothing, nothingness]
+output:
+  pdf_document:
+    fig_caption: yes
+    keep_tex: yes
+    number_sections: yes
+  html_document:
+    fig_caption: yes
+    force_captions: yes
+    highlight: pygments
+    number_sections: yes
+    theme: cerulean
+csl: mee.csl
+header-includes:
+   - \usepackage{lineno}
+   - \linenumbers
+---
 
-  <link crossorigin="anonymous" media="all" integrity="sha512-/yZA7MGD9acBi5MmgjnivwjGeiNsmimsI/bhLlK7akrRuw+hMxNpJoQEMO9Zt0Nq6ZRu1m1NGV6r95Ib0zx7Qw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/frameworks-1ca00d32d1a8adc78ae7bb6677410eb1.css" />
-  <link crossorigin="anonymous" media="all" integrity="sha512-pHF1luoMSUFxvz63bW3jEbbifYl/pruHUw+kljThAPi2g0nhgMdvWj4bQRh4O8MYp9NR60XYcylaLXmYA8YXSw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/github-5043b3d96d50b119b971c2cdde4e0a62.css" />
+```{r, echo=FALSE}
+  # devtools::install_github("cboettig/knitcitations@v1")
+  library(knitcitations); cleanbib()
+  cite_options(citation_format = "pandoc", check.entries=TRUE)
+  library(bibtex)
+```
 
-  <meta name="viewport" content="width=device-width">
+# Abstract
 
-  <title>Blog/manuscript_template.Rmd at master · petrkeil/Blog</title>
-    <meta name="description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog">
-    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
-  <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
-  <meta property="fb:app_id" content="1401488693436528">
-
-    <meta property="og:image" content="https://avatars2.githubusercontent.com/u/5421227?s=400&amp;v=4" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="petrkeil/Blog" /><meta property="og:url" content="https://github.com/petrkeil/Blog" /><meta property="og:description" content="This repository contains codes for all of my blog posts since March 11 2015.
-- petrkeil/Blog" />
-
-  <link rel="assets" href="https://assets-cdn.github.com/">
-  <link rel="web-socket" href="wss://live.github.com/_sockets/VjI6MzE5MjkzMDMyOmY4ZDEyYmU0MjE5YTNjMTg5YzMwODMwOTRhOWJmYjA2NmU1ZDRjYzNmNTlkMmZmNThiNmEyMDhkY2U0ODM3YjU=--6699b174fe2e40623d9cdaf2af3c8eb14a2753a8">
-  <meta name="pjax-timeout" content="1000">
-  <link rel="sudo-modal" href="/sessions/sudo_modal">
-  <meta name="request-id" content="DEC4:7B80:13DB109:2408B1B:5BA52F38" data-pjax-transient>
-
-  <meta name="selected-link" value="repo_source" data-pjax-transient>
-
-      <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
-    <meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
-    <meta name="google-site-verification" content="GXs5KoUUkNCoaAZn7wPN-t01Pywp9M3sEjnt_3_ZWPc">
-
-  <meta name="octolytics-host" content="collector.githubapp.com" /><meta name="octolytics-app-id" content="github" /><meta name="octolytics-event-url" content="https://collector.githubapp.com/github-external/browser_event" /><meta name="octolytics-dimension-request_id" content="DEC4:7B80:13DB109:2408B1B:5BA52F38" /><meta name="octolytics-dimension-region_edge" content="iad" /><meta name="octolytics-dimension-region_render" content="iad" /><meta name="octolytics-actor-id" content="34245401" /><meta name="octolytics-actor-login" content="jamesgrecian" /><meta name="octolytics-actor-hash" content="821728246d06cdfe784e56dfb8dc2a4447ec5ee2fb7525c8728616156ffa29a2" />
-<meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" />
-
-    <meta name="google-analytics" content="UA-3769691-2">
-
-  <meta class="js-ga-set" name="userId" content="078bbd73f63945865b3a6f9e3c674706" %>
-
-<meta class="js-ga-set" name="dimension1" content="Logged In">
-
-      <meta name="hostname" content="github.com">
-    <meta name="user-login" content="jamesgrecian">
-
-      <meta name="expected-hostname" content="github.com">
-    <meta name="js-proxy-site-detection-payload" content="NGYyMDUzNWVkYjVhZGU3ZTI0NmJjNzE5MmZkYTM3N2YwMDRlOTk2MTFmMDRkYjNjY2VjZDJlYTIzN2JlYTFlN3x7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjM0LjI0OC4yMDciLCJyZXF1ZXN0X2lkIjoiREVDNDo3QjgwOjEzREIxMDk6MjQwOEIxQjo1QkE1MkYzOCIsInRpbWVzdGFtcCI6MTUzNzU1MjE5NiwiaG9zdCI6ImdpdGh1Yi5jb20ifQ==">
-
-    <meta name="enabled-features" content="DASHBOARD_V2_LAYOUT_OPT_IN,EXPLORE_DISCOVER_REPOSITORIES,UNIVERSE_BANNER,MARKETPLACE_PLAN_RESTRICTION_EDITOR,MARKETPLACE_RETARGETING,QUOTE_MARKDOWN">
-
-  <meta name="html-safe-nonce" content="4d33eb369dbc9e939c0c70269799ff90a62c9762">
-
-  <meta http-equiv="x-pjax-version" content="3842ef7af97baac02526bd1bb609fd99">
-
-      <link href="https://github.com/petrkeil/Blog/commits/master.atom" rel="alternate" title="Recent Commits to Blog:master" type="application/atom+xml">
-
-  <meta name="go-import" content="github.com/petrkeil/Blog git https://github.com/petrkeil/Blog.git">
-
-  <meta name="octolytics-dimension-user_id" content="5421227" /><meta name="octolytics-dimension-user_login" content="petrkeil" /><meta name="octolytics-dimension-repository_id" content="32012442" /><meta name="octolytics-dimension-repository_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="32012442" /><meta name="octolytics-dimension-repository_network_root_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_explore_github_marketplace_ci_cta_shown" content="false" />
-
-    <link rel="canonical" href="https://github.com/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.Rmd" data-pjax-transient>
-
-  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">
-
-  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">
-
-  <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#000000">
-  <link rel="icon" type="image/x-icon" class="js-site-favicon" href="https://assets-cdn.github.com/favicon.ico">
-
-<meta name="theme-color" content="#1e2327">
-
-  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">
-
-  </head>
-
-  <body class="logged-in env-production page-blob">
-
-  <div class="position-relative js-header-wrapper ">
-    <a href="#start-of-content" tabindex="1" class="p-3 bg-blue text-white show-on-focus js-skip-to-content">Skip to content</a>
-    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>
-
-<header class="Header  f5" role="banner">
-  <div class="d-flex flex-justify-between px-3 ">
-    <div class="d-flex flex-justify-between ">
-      <div class="">
-        <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
-  <svg height="32" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="32" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
-</a>
-
-      </div>
-
-    </div>
-
-    <div class="HeaderMenu d-flex flex-justify-between flex-auto">
-      <div class="d-flex">
-            <div class="">
-              <div class="header-search scoped-search site-scoped-search js-site-search position-relative js-jump-to"
-  role="combobox"
-  aria-owns="jump-to-results"
-  aria-label="Search or jump to"
-  aria-haspopup="listbox"
-  aria-expanded="false"
->
-  <div class="position-relative">
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-site-search-form" data-scope-type="Repository" data-scope-id="32012442" data-scoped-search-url="/petrkeil/Blog/search" data-unscoped-search-url="/search" action="/petrkeil/Blog/search" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
-      <label class="form-control header-search-wrapper header-search-wrapper-jump-to position-relative d-flex flex-justify-between flex-items-center js-chromeless-input-container">
-        <input type="text"
-          class="form-control header-search-input jump-to-field js-jump-to-field js-site-search-focus js-site-search-field is-clearable"
-          data-hotkey="s,/"
-          name="q"
-          value=""
-          placeholder="Search or jump to…"
-          data-unscoped-placeholder="Search or jump to…"
-          data-scoped-placeholder="Search or jump to…"
-          autocapitalize="off"
-          aria-autocomplete="list"
-          aria-controls="jump-to-results"
-          data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations#csrf-token=vKtepHuL5c+ELLxqvw5pBoFyrsH33qoqLeuwQXRDqVrb+0oabwda3WZ6kzvLvbGCX4m1kWaOg5yCDa6OI6VHtw=="
-          spellcheck="false"
-          autocomplete="off"
-          >
-          <input type="hidden" class="js-site-search-type-field" name="type" >
-            <img src="https://assets-cdn.github.com/images/search-shortcut-hint.svg" alt="" class="mr-2 header-search-key-slash">
-
-            <div class="Box position-absolute overflow-hidden d-none jump-to-suggestions js-jump-to-suggestions-container">
-              <ul class="d-none js-jump-to-suggestions-template-container">
-                <li class="d-flex flex-justify-start flex-items-center p-0 f5 navigation-item js-navigation-item" role="option">
-                  <a tabindex="-1" class="no-underline d-flex flex-auto flex-items-center p-2 jump-to-suggestions-path js-jump-to-suggestion-path js-navigation-open" href="">
-                    <div class="jump-to-octicon js-jump-to-octicon mr-2 text-center d-none">
-                      <svg height="16" width="16" class="octicon octicon-repo flex-shrink-0 js-jump-to-octicon-repo d-none" title="Repository" aria-label="Repository" viewBox="0 0 12 16" version="1.1" role="img"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
-                      <svg height="16" width="16" class="octicon octicon-project flex-shrink-0 js-jump-to-octicon-project d-none" title="Project" aria-label="Project" viewBox="0 0 15 16" version="1.1" role="img"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
-                      <svg height="16" width="16" class="octicon octicon-search flex-shrink-0 js-jump-to-octicon-search d-none" title="Search" aria-label="Search" viewBox="0 0 16 16" version="1.1" role="img"><path fill-rule="evenodd" d="M15.7 13.3l-3.81-3.83A5.93 5.93 0 0 0 13 6c0-3.31-2.69-6-6-6S1 2.69 1 6s2.69 6 6 6c1.3 0 2.48-.41 3.47-1.11l3.83 3.81c.19.2.45.3.7.3.25 0 .52-.09.7-.3a.996.996 0 0 0 0-1.41v.01zM7 10.7c-2.59 0-4.7-2.11-4.7-4.7 0-2.59 2.11-4.7 4.7-4.7 2.59 0 4.7 2.11 4.7 4.7 0 2.59-2.11 4.7-4.7 4.7z"/></svg>
-                    </div>
-
-                    <img class="avatar mr-2 flex-shrink-0 js-jump-to-suggestion-avatar d-none" alt="" aria-label="Team" src="" width="28" height="28">
-
-                    <div class="jump-to-suggestion-name js-jump-to-suggestion-name flex-auto overflow-hidden text-left no-wrap css-truncate css-truncate-target">
-                    </div>
-
-                    <div class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none js-jump-to-badge-search">
-                      <span class="js-jump-to-badge-search-text-default d-none" aria-label="in this repository">
-                        In this repository
-                      </span>
-                      <span class="js-jump-to-badge-search-text-global d-none" aria-label="in all of GitHub">
-                        All GitHub
-                      </span>
-                      <span aria-hidden="true" class="d-inline-block ml-1 v-align-middle">↵</span>
-                    </div>
-
-                    <div aria-hidden="true" class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none d-on-nav-focus js-jump-to-badge-jump">
-                      Jump to
-                      <span class="d-inline-block ml-1 v-align-middle">↵</span>
-                    </div>
-                  </a>
-                </li>
-              </ul>
-              <ul class="d-none js-jump-to-no-results-template-container">
-                <li class="d-flex flex-justify-center flex-items-center p-3 f5 d-none">
-                  <span class="text-gray">No suggested jump to results</span>
-                </li>
-              </ul>
-
-              <ul id="jump-to-results" role="listbox" class="js-navigation-container jump-to-suggestions-results-container js-jump-to-suggestions-results-container" >
-                <li class="d-flex flex-justify-center flex-items-center p-0 f5">
-                  <img src="https://assets-cdn.github.com/images/spinners/octocat-spinner-128.gif" alt="Octocat Spinner Icon" class="m-2" width="28">
-                </li>
-              </ul>
-            </div>
-      </label>
-</form>  </div>
-</div>
-
-            </div>
-
-          <ul class="d-flex pl-2 flex-items-center text-bold list-style-none" role="navigation">
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g p" data-ga-click="Header, click, Nav menu - item:pulls context:user" aria-label="Pull requests you created" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls" href="/pulls">
-                Pull requests
-</a>            </li>
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g i" data-ga-click="Header, click, Nav menu - item:issues context:user" aria-label="Issues you created" data-selected-links="/issues /issues/assigned /issues/mentioned /issues" href="/issues">
-                Issues
-</a>            </li>
-              <li>
-                <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:marketplace context:user" data-octo-click="marketplace_click" data-octo-dimensions="location:nav_bar" data-selected-links=" /marketplace" href="/marketplace">
-                   Marketplace
-</a>              </li>
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:explore" data-selected-links="/explore /trending /trending/developers /integrations /integrations/feature/code /integrations/feature/collaborate /integrations/feature/ship showcases showcases_search showcases_landing /explore" href="/explore">
-                Explore
-</a>            </li>
-          </ul>
-      </div>
-
-      <div class="d-flex">
-
-<ul class="user-nav d-flex flex-items-center list-style-none" id="user-links">
-  <li class="dropdown">
-    <span class="d-inline-block  px-2">
-
-    <a aria-label="You have no unread notifications" class="notification-indicator tooltipped tooltipped-s  js-socket-channel js-notification-indicator" data-hotkey="g n" data-ga-click="Header, go to notifications, icon:read" data-channel="notification-changed:34245401" href="/notifications">
-        <span class="mail-status "></span>
-        <svg class="octicon octicon-bell" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M13.99 11.991v1H0v-1l.73-.58c.769-.769.809-2.547 1.189-4.416.77-3.767 4.077-4.996 4.077-4.996 0-.55.45-1 .999-1 .55 0 1 .45 1 1 0 0 3.387 1.229 4.156 4.996.38 1.879.42 3.657 1.19 4.417l.659.58h-.01zM6.995 15.99c1.11 0 1.999-.89 1.999-1.999H4.996c0 1.11.89 1.999 1.999 1.999z"/></svg>
-</a>
-    </span>
-  </li>
-
-  <li class="dropdown">
-    <details class="details-overlay details-reset d-flex px-2 flex-items-center">
-      <summary class="HeaderNavlink"
-         aria-label="Create new…"
-         data-ga-click="Header, create new, icon:add">
-        <svg class="octicon octicon-plus float-left mr-1 mt-1" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 9H7v5H5V9H0V7h5V2h2v5h5v2z"/></svg>
-        <span class="dropdown-caret mt-1"></span>
-      </summary>
-      <details-menu class="dropdown-menu dropdown-menu-sw">
-
-<a role="menuitem" class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
-  New repository
-</a>
-
-  <a role="menuitem" class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
-    Import repository
-  </a>
-
-<a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, create new gist">
-  New gist
-</a>
-
-  <a role="menuitem" class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
-    New organization
-  </a>
-
-  <div class="dropdown-divider"></div>
-  <div class="dropdown-header">
-    <span title="petrkeil/Blog">This repository</span>
-  </div>
-    <a role="menuitem" class="dropdown-item" href="/petrkeil/Blog/issues/new" data-ga-click="Header, create new issue">
-      New issue
-    </a>
-
-      </details-menu>
-    </details>
-  </li>
-
-  <li class="dropdown">
-
-    <details class="details-overlay details-reset d-flex pl-2 flex-items-center">
-      <summary class="HeaderNavlink name mt-1"
-        aria-label="View profile and more"
-        data-ga-click="Header, show menu, icon:avatar">
-        <img alt="@jamesgrecian" class="avatar float-left mr-1" src="https://avatars2.githubusercontent.com/u/34245401?s=40&amp;v=4" height="20" width="20">
-        <span class="dropdown-caret"></span>
-      </summary>
-      <details-menu class="dropdown-menu dropdown-menu-sw">
-        <ul>
-          <li class="header-nav-current-user css-truncate"><a role="menuitem" class="no-underline user-profile-link px-3 pt-2 pb-2 mb-n2 mt-n1 d-block" href="/jamesgrecian" data-ga-click="Header, go to profile, text:Signed in as">Signed in as <strong class="css-truncate-target">jamesgrecian</strong></a></li>
-          <li class="dropdown-divider"></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian" data-ga-click="Header, go to profile, text:your profile">Your profile</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=repositories" data-ga-click="Header, go to repositories, text:your repositories">Your repositories</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">Your stars</a></li>
-            <li><a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, your gists, text:your gists">Your gists</a></li>
-          <li class="dropdown-divider"></li>
-          <li><a role="menuitem" class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">Help</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">Settings</a></li>
-          <li>
-            <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="logout-form" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="70z+7pfJi/hSwFPV+HwBpRO+h6tPFRwPr5KWtHt/uVnEYJnva1K9ZZ8MF/preCNcmvA/GicmqsAz47+DjSrHhg==" />
-              <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout" role="menuitem">
-                Sign out
-              </button>
-</form>          </li>
-        </ul>
-      </details-menu>
-    </details>
-  </li>
-</ul>
-
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="sr-only right-0" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="xmQg0zHF9HnWv4MzKNWcgsKD5qm6fAiK0ZheRQvWYivtSEfSzV7C5Btzxxy70b57S81eGNJPvkVN6Xdy/YMc9A==" />
-          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
-            Sign out
-          </button>
-</form>      </div>
-    </div>
-  </div>
-</header>
-
-  </div>
-
-  <div id="start-of-content" class="show-on-focus"></div>
-
-    <div id="js-flash-container">
-
-</div>
-
-  <div role="main" class="application-main ">
-        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
-    <div id="js-repo-pjax-container" data-pjax-container >
-
-  <div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav  ">
-    <div class="repohead-details-container clearfix container">
-
-      <ul class="pagehead-actions">
-  <li>
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form data-autosubmit="true" data-remote="true" class="js-social-container" action="/notifications/subscribe" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="oOjYFEFAFqKUnhayqPj0oBlERt/6I+ne5pf8Sl8iMXmjlzqHCag0+YA+/9+8U1yIKjTim6/xQpufP+1q6zhkGQ==" />      <input type="hidden" name="repository_id" id="repository_id" value="32012442" class="form-control" />
-
-        <div class="select-menu js-menu-container js-select-menu">
-          <a href="/petrkeil/Blog/subscription"
-            class="btn btn-sm btn-with-count select-menu-button js-menu-target"
-            role="button"
-            aria-haspopup="true"
-            aria-expanded="false"
-            aria-label="Toggle repository notifications menu"
-            data-ga-click="Repository, click Watch settings, action:blob#show">
-            <span class="js-select-button">
-                <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                Watch
-            </span>
-          </a>
-          <a class="social-count js-social-count"
-            href="/petrkeil/Blog/watchers"
-            aria-label="17 users are watching this repository">
-            17
-          </a>
-
-        <div class="select-menu-modal-holder">
-          <div class="select-menu-modal subscription-menu-modal js-menu-content">
-            <div class="select-menu-header js-navigation-enable" tabindex="-1">
-              <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-              <span class="select-menu-title">Notifications</span>
-            </div>
-
-              <div class="select-menu-list js-navigation-container" role="menu">
-
-                <div class="select-menu-item js-navigation-item selected" role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_included" value="included" checked="checked" />
-                    <span class="select-menu-item-heading">Not watching</span>
-                    <span class="description">Be notified when participating or @mentioned.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                      Watch
-                    </span>
-                  </div>
-                </div>
-
-                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_subscribed" value="subscribed" />
-                    <span class="select-menu-item-heading">Watching</span>
-                    <span class="description">Be notified of all conversations.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                        Unwatch
-                    </span>
-                  </div>
-                </div>
-
-                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_ignore" value="ignore" />
-                    <span class="select-menu-item-heading">Ignoring</span>
-                    <span class="description">Never be notified.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-mute v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 2.81v10.38c0 .67-.81 1-1.28.53L3 10H1c-.55 0-1-.45-1-1V7c0-.55.45-1 1-1h2l3.72-3.72C7.19 1.81 8 2.14 8 2.81zm7.53 3.22l-1.06-1.06-1.97 1.97-1.97-1.97-1.06 1.06L11.44 8 9.47 9.97l1.06 1.06 1.97-1.97 1.97 1.97 1.06-1.06L13.56 8l1.97-1.97z"/></svg>
-                        Stop ignoring
-                    </span>
-                  </div>
-                </div>
-
-              </div>
-
-            </div>
-          </div>
-        </div>
-</form>
-  </li>
-
-  <li>
-
-  <div class="js-toggler-container js-social-container starring-container ">
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="starred js-social-form" action="/petrkeil/Blog/unstar" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="J1oHiD/jIasQWYvIghtqwNeIcq7Wz8HRwv5jjbAgOUiPVQ0EIQakzs+VFq2Jme9ff2CNRtGmfDd21a9Dmlzz+g==" />
-      <input type="hidden" name="context" value="repository"></input>
-      <button
-        type="submit"
-        class="btn btn-sm btn-with-count js-toggler-target"
-        aria-label="Unstar this repository" title="Unstar petrkeil/Blog"
-        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
-        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
-        Unstar
-      </button>
-        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
-           aria-label="79 users starred this repository">
-          79
-        </a>
-</form>
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="unstarred js-social-form" action="/petrkeil/Blog/star" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="QDgeOt/aBH8Yr862sLVj5rnSJEuVN8SGuxtswA5f/IDNGmAIWBfI4wwEyYlLxWpNLF8Shijy9vdBluRlDnHlzg==" />
-      <input type="hidden" name="context" value="repository"></input>
-      <button
-        type="submit"
-        class="btn btn-sm btn-with-count js-toggler-target"
-        aria-label="Star this repository" title="Star petrkeil/Blog"
-        data-ga-click="Repository, click star button, action:blob#show; text:Star">
-        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
-        Star
-      </button>
-        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
-           aria-label="79 users starred this repository">
-          79
-        </a>
-</form>  </div>
-
-  </li>
-
-  <li>
-          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="btn-with-count" action="/petrkeil/Blog/fork" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="Y84ilm5ix19gKu7BVYnfUlbhnPecmOc6pf0ITkJM8rS5L8RVxf9S1+VeyBggIdVBYUlUVnj+9FNoFw91y42Z/Q==" />
-            <button
-                type="submit"
-                class="btn btn-sm btn-with-count"
-                data-ga-click="Repository, show fork modal, action:blob#show; text:Fork"
-                title="Fork your own copy of petrkeil/Blog to your account"
-                aria-label="Fork your own copy of petrkeil/Blog to your account">
-              <svg class="octicon octicon-repo-forked v-align-text-bottom" viewBox="0 0 10 16" version="1.1" width="10" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 1a1.993 1.993 0 0 0-1 3.72V6L5 8 3 6V4.72A1.993 1.993 0 0 0 2 1a1.993 1.993 0 0 0-1 3.72V6.5l3 3v1.78A1.993 1.993 0 0 0 5 15a1.993 1.993 0 0 0 1-3.72V9.5l3-3V4.72A1.993 1.993 0 0 0 8 1zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3 10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3-10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
-              Fork
-            </button>
-</form>
-    <a href="/petrkeil/Blog/network/members" class="social-count"
-       aria-label="130 users forked this repository">
-      130
-    </a>
-  </li>
-</ul>
-
-      <h1 class="public ">
-  <svg class="octicon octicon-repo" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
-  <span class="author" itemprop="author"><a class="url fn" rel="author" href="/petrkeil">petrkeil</a></span><!--
---><span class="path-divider">/</span><!--
---><strong itemprop="name"><a data-pjax="#js-repo-pjax-container" href="/petrkeil/Blog">Blog</a></strong>
-
-</h1>
-
-    </div>
-
-<nav class="reponav js-repo-nav js-sidenav-container-pjax container"
-     itemscope
-     itemtype="http://schema.org/BreadcrumbList"
-     role="navigation"
-     data-pjax="#js-repo-pjax-container">
-
-  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-    <a class="js-selected-navigation-item selected reponav-item" itemprop="url" data-hotkey="g c" data-selected-links="repo_source repo_downloads repo_commits repo_releases repo_tags repo_branches repo_packages /petrkeil/Blog" href="/petrkeil/Blog">
-      <svg class="octicon octicon-code" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M9.5 3L8 4.5 11.5 8 8 11.5 9.5 13 14 8 9.5 3zm-5 0L0 8l4.5 5L6 11.5 2.5 8 6 4.5 4.5 3z"/></svg>
-      <span itemprop="name">Code</span>
-      <meta itemprop="position" content="1">
-</a>  </span>
-
-    <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-      <a itemprop="url" data-hotkey="g i" class="js-selected-navigation-item reponav-item" data-selected-links="repo_issues repo_labels repo_milestones /petrkeil/Blog/issues" href="/petrkeil/Blog/issues">
-        <svg class="octicon octicon-issue-opened" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7 2.3c3.14 0 5.7 2.56 5.7 5.7s-2.56 5.7-5.7 5.7A5.71 5.71 0 0 1 1.3 8c0-3.14 2.56-5.7 5.7-5.7zM7 1C3.14 1 0 4.14 0 8s3.14 7 7 7 7-3.14 7-7-3.14-7-7-7zm1 3H6v5h2V4zm0 6H6v2h2v-2z"/></svg>
-        <span itemprop="name">Issues</span>
-        <span class="Counter">1</span>
-        <meta itemprop="position" content="2">
-</a>    </span>
-
-  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-    <a data-hotkey="g p" itemprop="url" class="js-selected-navigation-item reponav-item" data-selected-links="repo_pulls checks /petrkeil/Blog/pulls" href="/petrkeil/Blog/pulls">
-      <svg class="octicon octicon-git-pull-request" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 11.28V5c-.03-.78-.34-1.47-.94-2.06C9.46 2.35 8.78 2.03 8 2H7V0L4 3l3 3V4h1c.27.02.48.11.69.31.21.2.3.42.31.69v6.28A1.993 1.993 0 0 0 10 15a1.993 1.993 0 0 0 1-3.72zm-1 2.92c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zM4 3c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v6.56A1.993 1.993 0 0 0 2 15a1.993 1.993 0 0 0 1-3.72V4.72c.59-.34 1-.98 1-1.72zm-.8 10c0 .66-.55 1.2-1.2 1.2-.65 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
-      <span itemprop="name">Pull requests</span>
-      <span class="Counter">0</span>
-      <meta itemprop="position" content="3">
-</a>  </span>
-
-    <a data-hotkey="g b" class="js-selected-navigation-item reponav-item" data-selected-links="repo_projects new_repo_project repo_project /petrkeil/Blog/projects" href="/petrkeil/Blog/projects">
-      <svg class="octicon octicon-project" viewBox="0 0 15 16" version="1.1" width="15" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
-      Projects
-      <span class="Counter" >0</span>
-</a>
-
-    <a class="js-selected-navigation-item reponav-item" data-hotkey="g w" data-selected-links="repo_wiki /petrkeil/Blog/wiki" href="/petrkeil/Blog/wiki">
-      <svg class="octicon octicon-book" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M3 5h4v1H3V5zm0 3h4V7H3v1zm0 2h4V9H3v1zm11-5h-4v1h4V5zm0 2h-4v1h4V7zm0 2h-4v1h4V9zm2-6v9c0 .55-.45 1-1 1H9.5l-1 1-1-1H2c-.55 0-1-.45-1-1V3c0-.55.45-1 1-1h5.5l1 1 1-1H15c.55 0 1 .45 1 1zm-8 .5L7.5 3H2v9h6V3.5zm7-.5H9.5l-.5.5V12h6V3z"/></svg>
-      Wiki
-</a>
-  <a class="js-selected-navigation-item reponav-item" data-selected-links="repo_graphs repo_contributors dependency_graph pulse /petrkeil/Blog/pulse" href="/petrkeil/Blog/pulse">
-    <svg class="octicon octicon-graph" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M16 14v1H0V0h1v14h15zM5 13H3V8h2v5zm4 0H7V3h2v10zm4 0h-2V6h2v7z"/></svg>
-    Insights
-</a>
-
-</nav>
-
-  </div>
-
-<div class="container new-discussion-timeline experiment-repo-nav  ">
-  <div class="repository-content ">
-
-  <a class="d-none js-permalink-shortcut" data-hotkey="y" href="/petrkeil/Blog/blob/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.Rmd">Permalink</a>
-
-  <!-- blob contrib key: blob_contributors:v21:0cba21dec00b9f9b447a2242a22fa2b0 -->
-
-  <div class="file-navigation">
-
-<div class="select-menu branch-select-menu js-menu-container js-select-menu float-left">
-  <button class=" btn btn-sm select-menu-button js-menu-target css-truncate" data-hotkey="w"
-
-    type="button" aria-label="Switch branches or tags" aria-expanded="false" aria-haspopup="true">
-      <i>Branch:</i>
-      <span class="js-select-button css-truncate-target">master</span>
-  </button>
-
-  <div class="select-menu-modal-holder js-menu-content js-navigation-container" data-pjax>
-
-    <div class="select-menu-modal">
-      <div class="select-menu-header">
-        <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-        <span class="select-menu-title">Switch branches/tags</span>
-      </div>
-
-      <div class="select-menu-filters">
-        <div class="select-menu-text-filter">
-          <input type="text" aria-label="Filter branches/tags" id="context-commitish-filter-field" class="form-control js-filterable-field js-navigation-enable" placeholder="Filter branches/tags">
-        </div>
-        <div class="select-menu-tabs">
-          <ul>
-            <li class="select-menu-tab">
-              <a href="#" data-tab-filter="branches" data-filter-placeholder="Filter branches/tags" class="js-select-menu-tab" role="tab">Branches</a>
-            </li>
-            <li class="select-menu-tab">
-              <a href="#" data-tab-filter="tags" data-filter-placeholder="Find a tag…" class="js-select-menu-tab" role="tab">Tags</a>
-            </li>
-          </ul>
-        </div>
-      </div>
-
-      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="branches" role="menu">
-
-        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">
-
-            <a class="select-menu-item js-navigation-item js-navigation-open selected"
-               href="/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.Rmd"
-               data-name="master"
-               data-skip-pjax="true"
-               rel="nofollow">
-              <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-              <span class="select-menu-item-text css-truncate-target js-select-menu-filter-text">
-                master
-              </span>
-            </a>
-        </div>
-
-          <div class="select-menu-no-results">Nothing to show</div>
-      </div>
-
-      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="tags">
-        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">
-
-        </div>
-
-        <div class="select-menu-no-results">Nothing to show</div>
-      </div>
-
-    </div>
-  </div>
-</div>
-
-    <div class="BtnGroup float-right">
-      <a href="/petrkeil/Blog/find/master"
-            class="js-pjax-capture-input btn btn-sm BtnGroup-item"
-            data-pjax
-            data-hotkey="t">
-        Find file
-      </a>
-      <clipboard-copy for="blob-path" class="btn btn-sm BtnGroup-item">
-        Copy path
-      </clipboard-copy>
-    </div>
-    <div id="blob-path" class="breadcrumb">
-      <span class="repo-root js-repo-root"><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog"><span>Blog</span></a></span></span><span class="separator">/</span><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog/tree/master/2015_03_12_R_ms_template"><span>2015_03_12_R_ms_template</span></a></span><span class="separator">/</span><strong class="final-path">manuscript_template.Rmd</strong>
-    </div>
-  </div>
-
-  <div class="commit-tease">
-      <span class="float-right">
-        <a class="commit-tease-sha" href="/petrkeil/Blog/commit/52b1e1cde0fb01bb0a205930ff265432581bb784" data-pjax>
-          52b1e1c
-        </a>
-        <relative-time datetime="2015-03-12T22:12:59Z">Mar 12, 2015</relative-time>
-      </span>
-      <div>
-        <img class="avatar" width="20" height="20" alt="" src="https://camo.githubusercontent.com/758da529902cc2f78e89a8a8ff28794146eabdf1/68747470733a2f2f322e67726176617461722e636f6d2f6176617461722f38626534333437643665363765386533353066616361316435613237663331643f643d68747470732533412532462532466173736574732d63646e2e6769746875622e636f6d253246696d6167657325324667726176617461727325324667726176617461722d757365722d3432302e706e6726723d6726733d313430" data-canonical-src="https://2.gravatar.com/avatar/8be4347d6e67e8e350faca1d5a27f31d?d=https%3A%2F%2Fassets-cdn.github.com%2Fimages%2Fgravatars%2Fgravatar-user-420.png&amp;r=g&amp;s=140" />
-        <span class="user-mention">Petr Keil</span>
-          <a data-pjax="true" title="Citations modified to include R and packages" class="message" href="/petrkeil/Blog/commit/52b1e1cde0fb01bb0a205930ff265432581bb784">Citations modified to include R and packages</a>
-      </div>
-
-    <div class="commit-tease-contributors">
-
-<details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark float-left mr-2" id="blob_contributors_box">
-  <summary class="btn-link" aria-haspopup="dialog"  >
-
-    <span><strong>0</strong> contributors</span>
-  </summary>
-  <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast " aria-label="Users who have contributed to this file">
-    <div class="Box-header">
-      <button class="Box-btn-octicon btn-octicon float-right" type="button" aria-label="Close dialog" data-close-dialog>
-        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-      </button>
-      <h3 class="Box-title">Users who have contributed to this file</h3>
-    </div>
-
-        <ul class="list-style-none overflow-auto">
-        </ul>
-
-  </details-dialog>
-</details>
-
-    </div>
-  </div>
-
-  <div class="file">
-    <div class="file-header">
-  <div class="file-actions">
-
-    <div class="BtnGroup">
-      <a id="raw-url" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/raw/master/2015_03_12_R_ms_template/manuscript_template.Rmd">Raw</a>
-        <a class="btn btn-sm js-update-url-with-hash BtnGroup-item" data-hotkey="b" href="/petrkeil/Blog/blame/master/2015_03_12_R_ms_template/manuscript_template.Rmd">Blame</a>
-      <a rel="nofollow" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/commits/master/2015_03_12_R_ms_template/manuscript_template.Rmd">History</a>
-    </div>
-
-          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form js-update-url-with-hash" action="/petrkeil/Blog/edit/master/2015_03_12_R_ms_template/manuscript_template.Rmd" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="RDQWb0ZLZztiOYIPlc8RR++SnYgTcU462l3VdiTyiYFsCe4KWd8HON+YIzeb3gW38TGuLa9sVdJc/AOC18Cn4w==" />
-            <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
-              aria-label="Fork this project and edit the file" data-hotkey="e" data-disable-with>
-              <svg class="octicon octicon-pencil" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"/></svg>
-            </button>
-</form>
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form" action="/petrkeil/Blog/delete/master/2015_03_12_R_ms_template/manuscript_template.Rmd" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="2SKvxp3pXN29EtFLN/3i3X0L0HbpmjB1H77ptWHdxXcWgHhUCtbdjiLn0Y5q/XAe46BnM5fLjZqhWOZPztrDLg==" />
-          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
-            aria-label="Fork this project and delete the file" data-disable-with>
-            <svg class="octicon octicon-trashcan" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"/></svg>
-          </button>
-</form>  </div>
-
-  <div class="file-info">
-      112 lines (71 sloc)
-      <span class="file-info-divider"></span>
-    5.18 KB
-  </div>
-</div>
-
-  <div id="readme" class="readme blob instapaper_body">
-    <article class="markdown-body entry-content" itemprop="text"><table data-table-type="yaml-metadata">
-  <thead>
-  <tr>
-  <th>title</th>
-  <th>author</th>
-  <th>date</th>
-  <th>output</th>
-  <th>csl</th>
-  <th>bibliography</th>
-  </tr>
-  </thead>
-  <tbody>
-  <tr>
-  <td><div>Template for writing scientific papers in R markdown</div></td>
-  <td><div>Petr Keil, pkeil@seznam.cz</div></td>
-  <td><div>11/1/2015</div></td>
-  <td><div><table>
-  <thead>
-  <tr>
-  <th>pdf_document</th>
-  <th>html_document</th>
-  </tr>
-  </thead>
-  <tbody>
-  <tr>
-  <td><div><table>
-  <thead>
-  <tr>
-  <th>fig_caption</th>
-  <th>keep_tex</th>
-  <th>number_sections</th>
-  </tr>
-  </thead>
-  <tbody>
-  <tr>
-  <td><div>true</div></td>
-  <td><div>true</div></td>
-  <td><div>true</div></td>
-  </tr>
-  </tbody>
-</table>
-</div></td>
-  <td><div><table>
-  <thead>
-  <tr>
-  <th>fig_caption</th>
-  <th>force_captions</th>
-  <th>highlight</th>
-  <th>number_sections</th>
-  <th>theme</th>
-  </tr>
-  </thead>
-  <tbody>
-  <tr>
-  <td><div>true</div></td>
-  <td><div>true</div></td>
-  <td><div>pygments</div></td>
-  <td><div>true</div></td>
-  <td><div>cerulean</div></td>
-  </tr>
-  </tbody>
-</table>
-</div></td>
-  </tr>
-  </tbody>
-</table>
-</div></td>
-  <td><div>mee.csl</div></td>
-  <td><div>references.bib</div></td>
-  </tr>
-  </tbody>
-</table>
-
-<pre lang="{r,"><code>  # devtools::install_github("cboettig/knitcitations@v1")
-  library(knitcitations); cleanbib()
-  cite_options(citation_format = "pandoc", check.entries=FALSE)
-  library(bibtex)
-</code></pre>
-<h1><a id="user-content-abstract" class="anchor" aria-hidden="true" href="#abstract"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Abstract</h1>
-<p><em>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
+*Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
 Mel erat falli ut.
@@
 An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea.
-Ponderum vivendum te nec, id agam brute disputando mei.</em></p>
-<h1><a id="user-content-introduction" class="anchor" aria-hidden="true" href="#introduction"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Introduction</h1>
-<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
+Ponderum vivendum te nec, id agam brute disputando mei.*
+
+# Introduction
+
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
 Mel erat falli ut.
@@
 An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea.
-Ponderum vivendum te nec, id agam brute disputando mei.</p>
-<p>Putant numquam tacimates at eum.
+Ponderum vivendum te nec, id agam brute disputando mei.
+
+Putant numquam tacimates at eum.
 Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu.
@@
 Posse dicunt id usu.
-Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.</p>
-<p>Has audire salutandi no, ut eam dicat libris dicunt.
+Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.
+
+Has audire salutandi no, ut eam dicat libris dicunt.
 Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea.
@@
 At postea utamur mel, eius nonumes percipitur at vis.
-Numquam similique in per, te quo saepe utroque pericula.</p>
-<p>Ea nonumy volumus usu, no mel inermis dissentias.
+Numquam similique in per, te quo saepe utroque pericula.
+
+Ea nonumy volumus usu, no mel inermis dissentias.
 Dico partiendo vituperatoribus eum et.
@@
 Eu eum oratio altera option, ad mea ignota scriptorem.
-Ne suas latine vix, eos oblique sanctus pertinax cu.</p>
-<h1><a id="user-content-methods" class="anchor" aria-hidden="true" href="#methods"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Methods</h1>
-<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
+Ne suas latine vix, eos oblique sanctus pertinax cu.
+
+# Methods
+
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
 Mel erat falli ut.
@@
 Posse dicunt id usu.
-Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.</p>
-<h2><a id="user-content-equations" class="anchor" aria-hidden="true" href="#equations"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Equations</h2>
-<p>The deterministic part of the model is defined by this <strong>in-line equation</strong> as
-$\mu_i = \beta_0 + \beta_1x$, and the stochastic part by the <strong>centered equation</strong>:</p>
-<p>$$ \frac{1}{\sqrt{2\pi}\sigma}e^{-(x-\mu_i)^2/(2\sigma^2)} $$</p>
-<h2><a id="user-content-tables" class="anchor" aria-hidden="true" href="#tables"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Tables</h2>
-<pre lang="{r"><code>library(knitr)
+Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.
 
-x &lt;- rnorm(100)
-y &lt;- 2*x + rnorm(100)
-out &lt;- lm(y ~ x)
+## Equations
+
+The deterministic part of the model is defined by this **in-line equation** as 
+$\mu_i = \beta_0 + \beta_1x$, and the stochastic part by the **centered equation**:
+
+$$ \frac{1}{\sqrt{2\pi}\sigma}e^{-(x-\mu_i)^2/(2\sigma^2)} $$
+
+## Tables
+
+```{r kable, echo=FALSE}
+library(knitr)
+
+x <- rnorm(100)
+y <- 2*x + rnorm(100)
+out <- lm(y ~ x)
 kable(summary(out)$coef, digits=2, caption="This is a GLM summary table.")
-</code></pre>
-<pre lang="{r"><code>library(xtable)
-tab &lt;- xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
+```
+
+```{r xtable, results="asis", echo=FALSE, eval=FALSE, message=FALSE}
+library(xtable)
+tab <- xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
               caption="This is a GLM summary table.")
 print(tab, type="latex")
-</code></pre>
-<h2><a id="user-content-plots" class="anchor" aria-hidden="true" href="#plots"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Plots</h2>
-<pre lang="{r"><code>  plot(x, y)
+```
+
+## Plots
+
+```{r carDataPlot, echo=FALSE, fig.cap="Relationship between x and y. The solid line is least-squares linear regression.", fig.width=4, fig.height=4}
+  plot(x, y)
   abline(out)
-</code></pre>
-<h2><a id="user-content-citations" class="anchor" aria-hidden="true" href="#citations"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Citations</h2>
-<p>The relationship was first described by
-<code>r citet("10.1111/j.1461-0248.2005.00827.x")</code>. However, there are also opinions
-that the relationship is spurious <code>r citep("10.1111/j.2041-210x.2012.00264.x")</code>.
-We used R for our calculations <code>r citep(citation())</code>, and we used package <code>knitcitations</code> <code>r citep(citation("knitcitations"))</code> to make the bibliography.</p>
-<h1><a id="user-content-results-and-discussion" class="anchor" aria-hidden="true" href="#results-and-discussion"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>Results and discussion</h1>
-<p>Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
+```
+
+## Citations
+
+The relationship was first described by
+`r citet("10.1111/j.1461-0248.2005.00827.x")`. However, there are also opinions
+that the relationship is spurious `r citep("10.1111/j.2041-210x.2012.00264.x")`.
+We used R for our calculations `r citep(citation())`, and we used package `knitcitations` `r citep(citation("knitcitations"))` to make the bibliography.
+
+# Results and discussion
+
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
 Mel erat falli ut.
@@
 Eu eum oratio altera option, ad mea ignota scriptorem.
-Ne suas latine vix, eos oblique sanctus pertinax cu.</p>
-<h1><a id="user-content-references" class="anchor" aria-hidden="true" href="#references"><svg class="octicon octicon-link" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9h1v1H4c-1.5 0-3-1.69-3-3.5S2.55 3 4 3h4c1.45 0 3 1.69 3 3.5 0 1.41-.91 2.72-2 3.25V8.59c.58-.45 1-1.27 1-2.09C10 5.22 8.98 4 8 4H4c-.98 0-2 1.22-2 2.5S3 9 4 9zm9-3h-1v1h1c1 0 2 1.22 2 2.5S13.98 12 13 12H9c-.98 0-2-1.22-2-2.5 0-.83.42-1.64 1-2.09V6.25c-1.09.53-2 1.84-2 3.25C6 11.31 7.55 13 9 13h4c1.45 0 3-1.69 3-3.5S14.5 6 13 6z"></path></svg></a>References</h1>
-<pre lang="{r,"><code>  write.bibtex(file="references.bib")
-</code></pre>
-</article>
-  </div>
+Ne suas latine vix, eos oblique sanctus pertinax cu.
 
-  </div>
+# References
 
-  <details class="details-reset details-overlay details-overlay-dark">
-    <summary data-hotkey="l" aria-label="Jump to line"></summary>
-    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast linejump" aria-label="Jump to line">
-      <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-jump-to-line-form Box-body d-flex" action="" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
-        <input class="form-control flex-auto mr-3 linejump-input js-jump-to-line-field" type="text" placeholder="Jump to line&hellip;" aria-label="Jump to line" autofocus>
-        <button type="submit" class="btn" data-close-dialog>Go</button>
-</form>    </details-dialog>
-  </details>
-
-  </div>
-  <div class="modal-backdrop js-touch-events"></div>
-</div>
-
-    </div>
-  </div>
-
-  </div>
-
-<div class="footer container-lg px-3" role="contentinfo">
-  <div class="position-relative d-flex flex-justify-between pt-6 pb-2 mt-6 f6 text-gray border-top border-gray-light ">
-    <ul class="list-style-none d-flex flex-wrap ">
-      <li class="mr-3">&copy; 2018 <span title="0.17379s from unicorn-6bfd5c759c-j6nwh">GitHub</span>, Inc.</li>
-        <li class="mr-3"><a data-ga-click="Footer, go to terms, text:terms" href="https://github.com/site/terms">Terms</a></li>
-        <li class="mr-3"><a data-ga-click="Footer, go to privacy, text:privacy" href="https://github.com/site/privacy">Privacy</a></li>
-        <li class="mr-3"><a href="https://help.github.com/articles/github-security/" data-ga-click="Footer, go to security, text:security">Security</a></li>
-        <li class="mr-3"><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
-        <li><a data-ga-click="Footer, go to help, text:help" href="https://help.github.com">Help</a></li>
-    </ul>
-
-    <a aria-label="Homepage" title="GitHub" class="footer-octicon mr-lg-4" href="https://github.com">
-      <svg height="24" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="24" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
-</a>
-   <ul class="list-style-none d-flex flex-wrap ">
-        <li class="mr-3"><a data-ga-click="Footer, go to contact, text:contact" href="https://github.com/contact">Contact GitHub</a></li>
-        <li class="mr-3"><a href="https://github.com/pricing" data-ga-click="Footer, go to Pricing, text:Pricing">Pricing</a></li>
-      <li class="mr-3"><a href="https://developer.github.com" data-ga-click="Footer, go to api, text:api">API</a></li>
-      <li class="mr-3"><a href="https://training.github.com" data-ga-click="Footer, go to training, text:training">Training</a></li>
-        <li class="mr-3"><a href="https://blog.github.com" data-ga-click="Footer, go to blog, text:blog">Blog</a></li>
-        <li><a data-ga-click="Footer, go to about, text:about" href="https://github.com/about">About</a></li>
-
-    </ul>
-  </div>
-  <div class="d-flex flex-justify-center pb-6">
-    <span class="f6 text-gray-light"></span>
-  </div>
-</div>
-
-  <div id="ajax-error-message" class="ajax-error-message flash flash-error">
-    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
-    <button type="button" class="flash-close js-ajax-error-dismiss" aria-label="Dismiss error">
-      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-    </button>
-    You can’t perform that action at this time.
-  </div>
-
-    <script crossorigin="anonymous" integrity="sha512-RJ1ufbxsSbKjRCyYvinsPNKvTBvcvvKUvEOJ8g+GjtWI5SuRr+QPBlZcvRDws4H9YwAgdQFcGxfL8UbwEfdI7A==" type="application/javascript" src="https://assets-cdn.github.com/assets/compat-daf14de28fadf1e2bc40d100cb773e2b.js"></script>
-    <script crossorigin="anonymous" integrity="sha512-IC5Ai6c7cUBfMx54JUAsIjA7VroipzkizlZ8F6/0efsGGyZStweZV7bX9bxSFL07nUNLfwrKSEysVIijX+CeUw==" type="application/javascript" src="https://assets-cdn.github.com/assets/frameworks-5874e38105ec062c740350eeb96bdd8a.js"></script>
-
-    <script crossorigin="anonymous" async="async" integrity="sha512-/E7YUPwg5s5FmwhSiwtXwNsTUCpjjdcrKoK7UFMQCguTSC71dACKl+XDhBftzkBsRra4w+a24G4oU535TieAIA==" type="application/javascript" src="https://assets-cdn.github.com/assets/github-1835546276a57f4d0c3203810d2ec7d6.js"></script>
-
-  <div class="js-stale-session-flash stale-session-flash flash flash-warn flash-banner d-none">
-    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
-    <span class="signed-in-tab-flash">You signed in with another tab or window. <a href="">Reload</a> to refresh your session.</span>
-    <span class="signed-out-tab-flash">You signed out in another tab or window. <a href="">Reload</a> to refresh your session.</span>
-  </div>
-  <div class="facebox" id="facebox" style="display:none;">
-  <div class="facebox-popup">
-    <div class="facebox-content" role="dialog" aria-labelledby="facebox-header" aria-describedby="facebox-description">
-    </div>
-    <button type="button" class="facebox-close js-facebox-close" aria-label="Close modal">
-      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-    </button>
-  </div>
-</div>
-
-  <template id="site-details-dialog">
-  <details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark" open>
-    <summary aria-haspopup="dialog" aria-label="Close dialog"></summary>
-    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast">
-      <button class="Box-btn-octicon m-0 btn-octicon position-absolute right-0 top-0" type="button" aria-label="Close dialog" data-close-dialog>
-        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-      </button>
-      <div class="octocat-spinner my-6 js-details-dialog-spinner"></div>
-    </details-dialog>
-  </details>
-</template>
-
-  <div class="Popover js-hovercard-content position-absolute" style="display: none; outline: none;" tabindex="0">
-  <div class="Popover-message Popover-message--bottom-left Popover-message--large Box box-shadow-large" style="width:360px;">
-  </div>
-</div>
-
-<div id="hovercard-aria-description" class="sr-only">
-  Press h to open a hovercard with more details.
-</div>
-
-  </body>
-</html>
+```{r, warning=FALSE, message=FALSE, echo=FALSE} 
+  write.bibtex(file="references.bib")
+```

### 2018-09-21 manuscript/manuscript_template.tex
Updating Rmarkdown template

@@
-<!DOCTYPE html>
-<html lang="en">
-  <head>
-    <meta charset="utf-8">
-  <link rel="dns-prefetch" href="https://assets-cdn.github.com">
-  <link rel="dns-prefetch" href="https://avatars0.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars1.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars2.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://avatars3.githubusercontent.com">
-  <link rel="dns-prefetch" href="https://github-cloud.s3.amazonaws.com">
-  <link rel="dns-prefetch" href="https://user-images.githubusercontent.com/">
+\documentclass[]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={A template for writing a manuscript in Rmarkdown},
+            pdfauthor={James Grecian One; Ian Jonsen Two},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-  <link crossorigin="anonymous" media="all" integrity="sha512-/yZA7MGD9acBi5MmgjnivwjGeiNsmimsI/bhLlK7akrRuw+hMxNpJoQEMO9Zt0Nq6ZRu1m1NGV6r95Ib0zx7Qw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/frameworks-1ca00d32d1a8adc78ae7bb6677410eb1.css" />
-  <link crossorigin="anonymous" media="all" integrity="sha512-pHF1luoMSUFxvz63bW3jEbbifYl/pruHUw+kljThAPi2g0nhgMdvWj4bQRh4O8MYp9NR60XYcylaLXmYA8YXSw==" rel="stylesheet" href="https://assets-cdn.github.com/assets/github-5043b3d96d50b119b971c2cdde4e0a62.css" />
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-  <meta name="viewport" content="width=device-width">
+%%% Change title format to be more compact
+\usepackage{titling}
 
-  <title>Blog/manuscript_template.tex at master · petrkeil/Blog</title>
-    <meta name="description" content="This repository contains codes for all of my blog posts since March 11 2015. - petrkeil/Blog">
-    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub">
-  <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub">
-  <meta property="fb:app_id" content="1401488693436528">
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
 
-    <meta property="og:image" content="https://avatars2.githubusercontent.com/u/5421227?s=400&amp;v=4" /><meta property="og:site_name" content="GitHub" /><meta property="og:type" content="object" /><meta property="og:title" content="petrkeil/Blog" /><meta property="og:url" content="https://github.com/petrkeil/Blog" /><meta property="og:description" content="This repository contains codes for all of my blog posts since March 11 2015.
-- petrkeil/Blog" />
+\setlength{\droptitle}{-2em}
 
-  <link rel="assets" href="https://assets-cdn.github.com/">
-  <link rel="web-socket" href="wss://live.github.com/_sockets/VjI6MzE5MjkzMDMyOjcxODYyYzE1ZGViNTZjN2U2YjQzMjlhZWYzYzI0Mjk2MjFjODZlN2QzMzM0YmVkYzI2NWJhNDYyY2JkYjc2MTM=--6f13a55f6f2aea699ea77deb92d45357f788dd6a">
-  <meta name="pjax-timeout" content="1000">
-  <link rel="sudo-modal" href="/sessions/sudo_modal">
-  <meta name="request-id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" data-pjax-transient>
+  \title{A template for writing a manuscript in Rmarkdown}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+    \author{James Grecian One\footnote{University of Somewhere} \\ Ian Jonsen Two\footnote{University of Nowhere}}
+    \preauthor{\centering\large\emph}
+  \postauthor{\par}
+      \predate{\centering\large\emph}
+  \postdate{\par}
+    \date{21 September 2018}
 
-  <meta name="selected-link" value="repo_source" data-pjax-transient>
+\usepackage{lineno}
+\linenumbers
 
-      <meta name="google-site-verification" content="KT5gs8h0wvaagLKAVWq8bbeNwnZZK1r1XQysX3xurLU">
-    <meta name="google-site-verification" content="ZzhVyEFwb7w3e0-uOTltm8Jsck2F5StVihD0exw2fsA">
-    <meta name="google-site-verification" content="GXs5KoUUkNCoaAZn7wPN-t01Pywp9M3sEjnt_3_ZWPc">
+\begin{document}
+\maketitle
 
-  <meta name="octolytics-host" content="collector.githubapp.com" /><meta name="octolytics-app-id" content="github" /><meta name="octolytics-event-url" content="https://collector.githubapp.com/github-external/browser_event" /><meta name="octolytics-dimension-request_id" content="DECF:7B7C:B3E55E:147C953:5BA52F75" /><meta name="octolytics-dimension-region_edge" content="iad" /><meta name="octolytics-dimension-region_render" content="iad" /><meta name="octolytics-actor-id" content="34245401" /><meta name="octolytics-actor-login" content="jamesgrecian" /><meta name="octolytics-actor-hash" content="821728246d06cdfe784e56dfb8dc2a4447ec5ee2fb7525c8728616156ffa29a2" />
-<meta name="analytics-location" content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" />
+\section{Abstract}\label{abstract}
 
-    <meta name="google-analytics" content="UA-3769691-2">
+\emph{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel
+erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet
+argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
+liberavisse sea. Ponderum vivendum te nec, id agam brute disputando
+mei.}
 
-  <meta class="js-ga-set" name="userId" content="078bbd73f63945865b3a6f9e3c674706" %>
+\section{Introduction}\label{introduction}
 
-<meta class="js-ga-set" name="dimension1" content="Logged In">
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
+falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
+suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
+liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.
 
-      <meta name="hostname" content="github.com">
-    <meta name="user-login" content="jamesgrecian">
+Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
+debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
+singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
+id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
+usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
+conceptam.
 
-      <meta name="expected-hostname" content="github.com">
-    <meta name="js-proxy-site-detection-payload" content="ZjQ2OTM3ZjcwZjc1MzhhMTAyNTFmYmY2MDk5NmJjYjZlM2NjNmMwMmQwYjExOTc1NGVlZDU4YzMzMzBkYmNhNXx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjM0LjI0OC4yMDciLCJyZXF1ZXN0X2lkIjoiREVDRjo3QjdDOkIzRTU1RToxNDdDOTUzOjVCQTUyRjc1IiwidGltZXN0YW1wIjoxNTM3NTUyMjQ2LCJob3N0IjoiZ2l0aHViLmNvbSJ9">
+Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
+quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
+ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
+percipitur at vis. Numquam similique in per, te quo saepe utroque
+pericula.
 
-    <meta name="enabled-features" content="DASHBOARD_V2_LAYOUT_OPT_IN,EXPLORE_DISCOVER_REPOSITORIES,UNIVERSE_BANNER,MARKETPLACE_PLAN_RESTRICTION_EDITOR,MARKETPLACE_RETARGETING,QUOTE_MARKDOWN">
+Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
+vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
+gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
+suas latine vix, eos oblique sanctus pertinax cu.
 
-  <meta name="html-safe-nonce" content="4d33eb369dbc9e939c0c70269799ff90a62c9762">
+\section{Methods}\label{methods}
 
-  <meta http-equiv="x-pjax-version" content="3842ef7af97baac02526bd1bb609fd99">
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
+falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
+suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
+liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.
 
-      <link href="https://github.com/petrkeil/Blog/commits/master.atom" rel="alternate" title="Recent Commits to Blog:master" type="application/atom+xml">
+Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
+debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
+singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
+id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
+usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
+conceptam.
 
-  <meta name="go-import" content="github.com/petrkeil/Blog git https://github.com/petrkeil/Blog.git">
+\subsection{Equations}\label{equations}
 
-  <meta name="octolytics-dimension-user_id" content="5421227" /><meta name="octolytics-dimension-user_login" content="petrkeil" /><meta name="octolytics-dimension-repository_id" content="32012442" /><meta name="octolytics-dimension-repository_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_public" content="true" /><meta name="octolytics-dimension-repository_is_fork" content="false" /><meta name="octolytics-dimension-repository_network_root_id" content="32012442" /><meta name="octolytics-dimension-repository_network_root_nwo" content="petrkeil/Blog" /><meta name="octolytics-dimension-repository_explore_github_marketplace_ci_cta_shown" content="false" />
+The deterministic part of the model is defined by this \textbf{in-line
+equation} as \(\mu_i = \beta_0 + \beta_1x\), and the stochastic part by
+the \textbf{centered equation}:
 
-    <link rel="canonical" href="https://github.com/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.tex" data-pjax-transient>
+\[ \frac{1}{\sqrt{2\pi}\sigma}e^{-(x-\mu_i)^2/(2\sigma^2)} \]
 
-  <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">
+\subsection{Tables}\label{tables}
 
-  <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{This is a GLM summary table.}\tabularnewline
+\toprule
+& Estimate & Std. Error & t value &
+Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& Estimate & Std. Error & t value &
+Pr(\textgreater{}\textbar{}t\textbar{})\tabularnewline
+\midrule
+\endhead
+(Intercept) & 0.05 & 0.1 & 0.48 & 0.63\tabularnewline
+x & 1.96 & 0.1 & 19.68 & 0.00\tabularnewline
+\bottomrule
+\end{longtable}
 
-  <link rel="mask-icon" href="https://assets-cdn.github.com/pinned-octocat.svg" color="#000000">
-  <link rel="icon" type="image/x-icon" class="js-site-favicon" href="https://assets-cdn.github.com/favicon.ico">
+\subsection{Plots}\label{plots}
 
-<meta name="theme-color" content="#1e2327">
+\begin{figure}[htbp]
+\centering
+\includegraphics{manuscript_template_files/figure-latex/carDataPlot-1.pdf}
+\caption{Relationship between x and y. The solid line is least-squares
+linear regression.}
+\end{figure}
 
-  <link rel="manifest" href="/manifest.json" crossOrigin="use-credentials">
+\subsection{Citations}\label{citations}
 
-  </head>
+The relationship was first described by @Halpern\_2006. However, there
+are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
+We used R for our calculations {[}@R\_Core\_Team\_2017{]}, and we used
+package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
+bibliography.
 
-  <body class="logged-in env-production page-blob">
+\section{Results and discussion}\label{results-and-discussion}
 
-  <div class="position-relative js-header-wrapper ">
-    <a href="#start-of-content" tabindex="1" class="p-3 bg-blue text-white show-on-focus js-skip-to-content">Skip to content</a>
-    <div id="js-pjax-loader-bar" class="pjax-loader-bar"><div class="progress"></div></div>
+Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat
+falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum
+suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
+liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.
 
-<header class="Header  f5" role="banner">
-  <div class="d-flex flex-justify-between px-3 ">
-    <div class="d-flex flex-justify-between ">
-      <div class="">
-        <a class="header-logo-invertocat" href="https://github.com/" data-hotkey="g d" aria-label="Homepage" data-ga-click="Header, go to dashboard, icon:logo">
-  <svg height="32" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="32" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
-</a>
+Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
+debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
+singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
+id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
+usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
+conceptam.
 
-      </div>
+Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
+quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
+ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
+percipitur at vis. Numquam similique in per, te quo saepe utroque
+pericula.
 
-    </div>
+Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
+vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
+gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
+suas latine vix, eos oblique sanctus pertinax cu.
 
-    <div class="HeaderMenu d-flex flex-justify-between flex-auto">
-      <div class="d-flex">
-            <div class="">
-              <div class="header-search scoped-search site-scoped-search js-site-search position-relative js-jump-to"
-  role="combobox"
-  aria-owns="jump-to-results"
-  aria-label="Search or jump to"
-  aria-haspopup="listbox"
-  aria-expanded="false"
->
-  <div class="position-relative">
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-site-search-form" data-scope-type="Repository" data-scope-id="32012442" data-scoped-search-url="/petrkeil/Blog/search" data-unscoped-search-url="/search" action="/petrkeil/Blog/search" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
-      <label class="form-control header-search-wrapper header-search-wrapper-jump-to position-relative d-flex flex-justify-between flex-items-center js-chromeless-input-container">
-        <input type="text"
-          class="form-control header-search-input jump-to-field js-jump-to-field js-site-search-focus js-site-search-field is-clearable"
-          data-hotkey="s,/"
-          name="q"
-          value=""
-          placeholder="Search or jump to…"
-          data-unscoped-placeholder="Search or jump to…"
-          data-scoped-placeholder="Search or jump to…"
-          autocapitalize="off"
-          aria-autocomplete="list"
-          aria-controls="jump-to-results"
-          data-jump-to-suggestions-path="/_graphql/GetSuggestedNavigationDestinations#csrf-token=zcJUvtqaKw72uX3+FzR9OQAX21rWJn+bojDj6/4pZ0qqkkAAzhaUHBTvUq9jh6W93uzACkd2Vi0N1v0kqc+Jpw=="
-          spellcheck="false"
-          autocomplete="off"
-          >
-          <input type="hidden" class="js-site-search-type-field" name="type" >
-            <img src="https://assets-cdn.github.com/images/search-shortcut-hint.svg" alt="" class="mr-2 header-search-key-slash">
+\section{References}\label{references}
 
-            <div class="Box position-absolute overflow-hidden d-none jump-to-suggestions js-jump-to-suggestions-container">
-              <ul class="d-none js-jump-to-suggestions-template-container">
-                <li class="d-flex flex-justify-start flex-items-center p-0 f5 navigation-item js-navigation-item" role="option">
-                  <a tabindex="-1" class="no-underline d-flex flex-auto flex-items-center p-2 jump-to-suggestions-path js-jump-to-suggestion-path js-navigation-open" href="">
-                    <div class="jump-to-octicon js-jump-to-octicon mr-2 text-center d-none">
-                      <svg height="16" width="16" class="octicon octicon-repo flex-shrink-0 js-jump-to-octicon-repo d-none" title="Repository" aria-label="Repository" viewBox="0 0 12 16" version="1.1" role="img"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
-                      <svg height="16" width="16" class="octicon octicon-project flex-shrink-0 js-jump-to-octicon-project d-none" title="Project" aria-label="Project" viewBox="0 0 15 16" version="1.1" role="img"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
-                      <svg height="16" width="16" class="octicon octicon-search flex-shrink-0 js-jump-to-octicon-search d-none" title="Search" aria-label="Search" viewBox="0 0 16 16" version="1.1" role="img"><path fill-rule="evenodd" d="M15.7 13.3l-3.81-3.83A5.93 5.93 0 0 0 13 6c0-3.31-2.69-6-6-6S1 2.69 1 6s2.69 6 6 6c1.3 0 2.48-.41 3.47-1.11l3.83 3.81c.19.2.45.3.7.3.25 0 .52-.09.7-.3a.996.996 0 0 0 0-1.41v.01zM7 10.7c-2.59 0-4.7-2.11-4.7-4.7 0-2.59 2.11-4.7 4.7-4.7 2.59 0 4.7 2.11 4.7 4.7 0 2.59-2.11 4.7-4.7 4.7z"/></svg>
-                    </div>
-
-                    <img class="avatar mr-2 flex-shrink-0 js-jump-to-suggestion-avatar d-none" alt="" aria-label="Team" src="" width="28" height="28">
-
-                    <div class="jump-to-suggestion-name js-jump-to-suggestion-name flex-auto overflow-hidden text-left no-wrap css-truncate css-truncate-target">
-                    </div>
-
-                    <div class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none js-jump-to-badge-search">
-                      <span class="js-jump-to-badge-search-text-default d-none" aria-label="in this repository">
-                        In this repository
-                      </span>
-                      <span class="js-jump-to-badge-search-text-global d-none" aria-label="in all of GitHub">
-                        All GitHub
-                      </span>
-                      <span aria-hidden="true" class="d-inline-block ml-1 v-align-middle">↵</span>
-                    </div>
-
-                    <div aria-hidden="true" class="border rounded-1 flex-shrink-0 bg-gray px-1 text-gray-light ml-1 f6 d-none d-on-nav-focus js-jump-to-badge-jump">
-                      Jump to
-                      <span class="d-inline-block ml-1 v-align-middle">↵</span>
-                    </div>
-                  </a>
-                </li>
-              </ul>
-              <ul class="d-none js-jump-to-no-results-template-container">
-                <li class="d-flex flex-justify-center flex-items-center p-3 f5 d-none">
-                  <span class="text-gray">No suggested jump to results</span>
-                </li>
-              </ul>
-
-              <ul id="jump-to-results" role="listbox" class="js-navigation-container jump-to-suggestions-results-container js-jump-to-suggestions-results-container" >
-                <li class="d-flex flex-justify-center flex-items-center p-0 f5">
-                  <img src="https://assets-cdn.github.com/images/spinners/octocat-spinner-128.gif" alt="Octocat Spinner Icon" class="m-2" width="28">
-                </li>
-              </ul>
-            </div>
-      </label>
-</form>  </div>
-</div>
-
-            </div>
-
-          <ul class="d-flex pl-2 flex-items-center text-bold list-style-none" role="navigation">
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g p" data-ga-click="Header, click, Nav menu - item:pulls context:user" aria-label="Pull requests you created" data-selected-links="/pulls /pulls/assigned /pulls/mentioned /pulls" href="/pulls">
-                Pull requests
-</a>            </li>
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-hotkey="g i" data-ga-click="Header, click, Nav menu - item:issues context:user" aria-label="Issues you created" data-selected-links="/issues /issues/assigned /issues/mentioned /issues" href="/issues">
-                Issues
-</a>            </li>
-              <li>
-                <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:marketplace context:user" data-octo-click="marketplace_click" data-octo-dimensions="location:nav_bar" data-selected-links=" /marketplace" href="/marketplace">
-                   Marketplace
-</a>              </li>
-            <li>
-              <a class="js-selected-navigation-item HeaderNavlink px-2" data-ga-click="Header, click, Nav menu - item:explore" data-selected-links="/explore /trending /trending/developers /integrations /integrations/feature/code /integrations/feature/collaborate /integrations/feature/ship showcases showcases_search showcases_landing /explore" href="/explore">
-                Explore
-</a>            </li>
-          </ul>
-      </div>
-
-      <div class="d-flex">
-
-<ul class="user-nav d-flex flex-items-center list-style-none" id="user-links">
-  <li class="dropdown">
-    <span class="d-inline-block  px-2">
-
-    <a aria-label="You have no unread notifications" class="notification-indicator tooltipped tooltipped-s  js-socket-channel js-notification-indicator" data-hotkey="g n" data-ga-click="Header, go to notifications, icon:read" data-channel="notification-changed:34245401" href="/notifications">
-        <span class="mail-status "></span>
-        <svg class="octicon octicon-bell" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M13.99 11.991v1H0v-1l.73-.58c.769-.769.809-2.547 1.189-4.416.77-3.767 4.077-4.996 4.077-4.996 0-.55.45-1 .999-1 .55 0 1 .45 1 1 0 0 3.387 1.229 4.156 4.996.38 1.879.42 3.657 1.19 4.417l.659.58h-.01zM6.995 15.99c1.11 0 1.999-.89 1.999-1.999H4.996c0 1.11.89 1.999 1.999 1.999z"/></svg>
-</a>
-    </span>
-  </li>
-
-  <li class="dropdown">
-    <details class="details-overlay details-reset d-flex px-2 flex-items-center">
-      <summary class="HeaderNavlink"
-         aria-label="Create new…"
-         data-ga-click="Header, create new, icon:add">
-        <svg class="octicon octicon-plus float-left mr-1 mt-1" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 9H7v5H5V9H0V7h5V2h2v5h5v2z"/></svg>
-        <span class="dropdown-caret mt-1"></span>
-      </summary>
-      <details-menu class="dropdown-menu dropdown-menu-sw">
-
-<a role="menuitem" class="dropdown-item" href="/new" data-ga-click="Header, create new repository">
-  New repository
-</a>
-
-  <a role="menuitem" class="dropdown-item" href="/new/import" data-ga-click="Header, import a repository">
-    Import repository
-  </a>
-
-<a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, create new gist">
-  New gist
-</a>
-
-  <a role="menuitem" class="dropdown-item" href="/organizations/new" data-ga-click="Header, create new organization">
-    New organization
-  </a>
-
-  <div class="dropdown-divider"></div>
-  <div class="dropdown-header">
-    <span title="petrkeil/Blog">This repository</span>
-  </div>
-    <a role="menuitem" class="dropdown-item" href="/petrkeil/Blog/issues/new" data-ga-click="Header, create new issue">
-      New issue
-    </a>
-
-      </details-menu>
-    </details>
-  </li>
-
-  <li class="dropdown">
-
-    <details class="details-overlay details-reset d-flex pl-2 flex-items-center">
-      <summary class="HeaderNavlink name mt-1"
-        aria-label="View profile and more"
-        data-ga-click="Header, show menu, icon:avatar">
-        <img alt="@jamesgrecian" class="avatar float-left mr-1" src="https://avatars2.githubusercontent.com/u/34245401?s=40&amp;v=4" height="20" width="20">
-        <span class="dropdown-caret"></span>
-      </summary>
-      <details-menu class="dropdown-menu dropdown-menu-sw">
-        <ul>
-          <li class="header-nav-current-user css-truncate"><a role="menuitem" class="no-underline user-profile-link px-3 pt-2 pb-2 mb-n2 mt-n1 d-block" href="/jamesgrecian" data-ga-click="Header, go to profile, text:Signed in as">Signed in as <strong class="css-truncate-target">jamesgrecian</strong></a></li>
-          <li class="dropdown-divider"></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian" data-ga-click="Header, go to profile, text:your profile">Your profile</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=repositories" data-ga-click="Header, go to repositories, text:your repositories">Your repositories</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/jamesgrecian?tab=stars" data-ga-click="Header, go to starred repos, text:your stars">Your stars</a></li>
-            <li><a role="menuitem" class="dropdown-item" href="https://gist.github.com/" data-ga-click="Header, your gists, text:your gists">Your gists</a></li>
-          <li class="dropdown-divider"></li>
-          <li><a role="menuitem" class="dropdown-item" href="https://help.github.com" data-ga-click="Header, go to help, text:help">Help</a></li>
-          <li><a role="menuitem" class="dropdown-item" href="/settings/profile" data-ga-click="Header, go to settings, icon:settings">Settings</a></li>
-          <li>
-            <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="logout-form" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="OM5YtlFU+S06U7ppNLcVxzqWiaBef+wxiPcpMrVBU5MT4j+3rc/PsPef/kanszc+s9gxETZMWv4UhgAFQxQtTA==" />
-              <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout" role="menuitem">
-                Sign out
-              </button>
-</form>          </li>
-        </ul>
-      </details-menu>
-    </details>
-  </li>
-</ul>
-
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="sr-only right-0" action="/logout" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="N1zKEjZbcCo1MI7p6SB0skpuMDcaIk1EZ0F9bAHxVPkccK0TysBGt/j8ysZ6JFZLwyCIhnIR+4v7MFRb96QqJg==" />
-          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
-            Sign out
-          </button>
-</form>      </div>
-    </div>
-  </div>
-</header>
-
-  </div>
-
-  <div id="start-of-content" class="show-on-focus"></div>
-
-    <div id="js-flash-container">
-
-</div>
-
-  <div role="main" class="application-main ">
-        <div itemscope itemtype="http://schema.org/SoftwareSourceCode" class="">
-    <div id="js-repo-pjax-container" data-pjax-container >
-
-  <div class="pagehead repohead instapaper_ignore readability-menu experiment-repo-nav  ">
-    <div class="repohead-details-container clearfix container">
-
-      <ul class="pagehead-actions">
-  <li>
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form data-autosubmit="true" data-remote="true" class="js-social-container" action="/notifications/subscribe" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="waV7OqLCkNQ0PEw4EE9fOf24fp4CwT8NUr+psybqPnPC2pmp6iqyjyCcpVUE5PcRzsja2lcTlEgrF7iTkvBrEw==" />      <input type="hidden" name="repository_id" id="repository_id" value="32012442" class="form-control" />
-
-        <div class="select-menu js-menu-container js-select-menu">
-          <a href="/petrkeil/Blog/subscription"
-            class="btn btn-sm btn-with-count select-menu-button js-menu-target"
-            role="button"
-            aria-haspopup="true"
-            aria-expanded="false"
-            aria-label="Toggle repository notifications menu"
-            data-ga-click="Repository, click Watch settings, action:blob#show">
-            <span class="js-select-button">
-                <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                Watch
-            </span>
-          </a>
-          <a class="social-count js-social-count"
-            href="/petrkeil/Blog/watchers"
-            aria-label="17 users are watching this repository">
-            17
-          </a>
-
-        <div class="select-menu-modal-holder">
-          <div class="select-menu-modal subscription-menu-modal js-menu-content">
-            <div class="select-menu-header js-navigation-enable" tabindex="-1">
-              <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-              <span class="select-menu-title">Notifications</span>
-            </div>
-
-              <div class="select-menu-list js-navigation-container" role="menu">
-
-                <div class="select-menu-item js-navigation-item selected" role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_included" value="included" checked="checked" />
-                    <span class="select-menu-item-heading">Not watching</span>
-                    <span class="description">Be notified when participating or @mentioned.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                      Watch
-                    </span>
-                  </div>
-                </div>
-
-                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_subscribed" value="subscribed" />
-                    <span class="select-menu-item-heading">Watching</span>
-                    <span class="description">Be notified of all conversations.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-eye v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.06 2C3 2 0 8 0 8s3 6 8.06 6C13 14 16 8 16 8s-3-6-7.94-6zM8 12c-2.2 0-4-1.78-4-4 0-2.2 1.8-4 4-4 2.22 0 4 1.8 4 4 0 2.22-1.78 4-4 4zm2-4c0 1.11-.89 2-2 2-1.11 0-2-.89-2-2 0-1.11.89-2 2-2 1.11 0 2 .89 2 2z"/></svg>
-                        Unwatch
-                    </span>
-                  </div>
-                </div>
-
-                <div class="select-menu-item js-navigation-item " role="menuitem" tabindex="0">
-                  <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-                  <div class="select-menu-item-text">
-                    <input type="radio" name="do" id="do_ignore" value="ignore" />
-                    <span class="select-menu-item-heading">Ignoring</span>
-                    <span class="description">Never be notified.</span>
-                    <span class="js-select-button-text hidden-select-button-text">
-                      <svg class="octicon octicon-mute v-align-text-bottom" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 2.81v10.38c0 .67-.81 1-1.28.53L3 10H1c-.55 0-1-.45-1-1V7c0-.55.45-1 1-1h2l3.72-3.72C7.19 1.81 8 2.14 8 2.81zm7.53 3.22l-1.06-1.06-1.97 1.97-1.97-1.97-1.06 1.06L11.44 8 9.47 9.97l1.06 1.06 1.97-1.97 1.97 1.97 1.06-1.06L13.56 8l1.97-1.97z"/></svg>
-                        Stop ignoring
-                    </span>
-                  </div>
-                </div>
-
-              </div>
-
-            </div>
-          </div>
-        </div>
-</form>
-  </li>
-
-  <li>
-
-  <div class="js-toggler-container js-social-container starring-container ">
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="starred js-social-form" action="/petrkeil/Blog/unstar" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="xltxbluajNFId7AvsA2kLFrwH068xBSLr0PJCzWLHSVuVHviRX8JtJe7LUq7jyGz8hjgprutqW0baAXFH/fXlw==" />
-      <input type="hidden" name="context" value="repository"></input>
-      <button
-        type="submit"
-        class="btn btn-sm btn-with-count js-toggler-target"
-        aria-label="Unstar this repository" title="Unstar petrkeil/Blog"
-        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
-        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
-        Unstar
-      </button>
-        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
-           aria-label="79 users starred this repository">
-          79
-        </a>
-</form>
-    <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="unstarred js-social-form" action="/petrkeil/Blog/star" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="cPLIa0QY+qYMlMwi/9bU+C/A9mTe3RprTTukgLuaBKX90LZZw9U2Ohg/yx0Ept1Tuk3AqWMYKBq3tiwlu7Qd6w==" />
-      <input type="hidden" name="context" value="repository"></input>
-      <button
-        type="submit"
-        class="btn btn-sm btn-with-count js-toggler-target"
-        aria-label="Star this repository" title="Star petrkeil/Blog"
-        data-ga-click="Repository, click star button, action:blob#show; text:Star">
-        <svg class="octicon octicon-star v-align-text-bottom" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74L14 6z"/></svg>
-        Star
-      </button>
-        <a class="social-count js-social-count" href="/petrkeil/Blog/stargazers"
-           aria-label="79 users starred this repository">
-          79
-        </a>
-</form>  </div>
-
-  </li>
-
-  <li>
-          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="btn-with-count" action="/petrkeil/Blog/fork" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="PsH2GGamjWRUveFXkgE8BlYYfdPSGso9/BRONJENUajkIBDbzTsY7NHJx47nqTYVYbC1cjZ82VQx/kkPGMw64Q==" />
-            <button
-                type="submit"
-                class="btn btn-sm btn-with-count"
-                data-ga-click="Repository, show fork modal, action:blob#show; text:Fork"
-                title="Fork your own copy of petrkeil/Blog to your account"
-                aria-label="Fork your own copy of petrkeil/Blog to your account">
-              <svg class="octicon octicon-repo-forked v-align-text-bottom" viewBox="0 0 10 16" version="1.1" width="10" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8 1a1.993 1.993 0 0 0-1 3.72V6L5 8 3 6V4.72A1.993 1.993 0 0 0 2 1a1.993 1.993 0 0 0-1 3.72V6.5l3 3v1.78A1.993 1.993 0 0 0 5 15a1.993 1.993 0 0 0 1-3.72V9.5l3-3V4.72A1.993 1.993 0 0 0 8 1zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3 10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm3-10c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
-              Fork
-            </button>
-</form>
-    <a href="/petrkeil/Blog/network/members" class="social-count"
-       aria-label="130 users forked this repository">
-      130
-    </a>
-  </li>
-</ul>
-
-      <h1 class="public ">
-  <svg class="octicon octicon-repo" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M4 9H3V8h1v1zm0-3H3v1h1V6zm0-2H3v1h1V4zm0-2H3v1h1V2zm8-1v12c0 .55-.45 1-1 1H6v2l-1.5-1.5L3 16v-2H1c-.55 0-1-.45-1-1V1c0-.55.45-1 1-1h10c.55 0 1 .45 1 1zm-1 10H1v2h2v-1h3v1h5v-2zm0-10H2v9h9V1z"/></svg>
-  <span class="author" itemprop="author"><a class="url fn" rel="author" href="/petrkeil">petrkeil</a></span><!--
---><span class="path-divider">/</span><!--
---><strong itemprop="name"><a data-pjax="#js-repo-pjax-container" href="/petrkeil/Blog">Blog</a></strong>
-
-</h1>
-
-    </div>
-
-<nav class="reponav js-repo-nav js-sidenav-container-pjax container"
-     itemscope
-     itemtype="http://schema.org/BreadcrumbList"
-     role="navigation"
-     data-pjax="#js-repo-pjax-container">
-
-  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-    <a class="js-selected-navigation-item selected reponav-item" itemprop="url" data-hotkey="g c" data-selected-links="repo_source repo_downloads repo_commits repo_releases repo_tags repo_branches repo_packages /petrkeil/Blog" href="/petrkeil/Blog">
-      <svg class="octicon octicon-code" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M9.5 3L8 4.5 11.5 8 8 11.5 9.5 13 14 8 9.5 3zm-5 0L0 8l4.5 5L6 11.5 2.5 8 6 4.5 4.5 3z"/></svg>
-      <span itemprop="name">Code</span>
-      <meta itemprop="position" content="1">
-</a>  </span>
-
-    <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-      <a itemprop="url" data-hotkey="g i" class="js-selected-navigation-item reponav-item" data-selected-links="repo_issues repo_labels repo_milestones /petrkeil/Blog/issues" href="/petrkeil/Blog/issues">
-        <svg class="octicon octicon-issue-opened" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7 2.3c3.14 0 5.7 2.56 5.7 5.7s-2.56 5.7-5.7 5.7A5.71 5.71 0 0 1 1.3 8c0-3.14 2.56-5.7 5.7-5.7zM7 1C3.14 1 0 4.14 0 8s3.14 7 7 7 7-3.14 7-7-3.14-7-7-7zm1 3H6v5h2V4zm0 6H6v2h2v-2z"/></svg>
-        <span itemprop="name">Issues</span>
-        <span class="Counter">1</span>
-        <meta itemprop="position" content="2">
-</a>    </span>
-
-  <span itemscope itemtype="http://schema.org/ListItem" itemprop="itemListElement">
-    <a data-hotkey="g p" itemprop="url" class="js-selected-navigation-item reponav-item" data-selected-links="repo_pulls checks /petrkeil/Blog/pulls" href="/petrkeil/Blog/pulls">
-      <svg class="octicon octicon-git-pull-request" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 11.28V5c-.03-.78-.34-1.47-.94-2.06C9.46 2.35 8.78 2.03 8 2H7V0L4 3l3 3V4h1c.27.02.48.11.69.31.21.2.3.42.31.69v6.28A1.993 1.993 0 0 0 10 15a1.993 1.993 0 0 0 1-3.72zm-1 2.92c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zM4 3c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v6.56A1.993 1.993 0 0 0 2 15a1.993 1.993 0 0 0 1-3.72V4.72c.59-.34 1-.98 1-1.72zm-.8 10c0 .66-.55 1.2-1.2 1.2-.65 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2zM2 4.2C1.34 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"/></svg>
-      <span itemprop="name">Pull requests</span>
-      <span class="Counter">0</span>
-      <meta itemprop="position" content="3">
-</a>  </span>
-
-    <a data-hotkey="g b" class="js-selected-navigation-item reponav-item" data-selected-links="repo_projects new_repo_project repo_project /petrkeil/Blog/projects" href="/petrkeil/Blog/projects">
-      <svg class="octicon octicon-project" viewBox="0 0 15 16" version="1.1" width="15" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M10 12h3V2h-3v10zm-4-2h3V2H6v8zm-4 4h3V2H2v12zm-1 1h13V1H1v14zM14 0H1a1 1 0 0 0-1 1v14a1 1 0 0 0 1 1h13a1 1 0 0 0 1-1V1a1 1 0 0 0-1-1z"/></svg>
-      Projects
-      <span class="Counter" >0</span>
-</a>
-
-    <a class="js-selected-navigation-item reponav-item" data-hotkey="g w" data-selected-links="repo_wiki /petrkeil/Blog/wiki" href="/petrkeil/Blog/wiki">
-      <svg class="octicon octicon-book" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M3 5h4v1H3V5zm0 3h4V7H3v1zm0 2h4V9H3v1zm11-5h-4v1h4V5zm0 2h-4v1h4V7zm0 2h-4v1h4V9zm2-6v9c0 .55-.45 1-1 1H9.5l-1 1-1-1H2c-.55 0-1-.45-1-1V3c0-.55.45-1 1-1h5.5l1 1 1-1H15c.55 0 1 .45 1 1zm-8 .5L7.5 3H2v9h6V3.5zm7-.5H9.5l-.5.5V12h6V3z"/></svg>
-      Wiki
-</a>
-  <a class="js-selected-navigation-item reponav-item" data-selected-links="repo_graphs repo_contributors dependency_graph pulse /petrkeil/Blog/pulse" href="/petrkeil/Blog/pulse">
-    <svg class="octicon octicon-graph" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M16 14v1H0V0h1v14h15zM5 13H3V8h2v5zm4 0H7V3h2v10zm4 0h-2V6h2v7z"/></svg>
-    Insights
-</a>
-
-</nav>
-
-  </div>
-
-<div class="container new-discussion-timeline experiment-repo-nav  ">
-  <div class="repository-content ">
-
-  <a class="d-none js-permalink-shortcut" data-hotkey="y" href="/petrkeil/Blog/blob/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.tex">Permalink</a>
-
-  <!-- blob contrib key: blob_contributors:v21:95c861515a089144992f835be9c5e7ee -->
-
-  <div class="file-navigation">
-
-<div class="select-menu branch-select-menu js-menu-container js-select-menu float-left">
-  <button class=" btn btn-sm select-menu-button js-menu-target css-truncate" data-hotkey="w"
-
-    type="button" aria-label="Switch branches or tags" aria-expanded="false" aria-haspopup="true">
-      <i>Branch:</i>
-      <span class="js-select-button css-truncate-target">master</span>
-  </button>
-
-  <div class="select-menu-modal-holder js-menu-content js-navigation-container" data-pjax>
-
-    <div class="select-menu-modal">
-      <div class="select-menu-header">
-        <svg class="octicon octicon-x js-menu-close" role="img" aria-label="Close" viewBox="0 0 12 16" version="1.1" width="12" height="16"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-        <span class="select-menu-title">Switch branches/tags</span>
-      </div>
-
-      <div class="select-menu-filters">
-        <div class="select-menu-text-filter">
-          <input type="text" aria-label="Filter branches/tags" id="context-commitish-filter-field" class="form-control js-filterable-field js-navigation-enable" placeholder="Filter branches/tags">
-        </div>
-        <div class="select-menu-tabs">
-          <ul>
-            <li class="select-menu-tab">
-              <a href="#" data-tab-filter="branches" data-filter-placeholder="Filter branches/tags" class="js-select-menu-tab" role="tab">Branches</a>
-            </li>
-            <li class="select-menu-tab">
-              <a href="#" data-tab-filter="tags" data-filter-placeholder="Find a tag…" class="js-select-menu-tab" role="tab">Tags</a>
-            </li>
-          </ul>
-        </div>
-      </div>
-
-      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="branches" role="menu">
-
-        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">
-
-            <a class="select-menu-item js-navigation-item js-navigation-open selected"
-               href="/petrkeil/Blog/blob/master/2015_03_12_R_ms_template/manuscript_template.tex"
-               data-name="master"
-               data-skip-pjax="true"
-               rel="nofollow">
-              <svg class="octicon octicon-check select-menu-item-icon" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M12 5l-8 8-4-4 1.5-1.5L4 10l6.5-6.5L12 5z"/></svg>
-              <span class="select-menu-item-text css-truncate-target js-select-menu-filter-text">
-                master
-              </span>
-            </a>
-        </div>
-
-          <div class="select-menu-no-results">Nothing to show</div>
-      </div>
-
-      <div class="select-menu-list select-menu-tab-bucket js-select-menu-tab-bucket" data-tab-filter="tags">
-        <div data-filterable-for="context-commitish-filter-field" data-filterable-type="substring">
-
-        </div>
-
-        <div class="select-menu-no-results">Nothing to show</div>
-      </div>
-
-    </div>
-  </div>
-</div>
-
-    <div class="BtnGroup float-right">
-      <a href="/petrkeil/Blog/find/master"
-            class="js-pjax-capture-input btn btn-sm BtnGroup-item"
-            data-pjax
-            data-hotkey="t">
-        Find file
-      </a>
-      <clipboard-copy for="blob-path" class="btn btn-sm BtnGroup-item">
-        Copy path
-      </clipboard-copy>
-    </div>
-    <div id="blob-path" class="breadcrumb">
-      <span class="repo-root js-repo-root"><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog"><span>Blog</span></a></span></span><span class="separator">/</span><span class="js-path-segment"><a data-pjax="true" href="/petrkeil/Blog/tree/master/2015_03_12_R_ms_template"><span>2015_03_12_R_ms_template</span></a></span><span class="separator">/</span><strong class="final-path">manuscript_template.tex</strong>
-    </div>
-  </div>
-
-  <div class="commit-tease">
-      <span class="float-right">
-        <a class="commit-tease-sha" href="/petrkeil/Blog/commit/bdb85252abceb5ef19a438325c387cd941fa8e59" data-pjax>
-          bdb8525
-        </a>
-        <relative-time datetime="2017-03-27T15:15:23Z">Mar 27, 2017</relative-time>
-      </span>
-      <div>
-        <a rel="author" data-skip-pjax="true" data-hovercard-user-id="5421227" data-octo-click="hovercard-link-click" data-octo-dimensions="link_type:self" href="/petrkeil"><img class="avatar" src="https://avatars2.githubusercontent.com/u/5421227?s=40&amp;v=4" width="20" height="20" alt="@petrkeil" /></a>
-        <a class="user-mention" rel="author" data-hovercard-user-id="5421227" data-octo-click="hovercard-link-click" data-octo-dimensions="link_type:self" href="/petrkeil">petrkeil</a>
-          <a data-pjax="true" title="single-point ANOVA inference" class="message" href="/petrkeil/Blog/commit/bdb85252abceb5ef19a438325c387cd941fa8e59">single-point ANOVA inference</a>
-      </div>
-
-    <div class="commit-tease-contributors">
-
-<details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark float-left mr-2" id="blob_contributors_box">
-  <summary class="btn-link" aria-haspopup="dialog"  >
-
-    <span><strong>1</strong> contributor</span>
-  </summary>
-  <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast " aria-label="Users who have contributed to this file">
-    <div class="Box-header">
-      <button class="Box-btn-octicon btn-octicon float-right" type="button" aria-label="Close dialog" data-close-dialog>
-        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-      </button>
-      <h3 class="Box-title">Users who have contributed to this file</h3>
-    </div>
-
-        <ul class="list-style-none overflow-auto">
-            <li class="Box-row">
-              <a class="link-gray-dark no-underline" href="/petrkeil">
-                <img class="avatar mr-2" alt="" src="https://avatars2.githubusercontent.com/u/5421227?s=40&amp;v=4" width="20" height="20" />
-                petrkeil
-</a>            </li>
-        </ul>
-
-  </details-dialog>
-</details>
-
-    </div>
-  </div>
-
-  <div class="file">
-    <div class="file-header">
-  <div class="file-actions">
-
-    <div class="BtnGroup">
-      <a id="raw-url" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/raw/master/2015_03_12_R_ms_template/manuscript_template.tex">Raw</a>
-        <a class="btn btn-sm js-update-url-with-hash BtnGroup-item" data-hotkey="b" href="/petrkeil/Blog/blame/master/2015_03_12_R_ms_template/manuscript_template.tex">Blame</a>
-      <a rel="nofollow" class="btn btn-sm BtnGroup-item" href="/petrkeil/Blog/commits/master/2015_03_12_R_ms_template/manuscript_template.tex">History</a>
-    </div>
-
-          <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form js-update-url-with-hash" action="/petrkeil/Blog/edit/master/2015_03_12_R_ms_template/manuscript_template.tex" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="w+3hYqJjhuh93uZllWgA4JOlUpjHqPHPgW/C5pBTejUDA3OILy5ZqIwZtUEUGtGOPtTAfSXs33NAtsUeHSZSSA==" />
-            <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
-              aria-label="Fork this project and edit the file" data-hotkey="e" data-disable-with>
-              <svg class="octicon octicon-pencil" viewBox="0 0 14 16" version="1.1" width="14" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"/></svg>
-            </button>
-</form>
-        <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="inline-form" action="/petrkeil/Blog/delete/master/2015_03_12_R_ms_template/manuscript_template.tex" accept-charset="UTF-8" method="post"><input name="utf8" type="hidden" value="&#x2713;" /><input type="hidden" name="authenticity_token" value="efKWsrgtSPI/V5DDU5bGP7EMhrQUES31G2ywFe2D7TzEbIKhujyGp7OMXBU/qR2PeGN1Pdxd256v9Z45qk+w1Q==" />
-          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
-            aria-label="Fork this project and delete the file" data-disable-with>
-            <svg class="octicon octicon-trashcan" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"/></svg>
-          </button>
-</form>  </div>
-
-  <div class="file-info">
-      236 lines (198 sloc)
-      <span class="file-info-divider"></span>
-    8.71 KB
-  </div>
-</div>
-
-  <div itemprop="text" class="blob-wrapper data type-tex">
-      <table class="highlight tab-size js-file-line-container" data-tab-size="8">
-      <tr>
-        <td id="L1" class="blob-num js-line-number" data-line-number="1"></td>
-        <td id="LC1" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\documentclass</span>[]{article}</td>
-      </tr>
-      <tr>
-        <td id="L2" class="blob-num js-line-number" data-line-number="2"></td>
-        <td id="LC2" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{lmodern}</td>
-      </tr>
-      <tr>
-        <td id="L3" class="blob-num js-line-number" data-line-number="3"></td>
-        <td id="LC3" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{amssymb,amsmath}</td>
-      </tr>
-      <tr>
-        <td id="L4" class="blob-num js-line-number" data-line-number="4"></td>
-        <td id="LC4" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{ifxetex,ifluatex}</td>
-      </tr>
-      <tr>
-        <td id="L5" class="blob-num js-line-number" data-line-number="5"></td>
-        <td id="LC5" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{fixltx2e} <span class="pl-c"><span class="pl-c">%</span> provides \textsubscript</span></td>
-      </tr>
-      <tr>
-        <td id="L6" class="blob-num js-line-number" data-line-number="6"></td>
-        <td id="LC6" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifnum</span> 0<span class="pl-c1">\ifxetex</span> 1<span class="pl-k">\fi</span><span class="pl-c1">\ifluatex</span> 1<span class="pl-k">\fi</span>=0 <span class="pl-c"><span class="pl-c">%</span> if pdftex</span></td>
-      </tr>
-      <tr>
-        <td id="L7" class="blob-num js-line-number" data-line-number="7"></td>
-        <td id="LC7" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\usepackage</span>[T1]{fontenc}</td>
-      </tr>
-      <tr>
-        <td id="L8" class="blob-num js-line-number" data-line-number="8"></td>
-        <td id="LC8" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\usepackage</span>[utf8]{inputenc}</td>
-      </tr>
-      <tr>
-        <td id="L9" class="blob-num js-line-number" data-line-number="9"></td>
-        <td id="LC9" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\else</span> <span class="pl-c"><span class="pl-c">%</span> if luatex or xelatex</span></td>
-      </tr>
-      <tr>
-        <td id="L10" class="blob-num js-line-number" data-line-number="10"></td>
-        <td id="LC10" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\ifxetex</span></td>
-      </tr>
-      <tr>
-        <td id="L11" class="blob-num js-line-number" data-line-number="11"></td>
-        <td id="LC11" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\usepackage</span>{mathspec}</td>
-      </tr>
-      <tr>
-        <td id="L12" class="blob-num js-line-number" data-line-number="12"></td>
-        <td id="LC12" class="blob-code blob-code-inner js-file-line">  <span class="pl-k">\else</span></td>
-      </tr>
-      <tr>
-        <td id="L13" class="blob-num js-line-number" data-line-number="13"></td>
-        <td id="LC13" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\usepackage</span>{fontspec}</td>
-      </tr>
-      <tr>
-        <td id="L14" class="blob-num js-line-number" data-line-number="14"></td>
-        <td id="LC14" class="blob-code blob-code-inner js-file-line">  <span class="pl-k">\fi</span></td>
-      </tr>
-      <tr>
-        <td id="L15" class="blob-num js-line-number" data-line-number="15"></td>
-        <td id="LC15" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\defaultfontfeatures</span>{Ligatures=TeX,Scale=MatchLowercase}</td>
-      </tr>
-      <tr>
-        <td id="L16" class="blob-num js-line-number" data-line-number="16"></td>
-        <td id="LC16" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
-      </tr>
-      <tr>
-        <td id="L17" class="blob-num js-line-number" data-line-number="17"></td>
-        <td id="LC17" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> use upquote if available, for straight quotes in verbatim environments</span></td>
-      </tr>
-      <tr>
-        <td id="L18" class="blob-num js-line-number" data-line-number="18"></td>
-        <td id="LC18" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{upquote.sty}{<span class="pl-c1">\usepackage</span>{upquote}}{}</td>
-      </tr>
-      <tr>
-        <td id="L19" class="blob-num js-line-number" data-line-number="19"></td>
-        <td id="LC19" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> use microtype if available</span></td>
-      </tr>
-      <tr>
-        <td id="L20" class="blob-num js-line-number" data-line-number="20"></td>
-        <td id="LC20" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{microtype.sty}{<span class="pl-c"><span class="pl-c">%</span></span></td>
-      </tr>
-      <tr>
-        <td id="L21" class="blob-num js-line-number" data-line-number="21"></td>
-        <td id="LC21" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{microtype}</td>
-      </tr>
-      <tr>
-        <td id="L22" class="blob-num js-line-number" data-line-number="22"></td>
-        <td id="LC22" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\UseMicrotypeSet</span>[protrusion]{basicmath} <span class="pl-c"><span class="pl-c">%</span> disable protrusion for tt fonts</span></td>
-      </tr>
-      <tr>
-        <td id="L23" class="blob-num js-line-number" data-line-number="23"></td>
-        <td id="LC23" class="blob-code blob-code-inner js-file-line">}{}</td>
-      </tr>
-      <tr>
-        <td id="L24" class="blob-num js-line-number" data-line-number="24"></td>
-        <td id="LC24" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>[margin=1in]{geometry}</td>
-      </tr>
-      <tr>
-        <td id="L25" class="blob-num js-line-number" data-line-number="25"></td>
-        <td id="LC25" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{hyperref}</td>
-      </tr>
-      <tr>
-        <td id="L26" class="blob-num js-line-number" data-line-number="26"></td>
-        <td id="LC26" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypersetup</span>{unicode=true,</td>
-      </tr>
-      <tr>
-        <td id="L27" class="blob-num js-line-number" data-line-number="27"></td>
-        <td id="LC27" class="blob-code blob-code-inner js-file-line">            pdftitle={Template for writing scientific papers in R markdown},</td>
-      </tr>
-      <tr>
-        <td id="L28" class="blob-num js-line-number" data-line-number="28"></td>
-        <td id="LC28" class="blob-code blob-code-inner js-file-line">            pdfauthor={Petr Keil, pkeil@seznam.cz},</td>
-      </tr>
-      <tr>
-        <td id="L29" class="blob-num js-line-number" data-line-number="29"></td>
-        <td id="LC29" class="blob-code blob-code-inner js-file-line">            pdfborder={0 0 0},</td>
-      </tr>
-      <tr>
-        <td id="L30" class="blob-num js-line-number" data-line-number="30"></td>
-        <td id="LC30" class="blob-code blob-code-inner js-file-line">            breaklinks=true}</td>
-      </tr>
-      <tr>
-        <td id="L31" class="blob-num js-line-number" data-line-number="31"></td>
-        <td id="LC31" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\urlstyle</span>{same}  <span class="pl-c"><span class="pl-c">%</span> don&#39;t use monospace font for urls</span></td>
-      </tr>
-      <tr>
-        <td id="L32" class="blob-num js-line-number" data-line-number="32"></td>
-        <td id="LC32" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{longtable,booktabs}</td>
-      </tr>
-      <tr>
-        <td id="L33" class="blob-num js-line-number" data-line-number="33"></td>
-        <td id="LC33" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{graphicx,grffile}</td>
-      </tr>
-      <tr>
-        <td id="L34" class="blob-num js-line-number" data-line-number="34"></td>
-        <td id="LC34" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\makeatletter</span></td>
-      </tr>
-      <tr>
-        <td id="L35" class="blob-num js-line-number" data-line-number="35"></td>
-        <td id="LC35" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\maxwidth</span>{<span class="pl-k">\ifdim</span><span class="pl-c1">\Gin@nat@width</span>&gt;<span class="pl-c1">\linewidth\linewidth</span><span class="pl-k">\else</span><span class="pl-c1">\Gin@nat@width</span><span class="pl-k">\fi</span>}</td>
-      </tr>
-      <tr>
-        <td id="L36" class="blob-num js-line-number" data-line-number="36"></td>
-        <td id="LC36" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\maxheight</span>{<span class="pl-k">\ifdim</span><span class="pl-c1">\Gin@nat@height</span>&gt;<span class="pl-c1">\textheight\textheight</span><span class="pl-k">\else</span><span class="pl-c1">\Gin@nat@height</span><span class="pl-k">\fi</span>}</td>
-      </tr>
-      <tr>
-        <td id="L37" class="blob-num js-line-number" data-line-number="37"></td>
-        <td id="LC37" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\makeatother</span></td>
-      </tr>
-      <tr>
-        <td id="L38" class="blob-num js-line-number" data-line-number="38"></td>
-        <td id="LC38" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Scale images if necessary, so that they will not overflow the page</span></td>
-      </tr>
-      <tr>
-        <td id="L39" class="blob-num js-line-number" data-line-number="39"></td>
-        <td id="LC39" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> margins by default, and it is still possible to overwrite the defaults</span></td>
-      </tr>
-      <tr>
-        <td id="L40" class="blob-num js-line-number" data-line-number="40"></td>
-        <td id="LC40" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> using explicit options in \includegraphics[width, height, ...]{}</span></td>
-      </tr>
-      <tr>
-        <td id="L41" class="blob-num js-line-number" data-line-number="41"></td>
-        <td id="LC41" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setkeys</span>{Gin}{width=<span class="pl-c1">\maxwidth</span>,height=<span class="pl-c1">\maxheight</span>,keepaspectratio}</td>
-      </tr>
-      <tr>
-        <td id="L42" class="blob-num js-line-number" data-line-number="42"></td>
-        <td id="LC42" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\IfFileExists</span>{parskip.sty}{<span class="pl-c"><span class="pl-c">%</span></span></td>
-      </tr>
-      <tr>
-        <td id="L43" class="blob-num js-line-number" data-line-number="43"></td>
-        <td id="LC43" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{parskip}</td>
-      </tr>
-      <tr>
-        <td id="L44" class="blob-num js-line-number" data-line-number="44"></td>
-        <td id="LC44" class="blob-code blob-code-inner js-file-line">}{<span class="pl-c"><span class="pl-c">%</span> else</span></td>
-      </tr>
-      <tr>
-        <td id="L45" class="blob-num js-line-number" data-line-number="45"></td>
-        <td id="LC45" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\parindent</span>}{0pt}</td>
-      </tr>
-      <tr>
-        <td id="L46" class="blob-num js-line-number" data-line-number="46"></td>
-        <td id="LC46" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\parskip</span>}{6pt plus 2pt minus 1pt}</td>
-      </tr>
-      <tr>
-        <td id="L47" class="blob-num js-line-number" data-line-number="47"></td>
-        <td id="LC47" class="blob-code blob-code-inner js-file-line">}</td>
-      </tr>
-      <tr>
-        <td id="L48" class="blob-num js-line-number" data-line-number="48"></td>
-        <td id="LC48" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\emergencystretch</span>}{3em}  <span class="pl-c"><span class="pl-c">%</span> prevent overfull lines</span></td>
-      </tr>
-      <tr>
-        <td id="L49" class="blob-num js-line-number" data-line-number="49"></td>
-        <td id="LC49" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\providecommand</span>{<span class="pl-c1">\tightlist</span>}{<span class="pl-c"><span class="pl-c">%</span></span></td>
-      </tr>
-      <tr>
-        <td id="L50" class="blob-num js-line-number" data-line-number="50"></td>
-        <td id="LC50" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\setlength</span>{<span class="pl-c1">\itemsep</span>}{0pt}<span class="pl-c1">\setlength</span>{<span class="pl-c1">\parskip</span>}{0pt}}</td>
-      </tr>
-      <tr>
-        <td id="L51" class="blob-num js-line-number" data-line-number="51"></td>
-        <td id="LC51" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setcounter</span>{secnumdepth}{5}</td>
-      </tr>
-      <tr>
-        <td id="L52" class="blob-num js-line-number" data-line-number="52"></td>
-        <td id="LC52" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Redefines (sub)paragraphs to behave more like sections</span></td>
-      </tr>
-      <tr>
-        <td id="L53" class="blob-num js-line-number" data-line-number="53"></td>
-        <td id="LC53" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifx</span><span class="pl-c1">\paragraph\undefined</span><span class="pl-k">\else</span></td>
-      </tr>
-      <tr>
-        <td id="L54" class="blob-num js-line-number" data-line-number="54"></td>
-        <td id="LC54" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\oldparagraph\paragraph</span></td>
-      </tr>
-      <tr>
-        <td id="L55" class="blob-num js-line-number" data-line-number="55"></td>
-        <td id="LC55" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\renewcommand</span>{<span class="pl-c1">\paragraph</span>}[1]{<span class="pl-c1">\oldparagraph</span>{#1}<span class="pl-c1">\mbox</span>{}}</td>
-      </tr>
-      <tr>
-        <td id="L56" class="blob-num js-line-number" data-line-number="56"></td>
-        <td id="LC56" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
-      </tr>
-      <tr>
-        <td id="L57" class="blob-num js-line-number" data-line-number="57"></td>
-        <td id="LC57" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\ifx</span><span class="pl-c1">\subparagraph\undefined</span><span class="pl-k">\else</span></td>
-      </tr>
-      <tr>
-        <td id="L58" class="blob-num js-line-number" data-line-number="58"></td>
-        <td id="LC58" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\oldsubparagraph\subparagraph</span></td>
-      </tr>
-      <tr>
-        <td id="L59" class="blob-num js-line-number" data-line-number="59"></td>
-        <td id="LC59" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\renewcommand</span>{<span class="pl-c1">\subparagraph</span>}[1]{<span class="pl-c1">\oldsubparagraph</span>{#1}<span class="pl-c1">\mbox</span>{}}</td>
-      </tr>
-      <tr>
-        <td id="L60" class="blob-num js-line-number" data-line-number="60"></td>
-        <td id="LC60" class="blob-code blob-code-inner js-file-line"><span class="pl-k">\fi</span></td>
-      </tr>
-      <tr>
-        <td id="L61" class="blob-num js-line-number" data-line-number="61"></td>
-        <td id="LC61" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L62" class="blob-num js-line-number" data-line-number="62"></td>
-        <td id="LC62" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span>%% Use protect on footnotes to avoid problems with footnotes in titles</span></td>
-      </tr>
-      <tr>
-        <td id="L63" class="blob-num js-line-number" data-line-number="63"></td>
-        <td id="LC63" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\let\rmarkdownfootnote\footnote</span><span class="pl-c"><span class="pl-c">%</span></span></td>
-      </tr>
-      <tr>
-        <td id="L64" class="blob-num js-line-number" data-line-number="64"></td>
-        <td id="LC64" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\def\footnote</span>{<span class="pl-c1">\protect\rmarkdownfootnote</span>}</td>
-      </tr>
-      <tr>
-        <td id="L65" class="blob-num js-line-number" data-line-number="65"></td>
-        <td id="LC65" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L66" class="blob-num js-line-number" data-line-number="66"></td>
-        <td id="LC66" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span>%% Change title format to be more compact</span></td>
-      </tr>
-      <tr>
-        <td id="L67" class="blob-num js-line-number" data-line-number="67"></td>
-        <td id="LC67" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\usepackage</span>{titling}</td>
-      </tr>
-      <tr>
-        <td id="L68" class="blob-num js-line-number" data-line-number="68"></td>
-        <td id="LC68" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L69" class="blob-num js-line-number" data-line-number="69"></td>
-        <td id="LC69" class="blob-code blob-code-inner js-file-line"><span class="pl-c"><span class="pl-c">%</span> Create subtitle command for use in maketitle</span></td>
-      </tr>
-      <tr>
-        <td id="L70" class="blob-num js-line-number" data-line-number="70"></td>
-        <td id="LC70" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\newcommand</span>{<span class="pl-c1">\subtitle</span>}[1]{</td>
-      </tr>
-      <tr>
-        <td id="L71" class="blob-num js-line-number" data-line-number="71"></td>
-        <td id="LC71" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\posttitle</span>{</td>
-      </tr>
-      <tr>
-        <td id="L72" class="blob-num js-line-number" data-line-number="72"></td>
-        <td id="LC72" class="blob-code blob-code-inner js-file-line">    <span class="pl-c1">\begin</span>{center}<span class="pl-c1">\large</span>#1<span class="pl-c1">\end</span>{center}</td>
-      </tr>
-      <tr>
-        <td id="L73" class="blob-num js-line-number" data-line-number="73"></td>
-        <td id="LC73" class="blob-code blob-code-inner js-file-line">    }</td>
-      </tr>
-      <tr>
-        <td id="L74" class="blob-num js-line-number" data-line-number="74"></td>
-        <td id="LC74" class="blob-code blob-code-inner js-file-line">}</td>
-      </tr>
-      <tr>
-        <td id="L75" class="blob-num js-line-number" data-line-number="75"></td>
-        <td id="LC75" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L76" class="blob-num js-line-number" data-line-number="76"></td>
-        <td id="LC76" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\setlength</span>{<span class="pl-c1">\droptitle</span>}{-2em}</td>
-      </tr>
-      <tr>
-        <td id="L77" class="blob-num js-line-number" data-line-number="77"></td>
-        <td id="LC77" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\title</span>{Template for writing scientific papers in R markdown}</td>
-      </tr>
-      <tr>
-        <td id="L78" class="blob-num js-line-number" data-line-number="78"></td>
-        <td id="LC78" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\pretitle</span>{<span class="pl-c1">\vspace</span>{<span class="pl-c1">\droptitle</span>}<span class="pl-c1">\centering\huge</span>}</td>
-      </tr>
-      <tr>
-        <td id="L79" class="blob-num js-line-number" data-line-number="79"></td>
-        <td id="LC79" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\posttitle</span>{<span class="pl-c1">\par</span>}</td>
-      </tr>
-      <tr>
-        <td id="L80" class="blob-num js-line-number" data-line-number="80"></td>
-        <td id="LC80" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\author</span>{Petr Keil, <span class="pl-c1">\href</span>{mailto:pkeil@seznam.cz}{<span class="pl-c1">\nolinkurl</span>{pkeil@seznam.cz}}}</td>
-      </tr>
-      <tr>
-        <td id="L81" class="blob-num js-line-number" data-line-number="81"></td>
-        <td id="LC81" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\preauthor</span>{<span class="pl-c1">\centering\large\emph</span>}</td>
-      </tr>
-      <tr>
-        <td id="L82" class="blob-num js-line-number" data-line-number="82"></td>
-        <td id="LC82" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\postauthor</span>{<span class="pl-c1">\par</span>}</td>
-      </tr>
-      <tr>
-        <td id="L83" class="blob-num js-line-number" data-line-number="83"></td>
-        <td id="LC83" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\predate</span>{<span class="pl-c1">\centering\large\emph</span>}</td>
-      </tr>
-      <tr>
-        <td id="L84" class="blob-num js-line-number" data-line-number="84"></td>
-        <td id="LC84" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\postdate</span>{<span class="pl-c1">\par</span>}</td>
-      </tr>
-      <tr>
-        <td id="L85" class="blob-num js-line-number" data-line-number="85"></td>
-        <td id="LC85" class="blob-code blob-code-inner js-file-line">  <span class="pl-c1">\date</span>{11/1/2015}</td>
-      </tr>
-      <tr>
-        <td id="L86" class="blob-num js-line-number" data-line-number="86"></td>
-        <td id="LC86" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L87" class="blob-num js-line-number" data-line-number="87"></td>
-        <td id="LC87" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L88" class="blob-num js-line-number" data-line-number="88"></td>
-        <td id="LC88" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{document}</td>
-      </tr>
-      <tr>
-        <td id="L89" class="blob-num js-line-number" data-line-number="89"></td>
-        <td id="LC89" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\maketitle</span></td>
-      </tr>
-      <tr>
-        <td id="L90" class="blob-num js-line-number" data-line-number="90"></td>
-        <td id="LC90" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L91" class="blob-num js-line-number" data-line-number="91"></td>
-        <td id="LC91" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Abstract}<span class="pl-c1">\label</span>{abstract}</td>
-      </tr>
-      <tr>
-        <td id="L92" class="blob-num js-line-number" data-line-number="92"></td>
-        <td id="LC92" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L93" class="blob-num js-line-number" data-line-number="93"></td>
-        <td id="LC93" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\emph</span>{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel</td>
-      </tr>
-      <tr>
-        <td id="L94" class="blob-num js-line-number" data-line-number="94"></td>
-        <td id="LC94" class="blob-code blob-code-inner js-file-line">erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet</td>
-      </tr>
-      <tr>
-        <td id="L95" class="blob-num js-line-number" data-line-number="95"></td>
-        <td id="LC95" class="blob-code blob-code-inner js-file-line">argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
-      </tr>
-      <tr>
-        <td id="L96" class="blob-num js-line-number" data-line-number="96"></td>
-        <td id="LC96" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando</td>
-      </tr>
-      <tr>
-        <td id="L97" class="blob-num js-line-number" data-line-number="97"></td>
-        <td id="LC97" class="blob-code blob-code-inner js-file-line">mei.}</td>
-      </tr>
-      <tr>
-        <td id="L98" class="blob-num js-line-number" data-line-number="98"></td>
-        <td id="LC98" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L99" class="blob-num js-line-number" data-line-number="99"></td>
-        <td id="LC99" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Introduction}<span class="pl-c1">\label</span>{introduction}</td>
-      </tr>
-      <tr>
-        <td id="L100" class="blob-num js-line-number" data-line-number="100"></td>
-        <td id="LC100" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L101" class="blob-num js-line-number" data-line-number="101"></td>
-        <td id="LC101" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
-      </tr>
-      <tr>
-        <td id="L102" class="blob-num js-line-number" data-line-number="102"></td>
-        <td id="LC102" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
-      </tr>
-      <tr>
-        <td id="L103" class="blob-num js-line-number" data-line-number="103"></td>
-        <td id="LC103" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
-      </tr>
-      <tr>
-        <td id="L104" class="blob-num js-line-number" data-line-number="104"></td>
-        <td id="LC104" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
-      </tr>
-      <tr>
-        <td id="L105" class="blob-num js-line-number" data-line-number="105"></td>
-        <td id="LC105" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L106" class="blob-num js-line-number" data-line-number="106"></td>
-        <td id="LC106" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
-      </tr>
-      <tr>
-        <td id="L107" class="blob-num js-line-number" data-line-number="107"></td>
-        <td id="LC107" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
-      </tr>
-      <tr>
-        <td id="L108" class="blob-num js-line-number" data-line-number="108"></td>
-        <td id="LC108" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
-      </tr>
-      <tr>
-        <td id="L109" class="blob-num js-line-number" data-line-number="109"></td>
-        <td id="LC109" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
-      </tr>
-      <tr>
-        <td id="L110" class="blob-num js-line-number" data-line-number="110"></td>
-        <td id="LC110" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
-      </tr>
-      <tr>
-        <td id="L111" class="blob-num js-line-number" data-line-number="111"></td>
-        <td id="LC111" class="blob-code blob-code-inner js-file-line">conceptam.</td>
-      </tr>
-      <tr>
-        <td id="L112" class="blob-num js-line-number" data-line-number="112"></td>
-        <td id="LC112" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L113" class="blob-num js-line-number" data-line-number="113"></td>
-        <td id="LC113" class="blob-code blob-code-inner js-file-line">Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit</td>
-      </tr>
-      <tr>
-        <td id="L114" class="blob-num js-line-number" data-line-number="114"></td>
-        <td id="LC114" class="blob-code blob-code-inner js-file-line">quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos</td>
-      </tr>
-      <tr>
-        <td id="L115" class="blob-num js-line-number" data-line-number="115"></td>
-        <td id="LC115" class="blob-code blob-code-inner js-file-line">ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes</td>
-      </tr>
-      <tr>
-        <td id="L116" class="blob-num js-line-number" data-line-number="116"></td>
-        <td id="LC116" class="blob-code blob-code-inner js-file-line">percipitur at vis. Numquam similique in per, te quo saepe utroque</td>
-      </tr>
-      <tr>
-        <td id="L117" class="blob-num js-line-number" data-line-number="117"></td>
-        <td id="LC117" class="blob-code blob-code-inner js-file-line">pericula.</td>
-      </tr>
-      <tr>
-        <td id="L118" class="blob-num js-line-number" data-line-number="118"></td>
-        <td id="LC118" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L119" class="blob-num js-line-number" data-line-number="119"></td>
-        <td id="LC119" class="blob-code blob-code-inner js-file-line">Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo</td>
-      </tr>
-      <tr>
-        <td id="L120" class="blob-num js-line-number" data-line-number="120"></td>
-        <td id="LC120" class="blob-code blob-code-inner js-file-line">vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque</td>
-      </tr>
-      <tr>
-        <td id="L121" class="blob-num js-line-number" data-line-number="121"></td>
-        <td id="LC121" class="blob-code blob-code-inner js-file-line">gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne</td>
-      </tr>
-      <tr>
-        <td id="L122" class="blob-num js-line-number" data-line-number="122"></td>
-        <td id="LC122" class="blob-code blob-code-inner js-file-line">suas latine vix, eos oblique sanctus pertinax cu.</td>
-      </tr>
-      <tr>
-        <td id="L123" class="blob-num js-line-number" data-line-number="123"></td>
-        <td id="LC123" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L124" class="blob-num js-line-number" data-line-number="124"></td>
-        <td id="LC124" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Methods}<span class="pl-c1">\label</span>{methods}</td>
-      </tr>
-      <tr>
-        <td id="L125" class="blob-num js-line-number" data-line-number="125"></td>
-        <td id="LC125" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L126" class="blob-num js-line-number" data-line-number="126"></td>
-        <td id="LC126" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
-      </tr>
-      <tr>
-        <td id="L127" class="blob-num js-line-number" data-line-number="127"></td>
-        <td id="LC127" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
-      </tr>
-      <tr>
-        <td id="L128" class="blob-num js-line-number" data-line-number="128"></td>
-        <td id="LC128" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
-      </tr>
-      <tr>
-        <td id="L129" class="blob-num js-line-number" data-line-number="129"></td>
-        <td id="LC129" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
-      </tr>
-      <tr>
-        <td id="L130" class="blob-num js-line-number" data-line-number="130"></td>
-        <td id="LC130" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L131" class="blob-num js-line-number" data-line-number="131"></td>
-        <td id="LC131" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
-      </tr>
-      <tr>
-        <td id="L132" class="blob-num js-line-number" data-line-number="132"></td>
-        <td id="LC132" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
-      </tr>
-      <tr>
-        <td id="L133" class="blob-num js-line-number" data-line-number="133"></td>
-        <td id="LC133" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
-      </tr>
-      <tr>
-        <td id="L134" class="blob-num js-line-number" data-line-number="134"></td>
-        <td id="LC134" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
-      </tr>
-      <tr>
-        <td id="L135" class="blob-num js-line-number" data-line-number="135"></td>
-        <td id="LC135" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
-      </tr>
-      <tr>
-        <td id="L136" class="blob-num js-line-number" data-line-number="136"></td>
-        <td id="LC136" class="blob-code blob-code-inner js-file-line">conceptam.</td>
-      </tr>
-      <tr>
-        <td id="L137" class="blob-num js-line-number" data-line-number="137"></td>
-        <td id="LC137" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L138" class="blob-num js-line-number" data-line-number="138"></td>
-        <td id="LC138" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Equations}<span class="pl-c1">\label</span>{equations}</td>
-      </tr>
-      <tr>
-        <td id="L139" class="blob-num js-line-number" data-line-number="139"></td>
-        <td id="LC139" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L140" class="blob-num js-line-number" data-line-number="140"></td>
-        <td id="LC140" class="blob-code blob-code-inner js-file-line">The deterministic part of the model is defined by this <span class="pl-c1">\textbf</span>{in-line</td>
-      </tr>
-      <tr>
-        <td id="L141" class="blob-num js-line-number" data-line-number="141"></td>
-        <td id="LC141" class="blob-code blob-code-inner js-file-line">equation} as <span class="pl-cce">\(</span><span class="pl-c1">\mu</span>_i = <span class="pl-c1">\beta</span>_0 + <span class="pl-c1">\beta</span>_1x<span class="pl-cce">\)</span>, and the stochastic part by</td>
-      </tr>
-      <tr>
-        <td id="L142" class="blob-num js-line-number" data-line-number="142"></td>
-        <td id="LC142" class="blob-code blob-code-inner js-file-line">the <span class="pl-c1">\textbf</span>{centered equation}:</td>
-      </tr>
-      <tr>
-        <td id="L143" class="blob-num js-line-number" data-line-number="143"></td>
-        <td id="LC143" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L144" class="blob-num js-line-number" data-line-number="144"></td>
-        <td id="LC144" class="blob-code blob-code-inner js-file-line"><span class="pl-cce">\[</span> <span class="pl-c1">\frac</span>{1}{<span class="pl-c1">\sqrt</span>{2<span class="pl-c1">\pi</span>}<span class="pl-c1">\sigma</span>}e^{-(x-<span class="pl-c1">\mu</span>_i)^2/(2<span class="pl-c1">\sigma</span>^2)} <span class="pl-cce">\]</span></td>
-      </tr>
-      <tr>
-        <td id="L145" class="blob-num js-line-number" data-line-number="145"></td>
-        <td id="LC145" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L146" class="blob-num js-line-number" data-line-number="146"></td>
-        <td id="LC146" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Tables}<span class="pl-c1">\label</span>{tables}</td>
-      </tr>
-      <tr>
-        <td id="L147" class="blob-num js-line-number" data-line-number="147"></td>
-        <td id="LC147" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L148" class="blob-num js-line-number" data-line-number="148"></td>
-        <td id="LC148" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{longtable}[]{@{}lrrrr@{}}</td>
-      </tr>
-      <tr>
-        <td id="L149" class="blob-num js-line-number" data-line-number="149"></td>
-        <td id="LC149" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\caption</span>{This is a GLM summary table.}<span class="pl-c1">\tabularnewline</span></td>
-      </tr>
-      <tr>
-        <td id="L150" class="blob-num js-line-number" data-line-number="150"></td>
-        <td id="LC150" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\toprule</span></td>
-      </tr>
-      <tr>
-        <td id="L151" class="blob-num js-line-number" data-line-number="151"></td>
-        <td id="LC151" class="blob-code blob-code-inner js-file-line">&amp; Estimate &amp; Std. Error &amp; t value &amp;</td>
-      </tr>
-      <tr>
-        <td id="L152" class="blob-num js-line-number" data-line-number="152"></td>
-        <td id="LC152" class="blob-code blob-code-inner js-file-line">Pr(<span class="pl-c1">\textgreater</span>{}<span class="pl-c1">\textbar</span>{}t<span class="pl-c1">\textbar</span>{})<span class="pl-c1">\tabularnewline</span></td>
-      </tr>
-      <tr>
-        <td id="L153" class="blob-num js-line-number" data-line-number="153"></td>
-        <td id="LC153" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\midrule</span></td>
-      </tr>
-      <tr>
-        <td id="L154" class="blob-num js-line-number" data-line-number="154"></td>
-        <td id="LC154" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\endfirsthead</span></td>
-      </tr>
-      <tr>
-        <td id="L155" class="blob-num js-line-number" data-line-number="155"></td>
-        <td id="LC155" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\toprule</span></td>
-      </tr>
-      <tr>
-        <td id="L156" class="blob-num js-line-number" data-line-number="156"></td>
-        <td id="LC156" class="blob-code blob-code-inner js-file-line">&amp; Estimate &amp; Std. Error &amp; t value &amp;</td>
-      </tr>
-      <tr>
-        <td id="L157" class="blob-num js-line-number" data-line-number="157"></td>
-        <td id="LC157" class="blob-code blob-code-inner js-file-line">Pr(<span class="pl-c1">\textgreater</span>{}<span class="pl-c1">\textbar</span>{}t<span class="pl-c1">\textbar</span>{})<span class="pl-c1">\tabularnewline</span></td>
-      </tr>
-      <tr>
-        <td id="L158" class="blob-num js-line-number" data-line-number="158"></td>
-        <td id="LC158" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\midrule</span></td>
-      </tr>
-      <tr>
-        <td id="L159" class="blob-num js-line-number" data-line-number="159"></td>
-        <td id="LC159" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\endhead</span></td>
-      </tr>
-      <tr>
-        <td id="L160" class="blob-num js-line-number" data-line-number="160"></td>
-        <td id="LC160" class="blob-code blob-code-inner js-file-line">(Intercept) &amp; 0.05 &amp; 0.11 &amp; 0.46 &amp; 0.65<span class="pl-c1">\tabularnewline</span></td>
-      </tr>
-      <tr>
-        <td id="L161" class="blob-num js-line-number" data-line-number="161"></td>
-        <td id="LC161" class="blob-code blob-code-inner js-file-line">x &amp; 2.00 &amp; 0.12 &amp; 16.91 &amp; 0.00<span class="pl-c1">\tabularnewline</span></td>
-      </tr>
-      <tr>
-        <td id="L162" class="blob-num js-line-number" data-line-number="162"></td>
-        <td id="LC162" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\bottomrule</span></td>
-      </tr>
-      <tr>
-        <td id="L163" class="blob-num js-line-number" data-line-number="163"></td>
-        <td id="LC163" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{longtable}</td>
-      </tr>
-      <tr>
-        <td id="L164" class="blob-num js-line-number" data-line-number="164"></td>
-        <td id="LC164" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L165" class="blob-num js-line-number" data-line-number="165"></td>
-        <td id="LC165" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Plots}<span class="pl-c1">\label</span>{plots}</td>
-      </tr>
-      <tr>
-        <td id="L166" class="blob-num js-line-number" data-line-number="166"></td>
-        <td id="LC166" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L167" class="blob-num js-line-number" data-line-number="167"></td>
-        <td id="LC167" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\begin</span>{figure}[htbp]</td>
-      </tr>
-      <tr>
-        <td id="L168" class="blob-num js-line-number" data-line-number="168"></td>
-        <td id="LC168" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\centering</span></td>
-      </tr>
-      <tr>
-        <td id="L169" class="blob-num js-line-number" data-line-number="169"></td>
-        <td id="LC169" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\includegraphics</span>{manuscript_template_files/figure-latex/carDataPlot-1.pdf}</td>
-      </tr>
-      <tr>
-        <td id="L170" class="blob-num js-line-number" data-line-number="170"></td>
-        <td id="LC170" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\caption</span>{Relationship between x and y. The solid line is least-squares</td>
-      </tr>
-      <tr>
-        <td id="L171" class="blob-num js-line-number" data-line-number="171"></td>
-        <td id="LC171" class="blob-code blob-code-inner js-file-line">linear regression.}</td>
-      </tr>
-      <tr>
-        <td id="L172" class="blob-num js-line-number" data-line-number="172"></td>
-        <td id="LC172" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{figure}</td>
-      </tr>
-      <tr>
-        <td id="L173" class="blob-num js-line-number" data-line-number="173"></td>
-        <td id="LC173" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L174" class="blob-num js-line-number" data-line-number="174"></td>
-        <td id="LC174" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\subsection</span>{Citations}<span class="pl-c1">\label</span>{citations}</td>
-      </tr>
-      <tr>
-        <td id="L175" class="blob-num js-line-number" data-line-number="175"></td>
-        <td id="LC175" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L176" class="blob-num js-line-number" data-line-number="176"></td>
-        <td id="LC176" class="blob-code blob-code-inner js-file-line">The relationship was first described by Halpern <span class="pl-c1">\emph</span>{et al.} (2006).</td>
-      </tr>
-      <tr>
-        <td id="L177" class="blob-num js-line-number" data-line-number="177"></td>
-        <td id="LC177" class="blob-code blob-code-inner js-file-line">However, there are also opinions that the relationship is spurious (Keil</td>
-      </tr>
-      <tr>
-        <td id="L178" class="blob-num js-line-number" data-line-number="178"></td>
-        <td id="LC178" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\emph</span>{et al.} 2012). We used R for our calculations (R Core Team 2016),</td>
-      </tr>
-      <tr>
-        <td id="L179" class="blob-num js-line-number" data-line-number="179"></td>
-        <td id="LC179" class="blob-code blob-code-inner js-file-line">and we used package <span class="pl-c1">\texttt</span>{knitcitations} (Boettiger 2015) to make the</td>
-      </tr>
-      <tr>
-        <td id="L180" class="blob-num js-line-number" data-line-number="180"></td>
-        <td id="LC180" class="blob-code blob-code-inner js-file-line">bibliography.</td>
-      </tr>
-      <tr>
-        <td id="L181" class="blob-num js-line-number" data-line-number="181"></td>
-        <td id="LC181" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L182" class="blob-num js-line-number" data-line-number="182"></td>
-        <td id="LC182" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>{Results and discussion}<span class="pl-c1">\label</span>{results-and-discussion}</td>
-      </tr>
-      <tr>
-        <td id="L183" class="blob-num js-line-number" data-line-number="183"></td>
-        <td id="LC183" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L184" class="blob-num js-line-number" data-line-number="184"></td>
-        <td id="LC184" class="blob-code blob-code-inner js-file-line">Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel erat</td>
-      </tr>
-      <tr>
-        <td id="L185" class="blob-num js-line-number" data-line-number="185"></td>
-        <td id="LC185" class="blob-code blob-code-inner js-file-line">falli ut. Feugiat legendos adipisci vix at, usu at laoreet argumentum</td>
-      </tr>
-      <tr>
-        <td id="L186" class="blob-num js-line-number" data-line-number="186"></td>
-        <td id="LC186" class="blob-code blob-code-inner js-file-line">suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor</td>
-      </tr>
-      <tr>
-        <td id="L187" class="blob-num js-line-number" data-line-number="187"></td>
-        <td id="LC187" class="blob-code blob-code-inner js-file-line">liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.</td>
-      </tr>
-      <tr>
-        <td id="L188" class="blob-num js-line-number" data-line-number="188"></td>
-        <td id="LC188" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L189" class="blob-num js-line-number" data-line-number="189"></td>
-        <td id="LC189" class="blob-code blob-code-inner js-file-line">Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando</td>
-      </tr>
-      <tr>
-        <td id="L190" class="blob-num js-line-number" data-line-number="190"></td>
-        <td id="LC190" class="blob-code blob-code-inner js-file-line">debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis</td>
-      </tr>
-      <tr>
-        <td id="L191" class="blob-num js-line-number" data-line-number="191"></td>
-        <td id="LC191" class="blob-code blob-code-inner js-file-line">singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,</td>
-      </tr>
-      <tr>
-        <td id="L192" class="blob-num js-line-number" data-line-number="192"></td>
-        <td id="LC192" class="blob-code blob-code-inner js-file-line">id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id</td>
-      </tr>
-      <tr>
-        <td id="L193" class="blob-num js-line-number" data-line-number="193"></td>
-        <td id="LC193" class="blob-code blob-code-inner js-file-line">usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum</td>
-      </tr>
-      <tr>
-        <td id="L194" class="blob-num js-line-number" data-line-number="194"></td>
-        <td id="LC194" class="blob-code blob-code-inner js-file-line">conceptam.</td>
-      </tr>
-      <tr>
-        <td id="L195" class="blob-num js-line-number" data-line-number="195"></td>
-        <td id="LC195" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L196" class="blob-num js-line-number" data-line-number="196"></td>
-        <td id="LC196" class="blob-code blob-code-inner js-file-line">Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit</td>
-      </tr>
-      <tr>
-        <td id="L197" class="blob-num js-line-number" data-line-number="197"></td>
-        <td id="LC197" class="blob-code blob-code-inner js-file-line">quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos</td>
-      </tr>
-      <tr>
-        <td id="L198" class="blob-num js-line-number" data-line-number="198"></td>
-        <td id="LC198" class="blob-code blob-code-inner js-file-line">ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes</td>
-      </tr>
-      <tr>
-        <td id="L199" class="blob-num js-line-number" data-line-number="199"></td>
-        <td id="LC199" class="blob-code blob-code-inner js-file-line">percipitur at vis. Numquam similique in per, te quo saepe utroque</td>
-      </tr>
-      <tr>
-        <td id="L200" class="blob-num js-line-number" data-line-number="200"></td>
-        <td id="LC200" class="blob-code blob-code-inner js-file-line">pericula.</td>
-      </tr>
-      <tr>
-        <td id="L201" class="blob-num js-line-number" data-line-number="201"></td>
-        <td id="LC201" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L202" class="blob-num js-line-number" data-line-number="202"></td>
-        <td id="LC202" class="blob-code blob-code-inner js-file-line">Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo</td>
-      </tr>
-      <tr>
-        <td id="L203" class="blob-num js-line-number" data-line-number="203"></td>
-        <td id="LC203" class="blob-code blob-code-inner js-file-line">vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque</td>
-      </tr>
-      <tr>
-        <td id="L204" class="blob-num js-line-number" data-line-number="204"></td>
-        <td id="LC204" class="blob-code blob-code-inner js-file-line">gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne</td>
-      </tr>
-      <tr>
-        <td id="L205" class="blob-num js-line-number" data-line-number="205"></td>
-        <td id="LC205" class="blob-code blob-code-inner js-file-line">suas latine vix, eos oblique sanctus pertinax cu.</td>
-      </tr>
-      <tr>
-        <td id="L206" class="blob-num js-line-number" data-line-number="206"></td>
-        <td id="LC206" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L207" class="blob-num js-line-number" data-line-number="207"></td>
-        <td id="LC207" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\section</span>*{References}<span class="pl-c1">\label</span>{references}</td>
-      </tr>
-      <tr>
-        <td id="L208" class="blob-num js-line-number" data-line-number="208"></td>
-        <td id="LC208" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\addcontentsline</span>{toc}{section}{References}</td>
-      </tr>
-      <tr>
-        <td id="L209" class="blob-num js-line-number" data-line-number="209"></td>
-        <td id="LC209" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L210" class="blob-num js-line-number" data-line-number="210"></td>
-        <td id="LC210" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{refs}{}</td>
-      </tr>
-      <tr>
-        <td id="L211" class="blob-num js-line-number" data-line-number="211"></td>
-        <td id="LC211" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Boettiger_2015}{}</td>
-      </tr>
-      <tr>
-        <td id="L212" class="blob-num js-line-number" data-line-number="212"></td>
-        <td id="LC212" class="blob-code blob-code-inner js-file-line">Boettiger, C. (2015). <span class="pl-c1">\emph</span>{Knitcitations: Citations for &#39;knitr&#39;</td>
-      </tr>
-      <tr>
-        <td id="L213" class="blob-num js-line-number" data-line-number="213"></td>
-        <td id="LC213" class="blob-code blob-code-inner js-file-line">markdown files}. Retrieved from</td>
-      </tr>
-      <tr>
-        <td id="L214" class="blob-num js-line-number" data-line-number="214"></td>
-        <td id="LC214" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://CRAN.R-project.org/package=knitcitations}</td>
-      </tr>
-      <tr>
-        <td id="L215" class="blob-num js-line-number" data-line-number="215"></td>
-        <td id="LC215" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L216" class="blob-num js-line-number" data-line-number="216"></td>
-        <td id="LC216" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Halpern_2006}{}</td>
-      </tr>
-      <tr>
-        <td id="L217" class="blob-num js-line-number" data-line-number="217"></td>
-        <td id="LC217" class="blob-code blob-code-inner js-file-line">Halpern, B.S., Regan, H.M., Possingham, H.P. <span class="pl-cce">\&amp;</span> McCarthy, M.A. (2006).</td>
-      </tr>
-      <tr>
-        <td id="L218" class="blob-num js-line-number" data-line-number="218"></td>
-        <td id="LC218" class="blob-code blob-code-inner js-file-line">Accounting for uncertainty in marine reserve design. <span class="pl-c1">\emph</span>{Ecology</td>
-      </tr>
-      <tr>
-        <td id="L219" class="blob-num js-line-number" data-line-number="219"></td>
-        <td id="LC219" class="blob-code blob-code-inner js-file-line">Letters}, <span class="pl-c1">\textbf</span>{9}, 2--11. Retrieved from</td>
-      </tr>
-      <tr>
-        <td id="L220" class="blob-num js-line-number" data-line-number="220"></td>
-        <td id="LC220" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://doi.org/10.1111<span class="pl-cce">\%</span>2Fj.1461-0248.2005.00827.x}</td>
-      </tr>
-      <tr>
-        <td id="L221" class="blob-num js-line-number" data-line-number="221"></td>
-        <td id="LC221" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L222" class="blob-num js-line-number" data-line-number="222"></td>
-        <td id="LC222" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-Keil_2012}{}</td>
-      </tr>
-      <tr>
-        <td id="L223" class="blob-num js-line-number" data-line-number="223"></td>
-        <td id="LC223" class="blob-code blob-code-inner js-file-line">Keil, P., Belmaker, J., Wilson, A.M., Unitt, P. <span class="pl-cce">\&amp;</span> Jetz, W. (2012).</td>
-      </tr>
-      <tr>
-        <td id="L224" class="blob-num js-line-number" data-line-number="224"></td>
-        <td id="LC224" class="blob-code blob-code-inner js-file-line">Downscaling of species distribution models: A hierarchical approach (R.</td>
-      </tr>
-      <tr>
-        <td id="L225" class="blob-num js-line-number" data-line-number="225"></td>
-        <td id="LC225" class="blob-code blob-code-inner js-file-line">Freckleton, Ed.). <span class="pl-c1">\emph</span>{Methods in Ecology and Evolution}, <span class="pl-c1">\textbf</span>{4},</td>
-      </tr>
-      <tr>
-        <td id="L226" class="blob-num js-line-number" data-line-number="226"></td>
-        <td id="LC226" class="blob-code blob-code-inner js-file-line">82--94. Retrieved from</td>
-      </tr>
-      <tr>
-        <td id="L227" class="blob-num js-line-number" data-line-number="227"></td>
-        <td id="LC227" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\url</span>{https://doi.org/10.1111<span class="pl-cce">\%</span>2Fj.2041-210x.2012.00264.x}</td>
-      </tr>
-      <tr>
-        <td id="L228" class="blob-num js-line-number" data-line-number="228"></td>
-        <td id="LC228" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L229" class="blob-num js-line-number" data-line-number="229"></td>
-        <td id="LC229" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\hypertarget</span>{ref-R_Core_Team_2016}{}</td>
-      </tr>
-      <tr>
-        <td id="L230" class="blob-num js-line-number" data-line-number="230"></td>
-        <td id="LC230" class="blob-code blob-code-inner js-file-line">R Core Team. (2016). <span class="pl-c1">\emph</span>{R: A language and environment for statistical</td>
-      </tr>
-      <tr>
-        <td id="L231" class="blob-num js-line-number" data-line-number="231"></td>
-        <td id="LC231" class="blob-code blob-code-inner js-file-line">computing}. R Foundation for Statistical Computing, Vienna, Austria.</td>
-      </tr>
-      <tr>
-        <td id="L232" class="blob-num js-line-number" data-line-number="232"></td>
-        <td id="LC232" class="blob-code blob-code-inner js-file-line">Retrieved from <span class="pl-c1">\url</span>{https://www.R-project.org/}</td>
-      </tr>
-      <tr>
-        <td id="L233" class="blob-num js-line-number" data-line-number="233"></td>
-        <td id="LC233" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L234" class="blob-num js-line-number" data-line-number="234"></td>
-        <td id="LC234" class="blob-code blob-code-inner js-file-line">
-</td>
-      </tr>
-      <tr>
-        <td id="L235" class="blob-num js-line-number" data-line-number="235"></td>
-        <td id="LC235" class="blob-code blob-code-inner js-file-line"><span class="pl-c1">\end</span>{document}</td>
-      </tr>
-</table>
-
-  <details class="details-reset details-overlay BlobToolbar position-absolute js-file-line-actions dropdown d-none" aria-hidden="true">
-    <summary class="btn-octicon ml-0 px-2 p-0 bg-white border border-gray-dark rounded-1" aria-label="Inline file action toolbar">
-      <svg class="octicon octicon-kebab-horizontal" viewBox="0 0 13 16" version="1.1" width="13" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M1.5 9a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3zm5 0a1.5 1.5 0 1 0 0-3 1.5 1.5 0 0 0 0 3zM13 7.5a1.5 1.5 0 1 1-3 0 1.5 1.5 0 0 1 3 0z"/></svg>
-    </summary>
-    <details-menu>
-      <ul class="BlobToolbar-dropdown dropdown-menu dropdown-menu-se mt-2">
-        <li><clipboard-copy role="menuitem" class="dropdown-item" id="js-copy-lines" style="cursor:pointer;" data-original-text="Copy lines">Copy lines</clipboard-copy></li>
-        <li><clipboard-copy role="menuitem" class="dropdown-item" id="js-copy-permalink" style="cursor:pointer;" data-original-text="Copy permalink">Copy permalink</clipboard-copy></li>
-        <li><a class="dropdown-item js-update-url-with-hash" id="js-view-git-blame" role="menuitem" href="/petrkeil/Blog/blame/a32e8fd240fe0237ea9f64854aca0f7dfec0b7b6/2015_03_12_R_ms_template/manuscript_template.tex">View git blame</a></li>
-          <li><a class="dropdown-item" id="js-new-issue" role="menuitem" href="/petrkeil/Blog/issues/new">Open new issue</a></li>
-      </ul>
-    </details-menu>
-  </details>
-
-  </div>
-
-  </div>
-
-  <details class="details-reset details-overlay details-overlay-dark">
-    <summary data-hotkey="l" aria-label="Jump to line"></summary>
-    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast linejump" aria-label="Jump to line">
-      <!-- '"` --><!-- </textarea></xmp> --></option></form><form class="js-jump-to-line-form Box-body d-flex" action="" accept-charset="UTF-8" method="get"><input name="utf8" type="hidden" value="&#x2713;" />
-        <input class="form-control flex-auto mr-3 linejump-input js-jump-to-line-field" type="text" placeholder="Jump to line&hellip;" aria-label="Jump to line" autofocus>
-        <button type="submit" class="btn" data-close-dialog>Go</button>
-</form>    </details-dialog>
-  </details>
-
-  </div>
-  <div class="modal-backdrop js-touch-events"></div>
-</div>
-
-    </div>
-  </div>
-
-  </div>
-
-<div class="footer container-lg px-3" role="contentinfo">
-  <div class="position-relative d-flex flex-justify-between pt-6 pb-2 mt-6 f6 text-gray border-top border-gray-light ">
-    <ul class="list-style-none d-flex flex-wrap ">
-      <li class="mr-3">&copy; 2018 <span title="0.30940s from unicorn-6bfd5c759c-8hwtx">GitHub</span>, Inc.</li>
-        <li class="mr-3"><a data-ga-click="Footer, go to terms, text:terms" href="https://github.com/site/terms">Terms</a></li>
-        <li class="mr-3"><a data-ga-click="Footer, go to privacy, text:privacy" href="https://github.com/site/privacy">Privacy</a></li>
-        <li class="mr-3"><a href="https://help.github.com/articles/github-security/" data-ga-click="Footer, go to security, text:security">Security</a></li>
-        <li class="mr-3"><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
-        <li><a data-ga-click="Footer, go to help, text:help" href="https://help.github.com">Help</a></li>
-    </ul>
-
-    <a aria-label="Homepage" title="GitHub" class="footer-octicon mr-lg-4" href="https://github.com">
-      <svg height="24" class="octicon octicon-mark-github" viewBox="0 0 16 16" version="1.1" width="24" aria-hidden="true"><path fill-rule="evenodd" d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"/></svg>
-</a>
-   <ul class="list-style-none d-flex flex-wrap ">
-        <li class="mr-3"><a data-ga-click="Footer, go to contact, text:contact" href="https://github.com/contact">Contact GitHub</a></li>
-        <li class="mr-3"><a href="https://github.com/pricing" data-ga-click="Footer, go to Pricing, text:Pricing">Pricing</a></li>
-      <li class="mr-3"><a href="https://developer.github.com" data-ga-click="Footer, go to api, text:api">API</a></li>
-      <li class="mr-3"><a href="https://training.github.com" data-ga-click="Footer, go to training, text:training">Training</a></li>
-        <li class="mr-3"><a href="https://blog.github.com" data-ga-click="Footer, go to blog, text:blog">Blog</a></li>
-        <li><a data-ga-click="Footer, go to about, text:about" href="https://github.com/about">About</a></li>
-
-    </ul>
-  </div>
-  <div class="d-flex flex-justify-center pb-6">
-    <span class="f6 text-gray-light"></span>
-  </div>
-</div>
-
-  <div id="ajax-error-message" class="ajax-error-message flash flash-error">
-    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
-    <button type="button" class="flash-close js-ajax-error-dismiss" aria-label="Dismiss error">
-      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-    </button>
-    You can’t perform that action at this time.
-  </div>
-
-    <script crossorigin="anonymous" integrity="sha512-RJ1ufbxsSbKjRCyYvinsPNKvTBvcvvKUvEOJ8g+GjtWI5SuRr+QPBlZcvRDws4H9YwAgdQFcGxfL8UbwEfdI7A==" type="application/javascript" src="https://assets-cdn.github.com/assets/compat-daf14de28fadf1e2bc40d100cb773e2b.js"></script>
-    <script crossorigin="anonymous" integrity="sha512-IC5Ai6c7cUBfMx54JUAsIjA7VroipzkizlZ8F6/0efsGGyZStweZV7bX9bxSFL07nUNLfwrKSEysVIijX+CeUw==" type="application/javascript" src="https://assets-cdn.github.com/assets/frameworks-5874e38105ec062c740350eeb96bdd8a.js"></script>
-
-    <script crossorigin="anonymous" async="async" integrity="sha512-/E7YUPwg5s5FmwhSiwtXwNsTUCpjjdcrKoK7UFMQCguTSC71dACKl+XDhBftzkBsRra4w+a24G4oU535TieAIA==" type="application/javascript" src="https://assets-cdn.github.com/assets/github-1835546276a57f4d0c3203810d2ec7d6.js"></script>
-
-  <div class="js-stale-session-flash stale-session-flash flash flash-warn flash-banner d-none">
-    <svg class="octicon octicon-alert" viewBox="0 0 16 16" version="1.1" width="16" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M8.893 1.5c-.183-.31-.52-.5-.887-.5s-.703.19-.886.5L.138 13.499a.98.98 0 0 0 0 1.001c.193.31.53.501.886.501h13.964c.367 0 .704-.19.877-.5a1.03 1.03 0 0 0 .01-1.002L8.893 1.5zm.133 11.497H6.987v-2.003h2.039v2.003zm0-3.004H6.987V5.987h2.039v4.006z"/></svg>
-    <span class="signed-in-tab-flash">You signed in with another tab or window. <a href="">Reload</a> to refresh your session.</span>
-    <span class="signed-out-tab-flash">You signed out in another tab or window. <a href="">Reload</a> to refresh your session.</span>
-  </div>
-  <div class="facebox" id="facebox" style="display:none;">
-  <div class="facebox-popup">
-    <div class="facebox-content" role="dialog" aria-labelledby="facebox-header" aria-describedby="facebox-description">
-    </div>
-    <button type="button" class="facebox-close js-facebox-close" aria-label="Close modal">
-      <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-    </button>
-  </div>
-</div>
-
-  <template id="site-details-dialog">
-  <details class="details-reset details-overlay details-overlay-dark lh-default text-gray-dark" open>
-    <summary aria-haspopup="dialog" aria-label="Close dialog"></summary>
-    <details-dialog class="Box Box--overlay d-flex flex-column anim-fade-in fast">
-      <button class="Box-btn-octicon m-0 btn-octicon position-absolute right-0 top-0" type="button" aria-label="Close dialog" data-close-dialog>
-        <svg class="octicon octicon-x" viewBox="0 0 12 16" version="1.1" width="12" height="16" aria-hidden="true"><path fill-rule="evenodd" d="M7.48 8l3.75 3.75-1.48 1.48L6 9.48l-3.75 3.75-1.48-1.48L4.52 8 .77 4.25l1.48-1.48L6 6.52l3.75-3.75 1.48 1.48L7.48 8z"/></svg>
-      </button>
-      <div class="octocat-spinner my-6 js-details-dialog-spinner"></div>
-    </details-dialog>
-  </details>
-</template>
-
-  <div class="Popover js-hovercard-content position-absolute" style="display: none; outline: none;" tabindex="0">
-  <div class="Popover-message Popover-message--bottom-left Popover-message--large Box box-shadow-large" style="width:360px;">
-  </div>
-</div>
-
-<div id="hovercard-aria-description" class="sr-only">
-  Press h to open a hovercard with more details.
-</div>
-
-  </body>
-</html>
+\end{document}

### 2018-09-21 manuscript/manuscript_template.Rmd
Update pandoc output from Rmarkdown

@@
 author:
-- James Grecian One^[University of Somewhere]
-- Ian Jonsen Two^[University of Nowhere]
+  - W. J. Grecian^1^, I. D. Jonsen^2^
+  - ^1^Sea Mammal Research Unit, Scottish Oceans Institute, University of St Andrews, St Andrews, UK
+  - ^2^Dept. of Biological Sciences, Macquarie University, Sydney, Australia
 date: "`r format(Sys.time(), '%d %B %Y')`"
-tags: [nothing, nothingness]
 output:

### 2018-09-21 manuscript/manuscript_template.tex
Update pandoc output from Rmarkdown

@@
             pdftitle={A template for writing a manuscript in Rmarkdown},
-            pdfauthor={James Grecian One; Ian Jonsen Two},
+            pdfauthor={W.
+J.
+Grecian1, I.
+D.
+Jonsen2; 1Sea Mammal Research Unit, Scottish Oceans Institute, University of St Andrews, St Andrews, UK; 2Dept.
+of Biological Sciences, Macquarie University, Sydney, Australia},
             pdfborder={0 0 0},
@@
   \posttitle{\par}
-    \author{James Grecian One\footnote{University of Somewhere} \\ Ian Jonsen Two\footnote{University of Nowhere}}
+    \author{W. J. Grecian\textsuperscript{1}, I. D. Jonsen\textsuperscript{2} \\ \textsuperscript{1}Sea Mammal Research Unit, Scottish Oceans Institute,
+University of St Andrews, St Andrews, UK \\ \textsuperscript{2}Dept. of Biological Sciences, Macquarie University,
+Sydney, Australia}
     \preauthor{\centering\large\emph}
@@
 \endhead
-(Intercept) & 0.05 & 0.1 & 0.48 & 0.63\tabularnewline
-x & 1.96 & 0.1 & 19.68 & 0.00\tabularnewline
+(Intercept) & 0.02 & 0.09 & 0.27 & 0.79\tabularnewline
+x & 1.94 & 0.09 & 22.13 & 0.00\tabularnewline
 \bottomrule

### 2018-10-03 manuscript/manuscript_template.Rmd
Update manuscript to include outline abstract

--- 2018-09-21 manuscript/manuscript_template.Rmd
@@
 ---
-title:  'A template for writing a manuscript in Rmarkdown'
-author:
-- James Grecian One^[University of Somewhere]
-- Ian Jonsen Two^[University of Nowhere]
+title:  'Incorporating dive behaviour into models of marine animal movement'
+
+author: |
+  | W. J. Grecian$^1$ ^[Corresponding author: james.grecian@gmail.com] , I. D. Jonsen$^2$
+  | $^1$Sea Mammal Research Unit, Scottish Oceans Institute, University of St Andrews
+  | $^2$Dept. of Biological Sciences, Macquarie University, Sydney, Australia
+
+abstract: |
+ The Abstract must not exceed 350 words and should list the main results and conclusions, using simple, factual, numbered statements.  
+ 1.
+Models of animal movement often only consider horizontal movement over 2 dimensions.
+Incorporating vertical movement in these models offers the potential to improve our understanding of the drivers of animal movement.
+ 2.
+Here we describe a state-space model that incorporates a random walk on both horizontal and vertical movements, and estimates the covariance between them.
+The model is flexible to allow both parameters to be conditioned on covariates, offering insights into the drivers of animal movement.
+ 3. outline the main results  
+ 4. identify the conclusions and the wider implications.
+
+keywords: | 
+ A list in alphabetical order not exceeding eight words or short phrases. The most important key-words should appear in the title and the abstract as well as the key-word list.
+
 date: "`r format(Sys.time(), '%d %B %Y')`"
-tags: [nothing, nothingness]
 output:
@@
 csl: mee.csl
+#bibliography: references.bib
 header-includes:
@@
 
-# Abstract
-
-*Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem.
-Mel erat falli ut.
-Feugiat legendos adipisci vix at, usu at laoreet argumentum suscipiantur.
-An eos adhuc aliquip scriptorem, te adhuc dolor liberavisse sea.
-Ponderum vivendum te nec, id agam brute disputando mei.*
-
-# Introduction
+# INTRODUCTION
 
@@
 
-Putant numquam tacimates at eum.
-Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu.
-Nam mucius facilis singulis id, duo ei autem imperdiet instructior.
-Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum.
-Posse dicunt id usu.
-Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.
-
-Has audire salutandi no, ut eam dicat libris dicunt.
-Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea.
-Illum insolens eos ne, eu enim graece rationibus mea.
-At postea utamur mel, eius nonumes percipitur at vis.
-Numquam similique in per, te quo saepe utroque pericula.
-
-Ea nonumy volumus usu, no mel inermis dissentias.
-Dico partiendo vituperatoribus eum et.
-Mea accusam convenire te, usu populo qualisque gloriatur ut.
-Eu eum oratio altera option, ad mea ignota scriptorem.
-Ne suas latine vix, eos oblique sanctus pertinax cu.
-
-# Methods
+# MATERIALS AND METHODS
 
@@
 Ponderum vivendum te nec, id agam brute disputando mei.
-
-Putant numquam tacimates at eum.
-Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu.
-Nam mucius facilis singulis id, duo ei autem imperdiet instructior.
-Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum.
-Posse dicunt id usu.
-Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.
 
@@
 
-The relationship was first described by
-`r citet("10.1111/j.1461-0248.2005.00827.x")`. However, there are also opinions
-that the relationship is spurious `r citep("10.1111/j.2041-210x.2012.00264.x")`.
-We used R for our calculations `r citep(citation())`, and we used package `knitcitations` `r citep(citation("knitcitations"))` to make the bibliography.
+The relationship was first described by @Halpern_2006. However, there are also opinions
+that the relationship is spurious [@Keil_2012].
+We used R for our calculations [@R_Core_Team_2016], and we used package `knitcitations` [@Boettiger_2017] to make the bibliography.
 
-# Results and discussion
+# RESULTS
 
@@
 
-Putant numquam tacimates at eum.
-Aliquip torquatos ex vis, mei et quando debitis appareat, impetus accumsan corrumpit in usu.
-Nam mucius facilis singulis id, duo ei autem imperdiet instructior.
-Cu ceteros alienum mel, id vix putant impedit, ex idque eruditi forensibus eum.
-Posse dicunt id usu.
-Ei iracundia constituto sed, duo ne exerci ignota, an eum unum conceptam.
+# DISCUSSION
 
-Has audire salutandi no, ut eam dicat libris dicunt.
-Pri hendrerit quaerendum adversarium ea, dicat atqui munere et sea.
-Illum insolens eos ne, eu enim graece rationibus mea.
-At postea utamur mel, eius nonumes percipitur at vis.
-Numquam similique in per, te quo saepe utroque pericula.
+# CONCLUSION
 
-Ea nonumy volumus usu, no mel inermis dissentias.
-Dico partiendo vituperatoribus eum et.
-Mea accusam convenire te, usu populo qualisque gloriatur ut.
-Eu eum oratio altera option, ad mea ignota scriptorem.
-Ne suas latine vix, eos oblique sanctus pertinax cu.
+# ACKNOWLEDGEMENTS
 
-# References
+This project was made possible through a travel award from the Canada-UK Foundation.
+
+# AUTHORS' CONTRIBUTION
+
+# DATA ACCESSIBILITY
+
+# REFERENCES
 
 ```{r, warning=FALSE, message=FALSE, echo=FALSE} 
-  write.bibtex(file="references.bib")
+  #write.bibtex(file="references.bib")
 ```

### 2018-10-03 manuscript/manuscript_template.tex
Update manuscript to include outline abstract

--- 2018-09-21 manuscript/manuscript_template.tex
@@
 \hypersetup{unicode=true,
-            pdftitle={A template for writing a manuscript in Rmarkdown},
-            pdfauthor={James Grecian One; Ian Jonsen Two},
+            pdftitle={Incorporating dive behaviour into models of marine animal movement},
+            pdfkeywords={A list in alphabetical order not exceeding eight words or short phrases.
+The most important key-words should appear in the title and the abstract
+as well as the key-word list.},
             pdfborder={0 0 0},
@@
 
-  \title{A template for writing a manuscript in Rmarkdown}
+  \title{Incorporating dive behaviour into models of marine animal movement}
     \pretitle{\vspace{\droptitle}\centering\huge}
   \posttitle{\par}
-    \author{James Grecian One\footnote{University of Somewhere} \\ Ian Jonsen Two\footnote{University of Nowhere}}
+    \author{W. J. Grecian\(^1\) \footnote{Corresponding author:
+  \href{mailto:james.grecian@gmail.com}{\nolinkurl{james.grecian@gmail.com}}}
+, I. D. Jonsen\(^2\)\\
+\(^1\)Sea Mammal Research Unit, Scottish Oceans Institute, University of
+St Andrews\\
+\(^2\)Dept. of Biological Sciences, Macquarie University, Sydney,
+Australia}
     \preauthor{\centering\large\emph}
@@
   \postdate{\par}
-    \date{21 September 2018}
+    \date{03 October 2018}
 
@@
 \maketitle
+\begin{abstract}
+The Abstract must not exceed 350 words and should list the main results
+and conclusions, using simple, factual, numbered statements.\\
+1. Models of animal movement often only consider horizontal movement
+over 2 dimensions. Incorporating vertical movement in these models
+offers the potential to improve our understanding of the drivers of
+animal movement.\\
+2. Here we describe a state-space model that incorporates a random walk
+on both horizontal and vertical movements, and estimates the covariance
+between them. The model is flexible to allow both parameters to be
+conditioned on covariates, offering insights into the drivers of animal
+movement.\\
+3. outline the main results\\
+4. identify the conclusions and the wider implications.
+\end{abstract}
 
-\section{Abstract}\label{abstract}
-
-\emph{Lorem ipsum dolor sit amet, est ad doctus eligendi scriptorem. Mel
-erat falli ut. Feugiat legendos adipisci vix at, usu at laoreet
-argumentum suscipiantur. An eos adhuc aliquip scriptorem, te adhuc dolor
-liberavisse sea. Ponderum vivendum te nec, id agam brute disputando
-mei.}
-
-\section{Introduction}\label{introduction}
+\section{INTRODUCTION}\label{introduction}
 
@@
 
-Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
-debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
-singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
-id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
-usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
-conceptam.
-
-Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
-quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
-ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
-percipitur at vis. Numquam similique in per, te quo saepe utroque
-pericula.
-
-Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
-vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
-gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
-suas latine vix, eos oblique sanctus pertinax cu.
-
-\section{Methods}\label{methods}
+\section{MATERIALS AND METHODS}\label{materials-and-methods}
 
@@
 liberavisse sea. Ponderum vivendum te nec, id agam brute disputando mei.
-
-Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
-debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
-singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
-id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
-usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
-conceptam.
 
@@
 \endhead
-(Intercept) & 0.05 & 0.1 & 0.48 & 0.63\tabularnewline
-x & 1.96 & 0.1 & 19.68 & 0.00\tabularnewline
+(Intercept) & 0.01 & 0.10 & 0.07 & 0.94\tabularnewline
+x & 1.83 & 0.11 & 16.95 & 0.00\tabularnewline
 \bottomrule
@@
 are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
-We used R for our calculations {[}@R\_Core\_Team\_2017{]}, and we used
+We used R for our calculations {[}@R\_Core\_Team\_2016{]}, and we used
 package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
@@
 
-\section{Results and discussion}\label{results-and-discussion}
+\section{RESULTS}\label{results}
 
@@
 
-Putant numquam tacimates at eum. Aliquip torquatos ex vis, mei et quando
-debitis appareat, impetus accumsan corrumpit in usu. Nam mucius facilis
-singulis id, duo ei autem imperdiet instructior. Cu ceteros alienum mel,
-id vix putant impedit, ex idque eruditi forensibus eum. Posse dicunt id
-usu. Ei iracundia constituto sed, duo ne exerci ignota, an eum unum
-conceptam.
+\section{DISCUSSION}\label{discussion}
 
-Has audire salutandi no, ut eam dicat libris dicunt. Pri hendrerit
-quaerendum adversarium ea, dicat atqui munere et sea. Illum insolens eos
-ne, eu enim graece rationibus mea. At postea utamur mel, eius nonumes
-percipitur at vis. Numquam similique in per, te quo saepe utroque
-pericula.
+\section{CONCLUSION}\label{conclusion}
 
-Ea nonumy volumus usu, no mel inermis dissentias. Dico partiendo
-vituperatoribus eum et. Mea accusam convenire te, usu populo qualisque
-gloriatur ut. Eu eum oratio altera option, ad mea ignota scriptorem. Ne
-suas latine vix, eos oblique sanctus pertinax cu.
+\section{ACKNOWLEDGEMENTS}\label{acknowledgements}
 
-\section{References}\label{references}
+This project was made possible through a travel award from the Canada-UK
+Foundation.
+
+\section{AUTHORS' CONTRIBUTION}\label{authors-contribution}
+
+\section{DATA ACCESSIBILITY}\label{data-accessibility}
+
+\section{REFERENCES}\label{references}
 

### 2018-10-03 R/script.r

@@ -1,6 +1,9 @@
+# load libraries
 require(tidyverse)
+require(sf)
 source("R/mpmm.r")
 
+# import data
 d <- read.csv("dat/hp2_ctrw.csv", stringsAsFactors = FALSE) %>%
   tbl_df() %>%
   select(-X) %>%
@@ -12,4 +15,27 @@ d <- read.csv("dat/hp2_ctrw.csv", stringsAsFactors = FALSE) %>%
   mutate(date = lubridate::ymd_hms(date, tz = "UTC")) %>%
   filter(id != "hp2-9320-04", id != "hp2-9349-04")
 
+# run lambda mpmm model
 fit <- mpmm(~ 1 + (1 | id), d, verbose = TRUE)
+
+# check convergence
+fit$opt
+
+# plot using sf
+fit_sf <- st_as_sf(fit$data, coords = c("lon", "lat")) %>%
+  st_set_crs("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+
+# plot output
+ggplot() + 
+  geom_sf(aes(colour = fit$fitted$gamma), size = 0.5, data = fit_sf) +
+  scale_colour_viridis_c() +
+  facet_wrap(~id)
+
+ggplot() + 
+  geom_sf(aes(colour = fit$fitted$lambda), size = 0.5, data = fit_sf) +
+  scale_colour_viridis_c() +
+  facet_wrap(~id)
+
+ggplot() + 
+  geom_path(aes(x = lambda, y = gamma, group = id), data = fit$fitted) +
+  facet_wrap(~id)

### 2018-10-04 manuscript/manuscript_template.Rmd
Use citr package for citations

@@
 csl: mee.csl
-#bibliography: references.bib
+bibliography: references.bib
 header-includes:
@@
    - \linenumbers
+   - \usepackage{setspace}
+   - \doublespacing
+fontsize: 12pt
 ---
@@
 ```{r, echo=FALSE}
-  # devtools::install_github("cboettig/knitcitations@v1")
-  library(knitcitations); cleanbib()
-  cite_options(citation_format = "pandoc", check.entries=TRUE)
-  library(bibtex)
+  require(citr)
 ```
@@
 that the relationship is spurious [@Keil_2012].
-We used R for our calculations [@R_Core_Team_2016], and we used package `knitcitations` [@Boettiger_2017] to make the bibliography.
+We used R for our calculations [@R_Core_Team_2016], and we used package.
 
@@
 # REFERENCES
-
-```{r, warning=FALSE, message=FALSE, echo=FALSE} 
-  #write.bibtex(file="references.bib")
-```

### 2018-10-04 manuscript/manuscript_template.Rmd
Add keywords to abstract

@@
   | $^2$Dept. of Biological Sciences, Macquarie University, Sydney, Australia
+
+date: "`r format(Sys.time(), '%d %B %Y')`"
 
@@
  4. identify the conclusions and the wider implications.  
+ **keywords:** A list in alphabetical order; not exceeding eight words or short phrases; The most important key-words should appear in the title; and the abstract; as well as the key-word list.
 
-keywords: | 
- A list in alphabetical order not exceeding eight words or short phrases. The most important key-words should appear in the title and the abstract as well as the key-word list.
-
-date: "`r format(Sys.time(), '%d %B %Y')`"
 output:

### 2018-10-04 manuscript/manuscript_template.tex
Add keywords to abstract

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
             pdftitle={Incorporating dive behaviour into models of marine animal movement},
-            pdfkeywords={A list in alphabetical order not exceeding eight words or short phrases.
-The most important key-words should appear in the title and the abstract
-as well as the key-word list.},
             pdfborder={0 0 0},
@@
   \posttitle{\par}
-    \author{W. J. Grecian\(^1\) \footnote{Corresponding author:
+    \author{W. J. Grecian\(^1\)\footnote{Corresponding author:
   \href{mailto:james.grecian@gmail.com}{\nolinkurl{james.grecian@gmail.com}}}
@@
   \postdate{\par}
-    \date{03 October 2018}
+    \date{04 October 2018}
 
@@
 \linenumbers
+\usepackage{setspace}
+\doublespacing
 
@@
 3. outline the main results\\
-4. identify the conclusions and the wider implications.
+4. identify the conclusions and the wider implications.\\
+\textbf{keywords:} A list in alphabetical order; not exceeding eight
+words or short phrases; The most important key-words should appear in
+the title; and the abstract; as well as the key-word list.
 \end{abstract}
+
+\begin{verbatim}
+## Loading required package: citr
+\end{verbatim}
 
@@
 \endhead
-(Intercept) & 0.01 & 0.10 & 0.07 & 0.94\tabularnewline
-x & 1.83 & 0.11 & 16.95 & 0.00\tabularnewline
+(Intercept) & -0.02 & 0.11 & -0.15 & 0.88\tabularnewline
+x & 2.00 & 0.12 & 16.76 & 0.00\tabularnewline
 \bottomrule
@@
 
-The relationship was first described by @Halpern\_2006. However, there
-are also opinions that the relationship is spurious {[}@Keil\_2012{]}.
-We used R for our calculations {[}@R\_Core\_Team\_2016{]}, and we used
-package \texttt{knitcitations} {[}@Boettiger\_2017{]} to make the
-bibliography.
+The relationship was first described by Halpern, Regan, Possingham, \&
+McCarthy (2006). However, there are also opinions that the relationship
+is spurious (Keil, Belmaker, Wilson, Unitt, \& Jetz, 2012). We used R
+for our calculations (R Core Team, 2016), and we used package.
 
@@
 
-\section{REFERENCES}\label{references}
+\section*{REFERENCES}\label{references}
+\addcontentsline{toc}{section}{REFERENCES}
+
+\hypertarget{refs}{}
+\hypertarget{ref-Halpern_2006}{}
+Halpern, B. S., Regan, H. M., Possingham, H. P., \& McCarthy, M. A.
+(2006). Accounting for uncertainty in marine reserve design.
+\emph{Ecology Letters}, \emph{9}(1), 2--11.
+doi:\href{https://doi.org/10.1111/j.1461-0248.2005.00827.x}{10.1111/j.1461-0248.2005.00827.x}
+
+\hypertarget{ref-Keil_2012}{}
+Keil, P., Belmaker, J., Wilson, A. M., Unitt, P., \& Jetz, W. (2012).
+Downscaling of species distribution models: A hierarchical approach.
+\emph{Methods in Ecology and Evolution}, \emph{4}(1), 82--94.
+doi:\href{https://doi.org/10.1111/j.2041-210x.2012.00264.x}{10.1111/j.2041-210x.2012.00264.x}
+
+\hypertarget{ref-R_Core_Team_2016}{}
+R Core Team. (2016). \emph{R: A language and environment for statistical
+computing}. Vienna, Austria: R Foundation for Statistical Computing.
+Retrieved from \url{https://www.R-project.org/}
 

### 2018-10-05 R/mapr.R
Add mapr function to generate land shapefile for ggplot

@@ -1,0 +1,52 @@
+##' Generate a land shapefile for a region of interest specified by telemetry data
+##'
+##' The telemetry data is given as a dataframe where each row is an
+##' observed location and columns
+##' \describe{
+##' \item{'id'}{individual animal identifier,}
+##' \item{'date'}{observation time (POSIXct,GMT),}
+##' \item{'lon'}{observed longitude,}
+##' \item{'lat'}{observed latitude,}
+##' \item{'...'}{named covariates appended to track}
+##' }
+##'
+##' @title mapr
+##' @param data a data frame of observations (see details)
+##' @param prj a PROJ.4 compatable projection for the region of interest *NOT* WGS84
+##' @param buff a buffer to expand region of interest specified in metres
+##' @return a list with components
+##' \item{\code{world_shp}}{a projected shapefile for the region of interest}
+##' @examples
+##' data(ellie.ice)
+##' prj <- "+proj=laea +lat_0=-60 +lon_0=70 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
+##' world_shp <- mapr(ellie.ice, prj, buff = 1e6)
+##' ggplot() + 
+##'   geom_sf(aes(), data = world_shp) +
+##'   geom_sf(aes(), data = st_as_sf(ellie.ice, coords = c("lon", "lat")) %>% st_set_crs("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
+##'
+##' @export
+mapr <- function(dat,
+                 prj,
+                 buff){
+  
+  #convert to sf and project
+  dat_sf <- sf::st_as_sf(dat, coords = c("lon", "lat")) %>%
+    sf::st_set_crs("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs") %>%
+    sf::st_transform(prj)
+  #create clip shape for world map
+  CP <- sf::st_bbox(dat_sf) %>%
+    sf::st_as_sfc() %>%
+    sf::st_buffer(buff) %>%
+    sf::st_segmentize(1e4) %>%
+    sf::st_transform("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+  
+  #Load in world shape from rworldmap and clip
+  world_shp <- sf::st_as_sf(rworldmap::countriesLow)
+  world_shp <- sf::st_crop(world_shp, CP)
[…]

### 2018-10-05 R/script.r

@@ -2,6 +2,7 @@
 require(tidyverse)
 require(sf)
 source("R/mpmm.r")
+source("R/mapr.r")
 
 # import data
 d <- read.csv("dat/hp2_ctrw.csv", stringsAsFactors = FALSE) %>%
@@ -14,6 +15,17 @@ d <- read.csv("dat/hp2_ctrw.csv", stringsAsFactors = FALSE) %>%
   mutate(av.depth = ifelse(av.depth >=8 , av.depth, NA)) %>%
   mutate(date = lubridate::ymd_hms(date, tz = "UTC")) %>%
   filter(id != "hp2-9320-04", id != "hp2-9349-04")
+
+# plot data to check and demonstrate new 'mapr' function
+d_sf <- st_as_sf(d, coords = c("lon", "lat")) %>%
+  st_set_crs("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
+
+prj = "+proj=laea +lat_0=75 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
+world_shp <- mapr(d, prj, buff = 500000)
+
+ggplot() +
+  geom_sf(aes(), data = world_shp) + 
+  geom_sf(aes(), data = d_sf)
 
 # run lambda mpmm model
 fit <- mpmm(~ 1 + (1 | id), d, verbose = TRUE)
